---
title: "fig05"
author: "adam gordon-fennell"
date: '2023-12-28'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# run all chunks from the project root so relative paths resolve correctly
knitr::opts_knit$set(root.dir = normalizePath('../'))
```

# setup
## libraries
```{r}
source('./logs_and_keys/key_local_directories.R')
Sys.unsetenv("RETICULATE_PYTHON_FALLBACK")
Sys.unsetenv("RETICULATE_PYTHON")
reticulate::use_python(path_python, required = TRUE)

library(tidyverse)
library(afex)
library(emmeans)
library(janitor)
library(readxl)
library(ggh4x) # force_panelsizes
library(arrow)
library(zoo)
library(lubridate)
library(patchwork)
library(ggbeeswarm)
library(ggpubr) # r2 on correlation
library(pals)
library(boot)  # bootstrapping
library(corrplot)
library(Hmisc)
library(plotly)

arrow::set_cpu_count(4)

source('./functions/params.R')
source('./functions/theme.R')
source('./functions/general.R')
source('./functions/r_general.R')
source('./functions/r_plots.R')
source('./functions/stats.R')
source('./functions/pca.R')
source('./functions/analysis_peth.R')
source('./functions/plotting_placements.R')
```

## directories
```{r}
dir_combined_setid <- './data/combined_setid/'
dir_output         <- './analysis_and_plots/fig05/'

dir.create(dir_output, recursive = TRUE, showWarnings = FALSE)
```

## logs / keys
```{r}
log_analysis_fp  <- read_xlsx('./logs_and_keys/log_data_analysis.xlsx', sheet = 'fp',          na = c('NA', ''))
log_analysis_exp <- read_xlsx('./logs_and_keys/log_data_analysis.xlsx', sheet = 'experiments', na = c('NA', ''))
log_placements   <- read.csv('./logs_and_keys/log_fiber_placements.csv', na.strings = c('', 'NA'))
```

# analysis / plotting
## setup
```{r}
# helper used by all fp str sections — filters to striatum (non-LHA) regions
filt_and_format_data <- function(df){
  df %>%
    filter(!region %>% str_detect('LHA')) %>%
    filter(set_id %in% c('frsuc', 'wrsuc', 'wrnacl')) %>%
    mutate(region = region %>% factor(levels = unique(key_regions$region_label))) %>%
    format_set_id(key_set_id)
}
```


## preprocessing
# all raw data is loaded here once and saved to pre/
# individual figure sections read only from pre/ — no cross-section dependencies
```{r eval=FALSE}
# ── setup ──────────────────────────────────────────────────────────────────────
toggle_process <- 0   # 1 = load from dir_combined_setid and save  |  0 = CSVs already exist

dir_output_pre <- str_c(dir_output, 'pre/')
dir.create(dir_output_pre, recursive = TRUE, showWarnings = FALSE)
```

```{r eval=FALSE}
if (toggle_process == 1) {

  # ── 1. fp str trace (fig5d) ──────────────────────────────────────────────────
  fns      <- list.files(dir_combined_setid)
  fns_filt <- fns[fns %>% str_detect('filtlick')]
  fns_filt <- fns_filt[fns_filt %>% str_detect('peth_summary_trace_overal')]
  fns_filt <- fns_filt[fns_filt != 'filtlick_peth_summary_trace_overall.csv']
  fns_filt <- fns_filt %>% str_remove('.csv')

  combined_import(
    import_directory = dir_combined_setid,
    filter_strings = fns_filt, prefixes = NA, suffixes = c('.csv'), verbose = 0
  )[[1]] %>%
    filt_and_format_data() %>%
    write_csv(str_c(dir_output_pre, 'fp_str_trace_data.csv'))

  # ── 2. licking trace (fig5d) ─────────────────────────────────────────────────
  fns      <- list.files(dir_combined_setid)
  fns_filt <- fns[fns %>% str_detect('binnedlick_trace_overall')]
  fns_filt <- fns_filt %>% str_remove('.csv')

  combined_import(
    import_directory = dir_combined_setid,
    filter_strings = fns_filt, prefixes = NA, suffixes = c('.csv'), verbose = 0
  )[[1]] %>%
    mutate(region = 'dummy') %>%
    filt_and_format_data() %>%
    select(-region) %>%
    write_csv(str_c(dir_output_pre, 'fp_str_licking_data.csv'))

  # ── 3. fp str means — sustained + post (fig5h, fig5i, fig5k, fig5l) ─────────
  fns      <- list.files(dir_combined_setid)
  fns_filt <- fns[fns %>% str_detect('filtlick')]
  fns_filt <- fns_filt[fns_filt %>% str_detect('peth_summary_means_subject')]
  fns_filt <- fns_filt %>% str_remove('.csv')

  df_means <- combined_import(
    import_directory = dir_combined_setid,
    filter_strings = fns_filt, prefixes = NA, suffixes = c('.csv'), verbose = 0
  )[[1]] %>%
    filt_and_format_data()

  df_means %>% filter(time_bin == 'sustained') %>% write_csv(str_c(dir_output_pre, 'fp_str_sustained_data.csv'))
  df_means %>% filter(time_bin == 'post')      %>% write_csv(str_c(dir_output_pre, 'fp_str_post_data.csv'))

  # ── 4. sustained range: high - low z-score (fig5i, fig5g/j/m) ───────────────
  df_means %>%
    filter(time_bin == 'sustained') %>%
    select(set_id, subject, region, solution, zscore_blsub_mean) %>%
    mutate(solution_magnitude = case_when(
      solution %in% c('sucrose00', 'nacl150') ~ 'low',
      solution %in% c('sucrose30', 'nacl000') ~ 'high'
    )) %>%
    filter(!is.na(solution_magnitude)) %>%
    select(-solution) %>%
    spread(solution_magnitude, zscore_blsub_mean) %>%
    mutate(range = high - low) %>%
    write_csv(str_c(dir_output_pre, 'fp_str_range_sustained_data.csv'))

  # ── 5. post range: high - low z-score (fig5l, fig5g/j/m) ────────────────────
  df_means %>%
    filter(time_bin == 'post') %>%
    select(set_id, subject, region, solution, zscore_blsub_mean) %>%
    mutate(solution_magnitude = case_when(
      solution %in% c('sucrose00', 'nacl150') ~ 'low',
      solution %in% c('sucrose30', 'nacl000') ~ 'high'
    )) %>%
    filter(!is.na(solution_magnitude)) %>%
    select(-solution) %>%
    spread(solution_magnitude, zscore_blsub_mean) %>%
    mutate(range = high - low) %>%
    write_csv(str_c(dir_output_pre, 'fp_str_range_post_data.csv'))

  # ── 6+7. lick vs nolick trace — per set_id and combined overall (fig5e top) ──
  fns      <- list.files(dir_combined_setid)
  fns_filt <- fns[fns %>% str_detect('full')]
  fns_filt <- fns_filt[fns_filt %>% str_detect('full_peth_summary_trace_triallick')]
  fns_filt <- fns_filt %>% str_remove('.csv')

  df_lick_trace <- combined_import(
    import_directory = dir_combined_setid,
    filter_strings = fns_filt, prefixes = NA, suffixes = c('.csv'), verbose = 0
  )[[1]] %>%
    filt_and_format_data() %>%
    mutate(trial_lick = case_when(trial_lick == 0 ~ 'no_lick', trial_lick == 1 ~ 'lick'))

  # per set_id
  df_lick_trace %>%
    write_csv(str_c(dir_output_pre, 'fp_str_lickvsnolick_trace_setid_data.csv'))

  # combined overall: collapse set_id and solution → one trace per region × trial_lick × time_rel
  df_lick_trace %>%
    group_by(region, trial_lick, time_rel) %>%
    summarise(
      zscore_blsub_mean = mean(zscore_blsub_mean, na.rm = TRUE),
      zscore_blsub_sem  = mean(zscore_blsub_sem,  na.rm = TRUE),
      .groups = 'drop'
    ) %>%
    write_csv(str_c(dir_output_pre, 'fp_str_lickvsnolick_trace_overall_data.csv'))

  # ── 8. lick vs nolick prelick means by subject (fig5e bottom, fig5f) ─────────
  fns      <- list.files(dir_combined_setid)
  fns_filt <- fns[fns %>% str_detect('triallick')]
  fns_filt <- fns_filt[fns_filt %>% str_detect('peth_summary_means_subject')]
  fns_filt <- fns_filt %>% str_remove('.csv')

  df_prelick <- combined_import(
    import_directory = dir_combined_setid,
    filter_strings = fns_filt, prefixes = NA, suffixes = c('.csv'), verbose = 0
  )[[1]] %>%
    filt_and_format_data()

  df_prelick %>% write_csv(str_c(dir_output_pre, 'fp_str_lickvsnolick_prelick_data.csv'))

  # ── 9. prelick range: lick - nolick z-score (fig5f, fig5g/j/m) ──────────────
  df_prelick %>%
    filter(time_bin == 'prelick') %>%
    select(set_id, subject, region, trial_lick, zscore_blsub_mean) %>%
    spread(trial_lick, zscore_blsub_mean) %>%
    mutate(range = `1` - `0`) %>%
    write_csv(str_c(dir_output_pre, 'fp_str_range_prelick_data.csv'))

  # ── 10. lick vs nolick prelick means — combined across all set_ids (fig5e bottom + stats)
  # this is a separately pre-computed file where trials were pooled across set_ids
  # BEFORE computing subject means — not merely an average of per-set_id means
  read.csv(str_c(dir_combined_setid, 'combined_main_set_id_lickvsnolick_peth_summary_means_subject.csv')) %>%
    filter(!region %>% str_detect('LHA')) %>%
    mutate(region = region %>% factor(levels = unique(key_regions$region_label))) %>%
    select(subject, region, time_bin, trial_lick, zscore_blsub_mean) %>%
    write_csv(str_c(dir_output_pre, 'fp_str_lickvsnolick_prelick_combined_data.csv'))

} else {

  message('toggle_process = 0: preprocessing CSVs will be read by each section as needed')

}
```


---

## fig5b: fp str placements colored region
```{r eval=FALSE}
dir_output_b <- str_c(dir_output, 'b/')
dir.create(dir_output_b, recursive = TRUE, showWarnings = FALSE)

# derive unique subject × region pairs from the range data
summary_range_b <- read.csv(str_c(dir_output_pre, 'fp_str_range_prelick_data.csv'))   %>% select(subject, region) %>%
  bind_rows(read.csv(str_c(dir_output_pre, 'fp_str_range_sustained_data.csv')) %>% select(subject, region)) %>%
  bind_rows(read.csv(str_c(dir_output_pre, 'fp_str_range_post_data.csv'))      %>% select(subject, region)) %>%
  unique()

plt_data_b <- summary_range_b %>%
  join_placements() %>%
  select(subject, region, starts_with('hit')) %>%
  mutate(region = region %>% factor(levels = unique(key_regions$region_label)))

# subject and fiber counts
plt_data_b %>% group_by(region) %>% summarise(count = n()) %>% summarise(fiber_count_total = sum(count))
plt_data_b %>% select(subject) %>% unique() %>% summarise(subject_count_total = n())
```

```{r eval=FALSE}
source('./functions/plotting_placements.R')

for(loop_plane in c('horizontal')){
  plt_str_d(df = plt_data_b, var_color = !!sym('region'), var_color_name = 'Region',
            vars_facet = c('.', '.'), plt_plane = loop_plane,
            plt_dim_base = 2, color_values = color_values_regions_da7)
  save_pdf(dir_output_b, str_c('placement_generic_', loop_plane, '.pdf'), 6, 6)
}

```

---

## fig5d: lick & fp str trace
```{r eval=FALSE}
dir_output_d <- str_c(dir_output, 'd/')
dir.create(dir_output_d, recursive = TRUE, showWarnings = FALSE)

plt_data_d <- read.csv(str_c(dir_output_pre, 'fp_str_trace_data.csv')) %>%
  mutate(region = factor(region, levels = key_regions$region_label %>% unique())) %>%
  mutate(set_id = factor(set_id, levels = key_set_id$set_id_label %>% unique()))

plt_data_d_lick <- read.csv(str_c(dir_output_pre, 'fp_str_licking_data.csv')) %>%
  mutate(set_id = factor(set_id, levels = key_set_id$set_id_label %>% unique()))
```

```{r eval=FALSE}
# licking trace
plt <- plt_data_d_lick %>%
  ggplot(aes(time_rel, lick_hz_mean, group = solution, color = solution, fill = solution)) +
  annotate("rect", xmin = 0, xmax = 3, ymin = -Inf, ymax = Inf, alpha = 1/3, fill = "darkgrey") +
  geom_hline(yintercept = 0, color = 'darkgrey', size = 0.5) +
  geom_ribbon(
    aes(ymin = lick_hz_mean - lick_hz_sem, ymax = lick_hz_mean + lick_hz_sem),
    alpha = 1/3, color = NA) +
  geom_line() +
  facet_grid(set_id~.) +
  scale_color_manual(values = c(color_values_nacl, color_values_suc)) +
  scale_fill_manual(values  = c(color_values_nacl, color_values_suc)) +
  theme_ag01(6) +
  theme(strip.text = element_text(margin = margin(t = 5, r = 5, b = 5, l = 5))) +
  theme(panel.spacing.y = unit(0.5, "lines")) +
  force_panelsizes(rows = unit(2, 'cm'), cols = unit(2.3, 'cm'))

plt <- plt %>% add_scale_bar(origin = c(-0.1, -1), x_len = 1, y_len = 1)
plt
save_pdf(dir_output_d, 'fp_str_licking.pdf', 9, 4)
```

```{r eval=FALSE, fig.width = 8, fig.height = 4}
# fp trace
plt <- plt_data_d %>%
  ggplot(aes(time_rel, zscore_blsub_mean, group = solution, color = solution, fill = solution)) +
  annotate("rect", xmin = 0, xmax = 3, ymin = -Inf, ymax = Inf, alpha = 1/3, fill = "darkgrey") +
  geom_hline(yintercept = 0, color = 'darkgrey', size = 0.5) +
  geom_ribbon(
    aes(ymin = zscore_blsub_mean - zscore_blsub_sem, ymax = zscore_blsub_mean + zscore_blsub_sem),
    alpha = 1/3, color = NA) +
  geom_line() +
  facet_grid(set_id~region) +
  scale_color_manual(values = c(color_values_nacl, color_values_suc)) +
  scale_fill_manual(values  = c(color_values_nacl, color_values_suc)) +
  theme_ag01(6) +
  theme(strip.text = element_text(margin = margin(t = 5, r = 5, b = 5, l = 5))) +
  theme(panel.spacing.y = unit(0.5, "lines")) +
  force_panelsizes(rows = unit(2, 'cm'), cols = unit(2.3, 'cm'))

plt <- plt %>% add_scale_bar(origin = c(-3, -1), x_len = 1, y_len = 1)
plt
save_pdf(dir_output_d, 'fp_str_trace.pdf', 9, 4)
```

---

## fig5e: fp str lick vs nolick
```{r eval=FALSE}
# ── setup ──────────────────────────────────────────────────────────────────────
toggle_process <- 0 # 1 = compute stats and save  |  0 = read saved stats

dir_output_e <- str_c(dir_output, 'e/')
dir.create(dir_output_e, recursive = TRUE, showWarnings = FALSE)

fn_e_stats <- 'fp_str_summary_lickvsnolick_prelick_stats'
```

```{r eval=FALSE}
plt_data_e_overall <- read.csv(str_c(dir_output_pre, 'fp_str_lickvsnolick_trace_overall_data.csv')) %>%
  mutate(region = factor(region, levels = key_regions$region_label %>% unique()))

plt_data_e_setid <- read.csv(str_c(dir_output_pre, 'fp_str_lickvsnolick_trace_setid_data.csv')) %>%
  mutate(region = factor(region, levels = key_regions$region_label %>% unique())) %>%
  mutate(set_id = factor(set_id, levels = key_set_id$set_id_label %>% unique()))

plt_data_e_prelick <- read.csv(str_c(dir_output_pre, 'fp_str_lickvsnolick_prelick_data.csv')) %>%
  mutate(region = factor(region, levels = key_regions$region_label %>% unique())) %>%
  mutate(set_id = factor(set_id, levels = key_set_id$set_id_label %>% unique()))

# combined across all set_ids — trials pooled before subject means were computed (see preprocessing step 10)
plt_data_e_prelick_overall <- read.csv(str_c(dir_output_pre, 'fp_str_lickvsnolick_prelick_combined_data.csv')) %>%
  mutate(region = factor(region, levels = key_regions$region_label %>% unique()))

if (toggle_process == 1) {

  stats_e_prelick <- plt_data_e_prelick_overall %>%
    filter(time_bin == 'prelick') %>%
    mutate(trial_lick = ifelse(trial_lick == 1, 'lick', 'nolick')) %>%
    select(subject, region, trial_lick, zscore_blsub_mean) %>%
    spread(trial_lick, zscore_blsub_mean) %>%
    tidy_ttest_paired(NA, NA, 'lick', 'nolick', 'region') %>%
    quick_sig()

  stats_e_prelick %>% write_csv(str_c(dir_output_e, fn_e_stats, '.csv'))

} else {

  stats_e_prelick <- read.csv(str_c(dir_output_e, fn_e_stats, '.csv'))

}
```

```{r eval=FALSE}
# trace: lick vs no-lick — combined across set_ids
plt <- plt_data_e_overall %>%
  filter(time_rel < 3, time_rel > -0.5) %>%
  ggplot(aes(time_rel, zscore_blsub_mean, group = trial_lick, color = trial_lick, fill = trial_lick)) +
  annotate("rect", xmin = 0, xmax = 3, ymin = -Inf, ymax = Inf, alpha = 1/3, fill = "darkgrey") +
  geom_vline(xintercept = 0.3, color = 'darkgrey', size = 0.5, linetype = 2) +
  geom_hline(yintercept = 0, color = 'darkgrey', size = 0.5) +
  geom_ribbon(
    aes(ymin = zscore_blsub_mean - zscore_blsub_sem, ymax = zscore_blsub_mean + zscore_blsub_sem),
    alpha = 1/3, color = NA) +
  geom_line() +
  facet_grid(.~region) +
  scale_color_manual(values = c('blue', 'black')) +
  scale_fill_manual(values  = c('blue', 'black')) +
  theme_ag01(6) +
  theme(strip.text = element_text(margin = margin(t = 5, r = 5, b = 5, l = 5))) +
  force_panelsizes(rows = unit(7.878, 'mm'), cols = unit(12, 'mm'))

plt <- plt %>% add_scale_bar(origin = c(-0.5, -0.5), x_len = 1, y_len = 1)
plt
save_pdf(dir_output_e, 'fp_str_lickvnolick_overall.pdf', 6, 6)
```

```{r eval=FALSE}
# prelick summary: lick vs no-lick (0 vs ≥1 licks) — combined across set_ids (trials pooled before subject means)
plt_data_e_prelick_overall %>%
  filter(time_bin == 'prelick') %>%
  mutate(trial_lick = ifelse(trial_lick == 0, '0', '≥1')) %>%
  mutate(trial_lick = trial_lick %>% factor(levels = c('0', '≥1'))) %>%
  ggplot(aes(trial_lick, zscore_blsub_mean)) +
  geom_line(aes(group = interaction(region, subject)), alpha = 1/3, size = 1/4) +
  geom_hline(yintercept = 0, size = 1/4, color = 'darkgrey') +
  stat_summary(fun = 'mean', geom = 'line', aes(group = 1)) +
  stat_summary(fun.data = 'mean_se', geom = 'errorbar', aes(group = 1), width = 0) +
  theme_ag01(6) +
  facet_grid(.~region, scales = 'free') +
  coord_cartesian(xlim = c(0.5, 2.5), ylim = c(-1, 3), clip = 'off', expand = 0) +
  force_panelsizes(rows = unit(7.878, 'mm'), cols = unit(12, 'mm')) +
  theme(strip.text.x = element_blank()) +
  ylab('Z-score pre-lick (0.0-0.3 s)') + xlab('')

save_pdf(dir_output_e, 'fp_str_summary_lickvsnolick_prelick.pdf', 6, 6)

# stats
stats_e_prelick %>% select(region, sig_symbol)
```

---

## fig5f: fp str prelick range
```{r eval=FALSE}
dir_output_f <- str_c(dir_output, 'f/')
dir.create(dir_output_f, recursive = TRUE, showWarnings = FALSE)

plt_data_f <- read.csv(str_c(dir_output_pre, 'fp_str_range_prelick_data.csv')) %>%
  mutate(region = factor(region, levels = key_regions$region_label %>% unique())) %>%
  mutate(set_id = factor(set_id, levels = key_set_id$set_id_label %>% unique()))
```

```{r eval=FALSE}
plt_data_f %>%
  group_by(set_id, region) %>%
  summarise(range_mean = range %>% mean(na.rm = TRUE), .groups = 'drop') %>%
  ggplot(aes(region, set_id, fill = range_mean)) +
  geom_tile() +
  scale_fill_viridis_c(limits = c(-0.2, 1), oob = scales::squish) +
  ylab('') + xlab('') +
  theme_ag01(6) +
  coord_cartesian(xlim = c(0.5, 7.5), ylim = c(0.5, 3.5), clip = 'off', expand = 0) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3)) +
  force_panelsizes(rows = unit(16, 'mm'), cols = unit(20, 'mm'))

save_pdf(dir_output_f, 'fp_str_summary_lickvsnolick_prelick_heat.pdf', 6, 6)
```

---

## fig5h: fp str sustained
```{r eval=FALSE}
# ── setup ──────────────────────────────────────────────────────────────────────
toggle_process <- 0   # 1 = compute stats and save  |  0 = read saved stats

dir_output_h <- str_c(dir_output, 'h/')
dir.create(dir_output_h, recursive = TRUE, showWarnings = FALSE)

fn_h <- 'fp_str_summary_combined_sustained'
```

```{r eval=FALSE}
plt_data_h <- read.csv(str_c(dir_output_pre, 'fp_str_sustained_data.csv')) %>%
  mutate(region = factor(region, levels = key_regions$region_label %>% unique())) %>%
  mutate(set_id = factor(set_id, levels = key_set_id$set_id_label %>% unique()))

if (toggle_process == 1) {

  set_ids    <- plt_data_h$set_id %>% unique()
  regions    <- plt_data_h$region %>% unique()
  first_loop <- 1

  for(loop_set_id in set_ids){
    for(loop_region in regions){
      stats_list <- plt_data_h %>%
        filter(set_id == loop_set_id, region == loop_region) %>%
        aov_rm_one_within(NA, NA, 'subject', 'zscore_blsub_mean', 'solution')

      stats_list[[2]] <- stats_list[[2]] %>%
        mutate(set_id = loop_set_id, region = loop_region) %>%
        select(set_id, region, everything())
      stats_list[[3]] <- stats_list[[3]] %>%
        mutate(set_id = loop_set_id, region = loop_region) %>%
        select(set_id, region, everything())

      if(first_loop == 1){
        aov_h_oneway <- stats_list[[2]]; hsd_h_oneway <- stats_list[[3]]; first_loop <- 0
      } else {
        aov_h_oneway <- stats_list[[2]] %>% bind_rows(aov_h_oneway,.)
        hsd_h_oneway <- stats_list[[3]] %>% bind_rows(hsd_h_oneway,.)
      }
    }
  }

  aov_h_oneway <- aov_h_oneway %>%
    select(-sig_text, -sig_symbol) %>%
    rename(p_value_raw = p_value) %>%
    mutate(p_value = ifelse(set_id %in% c('FR:Suc', 'WR:Suc'), p_value_raw * 3, p_value_raw)) %>%
    quick_sig()

  aov_h_oneway %>% write_csv(str_c(dir_output_h, fn_h, '_stats_aov_oneway.csv'))
  hsd_h_oneway %>% write_csv(str_c(dir_output_h, fn_h, '_stats_hsd_oneway.csv'))

  # two-way anova: solution × set_id for fr/wr suc, per region
  first_loop <- 1

  for(loop_region in regions){
    stats_list <- plt_data_h %>%
      filter(set_id %in% c('WR:Suc', 'FR:Suc'), region == loop_region) %>%
      aov_rm_two_within(NA, NA, 'subject', 'zscore_blsub_mean', 'solution', 'set_id')

    stats_list[[2]] <- stats_list[[2]] %>% mutate(region = loop_region) %>% select(region, everything())
    stats_list[[3]] <- stats_list[[3]] %>% mutate(region = loop_region) %>% select(region, everything())

    if(first_loop == 1){
      aov_h_interaction <- stats_list[[2]]; hsd_h_interaction <- stats_list[[3]]; first_loop <- 0
    } else {
      aov_h_interaction <- stats_list[[2]] %>% bind_rows(aov_h_interaction,.)
      hsd_h_interaction <- stats_list[[3]] %>% bind_rows(hsd_h_interaction,.)
    }
  }

  aov_h_interaction <- aov_h_interaction %>%
    select(-sig_text, -sig_symbol) %>%
    rename(p_value_raw = p_value) %>%
    mutate(p_value = p_value_raw * 3) %>%
    quick_sig()

  aov_h_interaction %>% write_csv(str_c(dir_output_h, fn_h, '_stats_aov_interaction.csv'))
  hsd_h_interaction %>% write_csv(str_c(dir_output_h, fn_h, '_stats_hsd_interaction.csv'))

} else {

  aov_h_oneway      <- read.csv(str_c(dir_output_h, fn_h, '_stats_aov_oneway.csv'))      %>% mutate(region = factor(region, levels = key_regions$region_label %>% unique())) %>% mutate(set_id = factor(set_id, levels = key_set_id$set_id_label %>% unique()))
  hsd_h_oneway      <- read.csv(str_c(dir_output_h, fn_h, '_stats_hsd_oneway.csv'))
  aov_h_interaction <- read.csv(str_c(dir_output_h, fn_h, '_stats_aov_interaction.csv')) %>% mutate(region = factor(region, levels = key_regions$region_label %>% unique()))
  hsd_h_interaction <- read.csv(str_c(dir_output_h, fn_h, '_stats_hsd_interaction.csv'))

}
```

```{r eval=FALSE}
plt_data_h %>%
  left_join(join_solution_x) %>%
  ggplot(aes(plt_x, zscore_blsub_mean, color = set_id)) +
  geom_hline(yintercept = 0, size = 1/4, color = 'darkgrey') +
  stat_summary(fun = 'mean', geom = 'line', aes(group = set_id)) +
  stat_summary(fun.data = 'mean_se', geom = 'errorbar', aes(group = set_id), width = 0) +
  theme_ag01(6) +
  scale_color_manual(values = color_values_experiment_set) +
  theme(axis.text.x = element_blank()) +
  facet_grid(.~region, scales = 'free') +
  coord_cartesian(xlim = c(0.5, 5.5), ylim = c(-2, 6), clip = 'off', expand = 0) +
  force_panelsizes(rows = unit(16,'mm'), cols = unit(12, 'mm')) +
  theme(strip.text = element_blank()) +
  ylab('Z-score sustained (2-3 s)') + xlab('')

save_pdf(dir_output_h, str_c(fn_h, '.pdf'), 6, 6)
```

```{r eval=FALSE}
# solution effect per region × set_id
aov_h_oneway %>%
  mutate(set_id = factor(set_id, levels = c('WR:Suc', 'FR:Suc', 'WR:NaCl'))) %>%
  filter(effect == 'solution') %>%
  select(set_id, region, p_value) %>%
  quick_sig() %>%
  ggplot(aes(region, set_id, label = sig_symbol)) +
  geom_text()

# solution × set_id interaction (fr/wr suc)
aov_h_interaction %>%
  filter(effect == 'solution*set_id') %>%
  select(region, p_value) %>%
  quick_sig() %>%
  ggplot(aes(region, 1, label = sig_symbol)) +
  geom_text()
```

---

## fig5i: fp str sustained range
```{r eval=FALSE}
dir_output_i <- str_c(dir_output, 'i/')
dir.create(dir_output_i, recursive = TRUE, showWarnings = FALSE)

plt_data_i <- read.csv(str_c(dir_output_pre, 'fp_str_range_sustained_data.csv')) %>%
  mutate(region = factor(region, levels = key_regions$region_label %>% unique())) %>%
  mutate(set_id = factor(set_id, levels = key_set_id$set_id_label %>% unique()))
```

```{r eval=FALSE}
plt_data_i %>%
  group_by(set_id, region) %>%
  summarise(range_mean = range %>% mean(), .groups = 'drop') %>%
  ggplot(aes(region, set_id, fill = range_mean)) +
  geom_tile() +
  scale_fill_viridis_c(limits = c(-1, 5), oob = scales::squish) +
  ylab('') + xlab('') +
  coord_cartesian(xlim = c(0.5, 7.5), ylim = c(0.5, 3.5), clip = 'off', expand = 0) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3)) +
  force_panelsizes(rows = unit(16, 'mm'), cols = unit(20, 'mm'))

save_pdf(dir_output_i, 'fp_str_range_sustained_heat.pdf', 6, 6)
```

---

## fig5k: fp str post
```{r eval=FALSE}
# ── setup ──────────────────────────────────────────────────────────────────────
toggle_process <- 0   # 1 = compute stats and save  |  0 = read saved stats

dir_output_k <- str_c(dir_output, 'k/')
dir.create(dir_output_k, recursive = TRUE, showWarnings = FALSE)

fn_k <- 'fp_str_summary_combined_post'
```

```{r eval=FALSE}
plt_data_k <- read.csv(str_c(dir_output_pre, 'fp_str_post_data.csv')) %>%
  mutate(region = factor(region, levels = key_regions$region_label %>% unique())) %>%
  mutate(set_id = factor(set_id, levels = key_set_id$set_id_label %>% unique()))

if (toggle_process == 1) {

  set_ids    <- plt_data_k$set_id %>% unique()
  regions    <- plt_data_k$region %>% unique()
  first_loop <- 1

  for(loop_set_id in set_ids){
    for(loop_region in regions){
      stats_list <- plt_data_k %>%
        filter(set_id == loop_set_id, region == loop_region) %>%
        aov_rm_one_within(NA, NA, 'subject', 'zscore_blsub_mean', 'solution')

      stats_list[[2]] <- stats_list[[2]] %>%
        mutate(set_id = loop_set_id, region = loop_region) %>%
        select(set_id, region, everything())
      stats_list[[3]] <- stats_list[[3]] %>%
        mutate(set_id = loop_set_id, region = loop_region) %>%
        select(set_id, region, everything())

      if(first_loop == 1){
        aov_k_oneway <- stats_list[[2]]; hsd_k_oneway <- stats_list[[3]]; first_loop <- 0
      } else {
        aov_k_oneway <- stats_list[[2]] %>% bind_rows(aov_k_oneway,.)
        hsd_k_oneway <- stats_list[[3]] %>% bind_rows(hsd_k_oneway,.)
      }
    }
  }

  aov_k_oneway <- aov_k_oneway %>%
    select(-sig_text, -sig_symbol) %>%
    rename(p_value_raw = p_value) %>%
    mutate(p_value = ifelse(set_id %in% c('FR:Suc', 'WR:Suc'), p_value_raw * 3, p_value_raw)) %>%
    quick_sig()

  aov_k_oneway %>% write_csv(str_c(dir_output_k, fn_k, '_stats_aov_oneway.csv'))
  hsd_k_oneway %>% write_csv(str_c(dir_output_k, fn_k, '_stats_hsd_oneway.csv'))

  # two-way anova: solution × set_id for fr/wr suc, per region
  first_loop <- 1

  for(loop_region in regions){
    stats_list <- plt_data_k %>%
      filter(set_id %in% c('WR:Suc', 'FR:Suc'), region == loop_region) %>%
      aov_rm_two_within(NA, NA, 'subject', 'zscore_blsub_mean', 'solution', 'set_id')

    stats_list[[2]] <- stats_list[[2]] %>% mutate(region = loop_region) %>% select(region, everything())
    stats_list[[3]] <- stats_list[[3]] %>% mutate(region = loop_region) %>% select(region, everything())

    if(first_loop == 1){
      aov_k_interaction <- stats_list[[2]]; hsd_k_interaction <- stats_list[[3]]; first_loop <- 0
    } else {
      aov_k_interaction <- stats_list[[2]] %>% bind_rows(aov_k_interaction,.)
      hsd_k_interaction <- stats_list[[3]] %>% bind_rows(hsd_k_interaction,.)
    }
  }

  aov_k_interaction <- aov_k_interaction %>%
    select(-sig_text, -sig_symbol) %>%
    rename(p_value_raw = p_value) %>%
    mutate(p_value = p_value_raw * 3) %>%
    quick_sig()

  aov_k_interaction %>% write_csv(str_c(dir_output_k, fn_k, '_stats_aov_interaction.csv'))
  hsd_k_interaction %>% write_csv(str_c(dir_output_k, fn_k, '_stats_hsd_interaction.csv'))

} else {

  aov_k_oneway      <- read.csv(str_c(dir_output_k, fn_k, '_stats_aov_oneway.csv'))      %>% mutate(region = factor(region, levels = key_regions$region_label %>% unique())) %>% mutate(set_id = factor(set_id, levels = key_set_id$set_id_label %>% unique()))
  hsd_k_oneway      <- read.csv(str_c(dir_output_k, fn_k, '_stats_hsd_oneway.csv'))
  aov_k_interaction <- read.csv(str_c(dir_output_k, fn_k, '_stats_aov_interaction.csv')) %>% mutate(region = factor(region, levels = key_regions$region_label %>% unique()))
  hsd_k_interaction <- read.csv(str_c(dir_output_k, fn_k, '_stats_hsd_interaction.csv'))

}
```

```{r eval=FALSE}
plt_data_k %>%
  left_join(join_solution_x) %>%
  ggplot(aes(plt_x, zscore_blsub_mean, color = set_id)) +
  geom_hline(yintercept = 0, size = 1/4, color = 'darkgrey') +
  stat_summary(fun = 'mean', geom = 'line', aes(group = set_id)) +
  stat_summary(fun.data = 'mean_se', geom = 'errorbar', aes(group = set_id), width = 0) +
  theme_ag01(6) +
  scale_color_manual(values = color_values_experiment_set) +
  theme(axis.text.x = element_blank()) +
  facet_grid(.~region, scales = 'free') +
  coord_cartesian(xlim = c(0.5, 5.5), ylim = c(-1, 1.5), clip = 'off', expand = 0) +
  force_panelsizes(rows = unit(16,'mm'), cols = unit(12, 'mm')) +
  theme(strip.text = element_blank()) +
  ylab('Z-score post (6-8 s)') + xlab('')

save_pdf(dir_output_k, str_c(fn_k, '.pdf'), 6, 6)
```

```{r eval=FALSE}
# solution effect per region × set_id
aov_k_oneway %>%
  mutate(set_id = factor(set_id, levels = c('WR:Suc', 'FR:Suc', 'WR:NaCl'))) %>%
  filter(effect == 'solution') %>%
  select(set_id, region, p_value) %>%
  quick_sig() %>%
  ggplot(aes(region, set_id, label = sig_symbol)) +
  geom_text()

# solution × set_id interaction (fr/wr suc)
aov_k_interaction %>%
  filter(effect == 'solution*set_id') %>%
  select(region, p_value) %>%
  quick_sig() %>%
  ggplot(aes(region, 1, label = sig_symbol)) +
  geom_text()
```

---

## fig5l: fp str post range
```{r eval=FALSE}
dir_output_l <- str_c(dir_output, 'l/')
dir.create(dir_output_l, recursive = TRUE, showWarnings = FALSE)

plt_data_l <- read.csv(str_c(dir_output_pre, 'fp_str_range_post_data.csv')) %>%
  mutate(region = factor(region, levels = key_regions$region_label %>% unique())) %>%
  mutate(set_id = factor(set_id, levels = key_set_id$set_id_label %>% unique()))
```

```{r eval=FALSE}
plt_data_l %>%
  group_by(set_id, region) %>%
  summarise(range_mean = range %>% mean(), .groups = 'drop') %>%
  ggplot(aes(region, set_id, fill = range_mean)) +
  geom_tile() +
  scale_fill_viridis_c(limits = c(-1, 2), oob = scales::squish) +
  ylab('') + xlab('') +
  coord_cartesian(xlim = c(0.5, 7.5), ylim = c(0.5, 3.5), clip = 'off', expand = 0) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3)) +
  force_panelsizes(rows = unit(16, 'mm'), cols = unit(20, 'mm'))

save_pdf(dir_output_l, 'fp_str_range_post_heat.pdf', 6, 6)
```

---

## fig5g/j/m: fp str placements range — 3D (WR:NaCl)
```{r eval=FALSE}
dir_output_gjm <- str_c(dir_output, 'gjm/')
dir.create(dir_output_gjm, recursive = TRUE, showWarnings = FALSE)

# combine range data across time bins — all read directly from pre/
summary_range_combined <- read.csv(str_c(dir_output_pre, 'fp_str_range_prelick_data.csv'))   %>% mutate(time_bin = 'prelick')   %>% select(set_id, subject, region, time_bin, range) %>%
  bind_rows(read.csv(str_c(dir_output_pre, 'fp_str_range_sustained_data.csv')) %>% mutate(time_bin = 'sustained') %>% select(set_id, subject, region, time_bin, range)) %>%
  bind_rows(read.csv(str_c(dir_output_pre, 'fp_str_range_post_data.csv'))      %>% mutate(time_bin = 'post')      %>% select(set_id, subject, region, time_bin, range)) %>%
  mutate(set_id = factor(set_id, levels = key_set_id$set_id_label %>% unique()))
```

```{r eval=FALSE}
for(loop_time_bin in c('prelick', 'sustained', 'post')){

  fn_stem_gjm <- str_c('placement_vs_range_WRNaCl_', loop_time_bin)

  df <- summary_range_combined %>%
    filter(set_id == 'WR:NaCl', time_bin == loop_time_bin) %>%
    join_placements() %>%
    select(set_id, subject, time_bin, region, range, starts_with('hit')) %>%
    mutate(region = region %>% factor(levels = unique(key_regions$region_label))) %>%
    filter(!is.na(range))

  if(loop_time_bin == 'prelick')   color_limits <- c(-0.2, 1)
  if(loop_time_bin == 'sustained') color_limits <- c(-1,   5)
  if(loop_time_bin == 'post')      color_limits <- c(-1,   2)

  tryCatch(
    plt_str_3d(df = df, var_color = 'range', color_limits = color_limits,
               dir_output = dir_output_gjm, fn_stem = fn_stem_gjm, toggle_save = 1),
    error = function(e) message('plt_str_3d skipped (kaleido): ', conditionMessage(e))
  )
}
```

---

