---
title: "fig04 / sfig05"
author: "adam gordon-fennell"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# run all chunks from the project root so relative paths resolve correctly
knitr::opts_knit$set(root.dir = normalizePath('../'))
```

# setup
## libraries
```{r eval=FALSE}
source('./logs_and_keys/key_local_directories.R')
Sys.unsetenv("RETICULATE_PYTHON_FALLBACK")
Sys.unsetenv("RETICULATE_PYTHON")
reticulate::use_python(path_python, required = TRUE)

library(tidyverse)
library(afex)
library(emmeans)
library(janitor)
library(readxl)
library(ggh4x)
library(arrow)
library(zoo)
library(lubridate)
library(patchwork)
library(ggbeeswarm)
library(ggpubr)
library(pals)
library(boot)
library(corrplot)
library(Hmisc)
library(plotly)

arrow::set_cpu_count(4)

source('./functions/params.R')
source('./functions/theme.R')
source('./functions/general.R')
source('./functions/r_general.R')
source('./functions/r_plots.R')
source('./functions/stats.R')
source('./functions/pca.R')
source('./functions/analysis_peth.R')
source('./functions/plotting_placements.R')
```

## directories
```{r eval=FALSE}
dir_output <- './analysis_and_plots/fig04_sfig05/'
dir_data   <- './data/fig04_sfig05/'

dir.create(dir_output,                    recursive = TRUE, showWarnings = FALSE)
dir.create(str_c(dir_output, 'b/'),       recursive = TRUE, showWarnings = FALSE)
dir.create(str_c(dir_output, 'c/'),       recursive = TRUE, showWarnings = FALSE)
dir.create(str_c(dir_output, 'd/'),       recursive = TRUE, showWarnings = FALSE)
dir.create(str_c(dir_output, 'e/'),       recursive = TRUE, showWarnings = FALSE)
dir.create(str_c(dir_output, 'f/'),       recursive = TRUE, showWarnings = FALSE)
dir.create(str_c(dir_output, 'g/'),       recursive = TRUE, showWarnings = FALSE)
dir.create(str_c(dir_output, 'h/'),       recursive = TRUE, showWarnings = FALSE)
dir.create(str_c(dir_output, 'sfig05a/'), recursive = TRUE, showWarnings = FALSE)
dir.create(str_c(dir_output, 'sfig05b/'), recursive = TRUE, showWarnings = FALSE)
dir.create(str_c(dir_output, 'sfig05c/'), recursive = TRUE, showWarnings = FALSE)
dir.create(str_c(dir_output, 'sfig05d/'), recursive = TRUE, showWarnings = FALSE)
dir.create(str_c(dir_output, 'sfig05e/'), recursive = TRUE, showWarnings = FALSE)

plt_dims <- c(3, 3)
```

## logs / keys
```{r eval=FALSE}
# Fiber placement log — used by plt_str_3d() and plt_corr()
log_placements <- read.csv('./logs_and_keys/log_fiber_placements.csv',
                           na.strings = c('', 'NA'))
```

## keys (fig04/sfig05-specific)
```{r eval=FALSE}
# 6-region striatal subset used in the acd inhibition experiment.
# Shadows key_regions from params.R.
key_regions <- tibble(
  region       = c('nac',   'nac_corr', 'nac_shelllat', 'dms', 'dls', 'ts'),
  region_label = c('NAcCR', 'NAcCC',    'NAcShL',        'DMS', 'DLS', 'TS')
)

# Group color palette — control / LHA:GABA (vgat) / LHA:Glut (vglut2)
color_group_combined <- color_values_groupcombined  # c('darkgrey', '#CC2029', '#70BF46')
```

## functions (fig04/sfig05-specific)
```{r eval=FALSE}
# ── format_group_combined ──────────────────────────────────────────────────────
# Builds group_combined from 'line' and 'group' columns.
# Produces: 'control', 'vgat_inh', 'vglut2_inh'.
format_group_combined <- function(df) {
  df %>%
    mutate(group_combined = ifelse(line %>% str_detect('vglut2'), 'vglut2', NA)) %>%
    mutate(group_combined = ifelse(line %>% str_detect('vgat'),   'vgat',   group_combined)) %>%
    mutate(group_combined = ifelse(tolower(group) == 'mcherry',   'control', group_combined)) %>%
    mutate(group_combined = ifelse(tolower(group) == 'chrimson',  group_combined %>% str_c('_stim'), group_combined)) %>%
    mutate(group_combined = ifelse(tolower(group) == 'hr',        group_combined %>% str_c('_inh'),  group_combined))
}

# ── format_vars ────────────────────────────────────────────────────────────────
# Converts raw solution and stim_id codes to display labels.
# solution: 'water' → 'Water', 'nacl100' → '1M NaCl'
# stim_id:  'lha'   → 'Stim',  'no_stim' → 'No stim'
format_vars <- function(df) {
  df %>%
    mutate(
      stim_id = case_when(
        stim_id == 'lha'     ~ 'Stim',
        stim_id == 'no_stim' ~ 'No stim',
        TRUE                 ~ stim_id
      )
    ) %>%
    mutate(
      solution = case_when(
        solution == 'water'   ~ 'Water',
        solution == 'nacl100' ~ '1M NaCl',
        TRUE                  ~ solution
      )
    )
}

# ── plt_corr ──────────────────────────────────────────────────────────────────
# Plots fiber placement (AP / ML / DV mm) vs. response (var_dep), faceted by
# group_combined. Returns list: AP, ML, DV ggplot objects + stats_output.
# Source: abo_analysis_opto_multispout_v02.Rmd (functions section, line ~430)
plt_corr <- function(df, ylim_all, xlim_ap, xlim_ml, xlim_dv,
                     var_dep, var_dep_label, plt_dims) {

  plt_data <- df %>%
    gather('dim', 'mm', starts_with('hit')) %>%
    mutate(dim = case_when(
      dim == 'hit_ap' ~ 'AP',
      dim == 'hit_ml' ~ 'ML',
      dim == 'hit_dv' ~ 'DV'
    )) %>%
    mutate(dim = dim %>% factor(levels = c('AP', 'ML', 'DV')))

  f_plt <- function(plt_data, ylim_all, xlim_ap, xlim_ml, xlim_dv,
                    var_dep, var_dep_label, plt_dims, plt_dim) {
    plt <- plt_data %>%
      filter(dim == plt_dim) %>%
      ggplot(aes(mm, !!as.name(var_dep), color = group_combined, fill = group_combined)) +
      geom_hline(yintercept = 0, color = 'darkgrey', size = 0.5) +
      geom_smooth(method = 'lm', size = 0.3, alpha = 1/5) +
      geom_jitter(shape = 21, size = 2, color = 'white', stroke = 1/3) +
      facet_grid(group_combined ~ dim, scales = 'free') +
      theme_ag01() +
      scale_color_manual(values = color_group_combined) +
      scale_fill_manual(values  = color_group_combined) +
      xlab('MM Relative to bregma') +
      ylab(var_dep_label) +
      theme(strip.text.y = element_blank()) +
      theme(panel.spacing.y = unit(0.75, 'lines'))

    if (plt_dim == 'AP') {
      plt <- plt +
        coord_cartesian(ylim = ylim_all, xlim = c(min(xlim_ap), max(xlim_ap)), expand = F, clip = 'off') +
        stat_cor(method = 'pearson', label.y = ylim_all[2], label.x = -3, size = 2) +
        scale_x_continuous(breaks = xlim_ap) +
        theme(axis.title.x = element_blank())
    }
    if (plt_dim == 'ML') {
      plt <- plt +
        coord_cartesian(ylim = ylim_all, xlim = c(min(xlim_ml), max(xlim_ml)), expand = F, clip = 'off') +
        stat_cor(method = 'pearson', label.y = ylim_all[2], label.x = 0, size = 2) +
        scale_x_continuous(breaks = xlim_ml)
      plt <- plt %>% remove_y_all
    }
    if (plt_dim == 'DV') {
      plt <- plt +
        coord_cartesian(ylim = ylim_all, xlim = c(min(xlim_dv), max(xlim_dv)), expand = F, clip = 'off') +
        stat_cor(method = 'pearson', label.y = ylim_all[2], label.x = -6, size = 2) +
        scale_x_continuous(breaks = xlim_dv) +
        theme(axis.title.x = element_blank())
      plt <- plt %>% remove_y_all
    }
    return(plt)
  }

  plt_list <- list()
  for (plt_dim in c('AP', 'ML', 'DV')) {
    plt_list[[plt_dim]] <- f_plt(plt_data, ylim_all, xlim_ap, xlim_ml, xlim_dv,
                                 var_dep, var_dep_label, plt_dims, plt_dim)
  }

  plt_list[['stats_output']] <- plt_data %>%
    tidy_cor('mm', var_dep, 'dim', 'group_combined')

  return(plt_list)
}
```

---

# preprocessing notes

## behavior (panels B / C / D)
```{r eval=FALSE}
# ── PREPROCESSING NOTE ────────────────────────────────────────────────────────
# The block below documents how the pre-computed CSVs in data/fig04_sfig05/ were
# produced. Requires Google Sheets credentials and arduino extracted/processed data.
#
# Source files:
#   arduino processed: str_c(dir_exp_abo, 'data/arduino/processed/')
#   arduino extracted: str_c(dir_exp_abo, 'data/arduino/extracted/')
#   log_npm:           Google Sheet (url_sheet_npm)
#   log_data_multi:    Google Sheet (url_sheet_npm_multi)
#   log_subject:       Google Sheet (url_sheet_subject)
#   log_opto_stim_ids: above url_sheet_npm_multi, sheet = 'opto_stimulation_ids'
#
# Source Rmd:
#   str_c(dir_writing_lha_da, 'submission01/analysis/analysis_multispout_behavior_optoinhibition.Rmd')
#   # inhibition behavior [fig04d]     (line ~178)
#   # lick rasters opto behavior       (line ~258)
#   # [fig04b]                          (line ~322) → writes fig04c_licking_raster_rep.csv
#   # binned lick rate [fig4c]          (line ~379) → writes fig04c_binned_lick_subject.csv
# ─────────────────────────────────────────────────────────────────────────────

# # ── logs / sheets ──────────────────────────────────────────────────────────
# log_npm <- read_sheet(url_sheet_npm, na = c('','NA'))
# log_data_multi <- read_sheet(url_sheet_npm_multi, na = c('NA',''))
# log_subject <- read_sheet(url_sheet_subject, na = 'NA', sheet = 'subject')
# log_opto_stim_ids <- suppressWarnings(
#   read_sheet(url_sheet_npm_multi,
#              sheet = 'opto_stimulation_ids', na = c('NA', ''))
# ) %>%
#   select(-today) %>%
#   filter(experiment == 'acd')
#
# # trial-level behavior (produced in analysis_multispout_behavior_optoinhibition.Rmd)
# trial_summary_behavior <- read.csv(
#   './data/multispout_behavior_optoinhibition/data_trial_summary.csv') %>%
#   format_group_combined() %>%
#   format_vars()
#
# # write to repo
# trial_summary_behavior %>%
#   write_csv('./data/fig04_sfig05/fig04_licking_trial.csv')
#
# # ── arduino data for lick rasters (acd experiment) ────────────────────────
# dir_arduino_processed <- str_c(dir_exp_abo, 'data/arduino/processed/')
# dir_arduino_extracted <- str_c(dir_exp_abo, 'data/arduino/extracted/')
#
# import_fns <- log_npm %>%
#   filter(experiment %in% c('acd')) %>%
#   filter(procedure == 'water_nacl_opto') %>%
#   filter(exclude == 0) %>%
#   pull(blockname) %>% unique()
#
# data_list <- combined_import(import_directory = dir_arduino_processed,
#                              filter_strings = import_fns,
#                              prefixes = NA,
#                              suffixes = c('_data_trial.csv', '_data_trial_binned.csv', '_data_trial_summary.csv'))
# data_trial         <- data_list[[1]]
# data_trial_binned  <- data_list[[2]]
# data_trial_summary <- data_list[[3]]
#
# trial_stim_ids <- return_trial_ids(dir_arduino_extracted, import_fns, 'csv', filt_last = 0) %>%
#   left_join(log_data_multi %>% select(blockname, experiment, date, subject)) %>%
#   left_join(log_opto_stim_ids %>%
#               select(experiment, date, subject, trial_stim_id, stim_power_uw, pulse_frequency, delay, region, id))
#
# data_trial <- data_trial %>%
#   left_join(trial_stim_ids %>% select(blockname, trial_num, id)) %>%
#   mutate(stim_id = ifelse(is.na(id), 'No Stim', 'Stim'))
#
# data_trial_binned <- data_trial_binned %>%
#   left_join(trial_stim_ids %>% select(blockname, trial_num, id)) %>%
#   mutate(stim_id = ifelse(is.na(id), 'No Stim', 'Stim'))
#
# # ── raster data: representative subjects [fig04b] ─────────────────────────
# # subjects: acd06 (control), acd11 (vglut2_inh), acd14 (vgat_inh)
# join_trial_num_solution_stim <- data_trial_summary %>%
#   select(blockname, solution, stim_id, trial_num) %>%
#   unique() %>%
#   group_by(blockname, solution, stim_id) %>%
#   mutate(trial_num_solution_stim = row_number())
#
# data_plt_raster <- data_trial %>%
#   mutate(lick_number = row_number()) %>%
#   left_join(join_trial_num_solution_stim) %>%
#   mutate(solution = str_c(solution, stim_id)) %>%
#   filter(blockname %in% c('2024_05_29_acd06', '2024_05_29_acd11', '2024_05_29_acd14')) %>%
#   mutate(group_combined = case_when(
#     blockname == '2024_05_29_acd06' ~ 'control',
#     blockname == '2024_05_29_acd11' ~ 'vglut_inh',
#     blockname == '2024_05_29_acd14' ~ 'vgat_inh'
#   ))
#
# data_plt_raster %>%
#   write_csv('./data/fig04_sfig05/fig04c_licking_raster_rep.csv')
#
# # ── binned lick rate: all subjects [fig04c] ───────────────────────────────
# data_plt_binned <- data_trial_binned %>%
#   mutate(binned_lick_rate = count_binned / (time_bin_width / 1000),
#          time_bin = time_bin / 1000) %>%
#   left_join(log_npm %>% select(blockname, subject) %>% unique()) %>%
#   left_join(log_subject %>% select(subject, line, group)) %>%
#   format_group_combined() %>%
#   select(blockname, subject, group_combined, solution, stim_id, time_bin, binned_lick_rate)
#
# data_plt_binned %>%
#   write_csv('./data/fig04_sfig05/fig04c_binned_lick_subject.csv')
```

## FP preprocessing — light artifact and baseline subtraction (panels E–H and sfig05 a–e)
```{r eval=FALSE}
# ── PREPROCESSING NOTE ────────────────────────────────────────────────────────
# The block below documents how fig04_peth_subjects.csv and sfig05a_peth_rep.csv
# were produced. Requires npm processed FP (network) and Google Sheets credentials.
#
# Source files:
#   npm processed FP:  str_c(dir_npm, 'data_processed/')
#   log_placements:    Google Sheet (url_sheet_placements, sheet = 'placements', experiment == 'acd')
#   QC metrics:        ./data/sessions/quality_metrics.csv
#
# Source Rmd:
#   str_c(dir_exp_abo, 'abo_analysis_opto_multispout_v02.Rmd')
#   ## final: consumption effect - distant baseline [fig04e-f]   (line ~2048)
#   #### placements [fig04g-h]                                    (line ~2208)
#   ### depiction of baseline subtraction [sfig05a]              (line ~1514)
#   ## final: inhibtion baseline effect [sfig05b]                (line ~1898)
#   ## final: consumption effect - proximal baseline [sfig05d-e] (line ~2312)
#
# ── Baseline subtraction — two steps ──────────────────────────────────────────
# Step 1a (blsubdist — "distant" pre-laser baseline):
#   Window: time_rel -9 to -6 s. Per-trial mean subtracted from all timepoints.
#   Then subract_artifact_continuouslaser(window_bl=c(-5.9,-5.8), window_artifact=c(-5.9,9))
#   removes the artifact shape within the continuous laser window.
#   → delta_signal_poly_zscore_blsubdist
#
# Step 2 (blsub — "proximal" pre-access baseline):
#   Window: time_rel -3 to 0 s. Per-trial mean of blsubdist subtracted.
#   → delta_signal_poly_zscore_blsub
#
# fig04e–f and sfig05b use blsubdist (distant baseline).
# sfig05d–e use blsub (proximal baseline).
# sfig05a shows all three variants (no bl / blsubdist / blsub) for subject acd09, DLS, control.
# ─────────────────────────────────────────────────────────────────────────────

# # ── local artifact removal function ───────────────────────────────────────
# subract_artifact_continuouslaser <- function(df, window_bl, window_artifact, var_grouping){
#   df %>%
#     filter(time_rel >= window_bl[1], time_rel <= window_bl[2]) %>%
#     group_by(across(all_of(var_grouping))) %>%
#     summarise(
#       zscore_bldist  = delta_signal_poly_zscore_blsubdist %>% mean(),
#       control_bldist = delta_control_poly_zscore_blsubdist %>% mean(),
#       lls_bldist     = delta_signal_fitted_control_zscore_blsubdist %>% mean(),
#       .groups = 'drop'
#     ) %>%
#     left_join(df) %>%
#     mutate(
#       delta_signal_poly_zscore_blsubdist = ifelse(
#         time_rel >= window_artifact[1] & time_rel <= window_artifact[2],
#         delta_signal_poly_zscore_blsubdist - zscore_bldist,
#         delta_signal_poly_zscore_blsubdist),
#       delta_control_poly_zscore_blsubdist = ifelse(
#         time_rel >= window_artifact[1] & time_rel <= window_artifact[2],
#         delta_control_poly_zscore_blsubdist - control_bldist,
#         delta_control_poly_zscore_blsubdist),
#       delta_signal_fitted_control_zscore_blsubdist = ifelse(
#         time_rel >= window_artifact[1] & time_rel <= window_artifact[2],
#         delta_signal_fitted_control_zscore_blsubdist - lls_bldist,
#         delta_signal_fitted_control_zscore_blsubdist)
#     ) %>%
#     select(-zscore_bldist, -control_bldist, -lls_bldist)
# }
#
# # ── session identification ─────────────────────────────────────────────────
# import_fns <- log_npm %>%
#   filter(experiment %in% c('acd')) %>%
#   filter(procedure == 'water_nacl_opto') %>%
#   filter(exclude == 0) %>%
#   pull(blockname) %>% unique()
#
# log_opto_stim_ids <- suppressWarnings(
#   read_sheet(url_sheet_npm_multi,
#              sheet = 'opto_stimulation_ids', na = c('NA', ''))
# ) %>%
#   select(-today) %>%
#   filter(experiment == 'acd')
#
# trial_stim_ids <- return_trial_ids(dir_arduino_extraction, import_fns, 'csv', filt_last = 0) %>%
#   left_join(log_data_multi %>% select(blockname, experiment, date, subject)) %>%
#   left_join(log_opto_stim_ids %>%
#               select(experiment, date, subject, trial_stim_id, stim_power_uw, pulse_frequency, delay, region, id))
#
# # ── import raw FP streams ─────────────────────────────────────────────────
# dir_npm_processed <- str_c(dir_npm, 'data_processed/')
#
# data_list <- combined_import(import_directory = dir_npm_processed,
#                              filter_strings = import_fns,
#                              prefixes = NA,
#                              suffixes = c('streams_peth.feather', 'events.feather'),
#                              verbose = 0)
# events       <- data_list[[2]]
# streams_peth <- data_list[[1]] %>% filter(signal_wavelength == 470)
# streams_peth <- streams_peth %>% mutate(subject = blockname %>% str_sub(12, 16))
#
# # ── Step 1a: distant pre-laser baseline subtraction ────────────────────────
# streams_peth <- streams_peth %>%
#   filter(time_rel > -9, time_rel < -6) %>%
#   group_by(blockname, event_id_char, branch_id, signal_wavelength, event_number) %>%
#   summarise(
#     zscore_bl    = mean(delta_signal_poly_zscore),
#     control_bl   = mean(delta_control_poly_zscore),
#     zscorells_bl = mean(delta_signal_fitted_control_zscore)
#   ) %>%
#   left_join(streams_peth, .) %>%
#   mutate(
#     delta_signal_poly_zscore_blsubdist           = delta_signal_poly_zscore - zscore_bl,
#     delta_control_poly_zscore_blsubdist          = delta_control_poly_zscore - control_bl,
#     delta_signal_fitted_control_zscore_blsubdist = delta_signal_fitted_control_zscore - zscorells_bl
#   ) %>%
#   select(-zscore_bl, -control_bl, -zscorells_bl)
#
# # ── Step 1b: artifact shape removal (continuous laser window) ──────────────
# streams_peth <- streams_peth %>%
#   subract_artifact_continuouslaser(
#     window_bl       = c(-5.9, -5.8),
#     window_artifact = c(-5.9, 9),
#     var_grouping    = c('blockname', 'event_id_char', 'signal_wavelength', 'branch_id', 'event_number'))
#
# # ── Step 2: proximal pre-access baseline subtraction ──────────────────────
# streams_peth <- streams_peth %>%
#   filter(time_rel > -3, time_rel < 0) %>%
#   group_by(blockname, event_id_char, branch_id, signal_wavelength, event_number) %>%
#   summarise(
#     zscore_bl    = mean(delta_signal_poly_zscore_blsubdist),
#     control_bl   = mean(delta_control_poly_zscore_blsubdist),
#     zscorells_bl = mean(delta_signal_fitted_control_zscore_blsubdist)
#   ) %>%
#   left_join(streams_peth, .) %>%
#   mutate(
#     delta_signal_poly_zscore_blsub           = delta_signal_poly_zscore_blsubdist - zscore_bl,
#     delta_control_poly_zscore_blsub          = delta_control_poly_zscore_blsubdist - control_bl,
#     delta_signal_fitted_control_zscore_blsub = delta_signal_fitted_control_zscore_blsubdist - zscorells_bl
#   ) %>%
#   select(-zscore_bl, -control_bl, -zscorells_bl)
#
# # ── join trial behavioral data ─────────────────────────────────────────────
# join_trial_summary_behavior <- trial_summary_behavior %>%
#   filter(blockname %in% import_fns) %>%
#   select(blockname, line, group, trial_num, lick_count, lick_ts_last, solution, stim_id)
#
# streams_peth_solution <- streams_peth %>%
#   rename(trial_num = event_number) %>%
#   left_join(join_trial_summary_behavior) %>%
#   filter(!is.na(solution))
#
# join_event_number_solution <- streams_peth_solution %>%
#   select(blockname, solution, trial_num) %>%
#   unique() %>%
#   arrange(blockname, trial_num) %>%
#   group_by(blockname, solution) %>%
#   mutate(event_number_solution = row_number())
#
# streams_peth_solution <- streams_peth_solution %>%
#   left_join(join_event_number_solution)
#
# # ── filter: placements and signal quality ─────────────────────────────────
# log_placements_abo <- read_sheet(
#   url_sheet_placements,
#   na = c('NA',''), sheet = 'placements') %>%
#   filter(experiment == 'acd')
#
# fibers_to_remove <- log_placements_abo %>%
#   filter(exclude_da_consumption == 1) %>%
#   select(subject, region = target)
#
# streams_peth_solution <- streams_peth_solution %>%
#   left_join(log_npm %>% select(blockname, branch_id, region)) %>%
#   format_regions('region', key_regions) %>%
#   anti_join(fibers_to_remove)
#
# fns_qc_metrics <- list.files('./data/sessions/',
#                               pattern = 'quality_metrics.csv', recursive = TRUE, full.names = TRUE)
# combined_qc_metrics <- bind_rows(lapply(fns_qc_metrics, read.csv)) %>%
#   format_regions('region', key_regions)
#
# streams_peth_solution <- streams_peth_solution %>%
#   left_join(combined_qc_metrics %>% select(blockname, region, exclude_poor_signal),
#             by = c('blockname', 'region')) %>%
#   filter(exclude_poor_signal == 0 | is.na(exclude_poor_signal)) %>%
#   select(-exclude_poor_signal)
#
# # ── sfig05a: single-subject depiction (acd09, DLS, control) ───────────────
# df_plt_sbj <- streams_peth_solution %>%
#   filter(region == 'DLS', subject == 'acd09') %>%
#   format_group_combined() %>%
#   filter(group_combined == 'control') %>%
#   group_by(subject, group_combined, region, stim_id, time_rel) %>%
#   summarise(
#     delta_signal_poly_zscore            = mean(delta_signal_poly_zscore),
#     delta_signal_poly_zscore_blsubdist  = mean(delta_signal_poly_zscore_blsubdist),
#     delta_signal_poly_zscore_blsub      = mean(delta_signal_poly_zscore_blsub)
#   )
#
# df_plt_sbj %>%
#   write_csv('./data/fig04_sfig05/sfig05a_peth_rep.csv')
#
# # ── subject-level average (all panels) ────────────────────────────────────
# df <- streams_peth_solution %>%
#   select(blockname, subject, line, group, region, solution, stim_id, time_rel,
#          delta_signal_poly_zscore,
#          delta_signal_poly_zscore_blsub,
#          delta_signal_poly_zscore_blsubdist,
#          delta_control_poly_zscore_blsub,
#          delta_control_poly_zscore_blsubdist) %>%
#   format_group_combined() %>%
#   group_by(subject, group_combined, region, solution, stim_id, time_rel) %>%
#   summarise(
#     delta_signal_poly_zscore             = mean(delta_signal_poly_zscore),
#     delta_signal_poly_zscore_blsub       = mean(delta_signal_poly_zscore_blsub),
#     delta_signal_poly_zscore_blsubdist   = mean(delta_signal_poly_zscore_blsubdist),
#     delta_control_poly_zscore_blsub      = mean(delta_control_poly_zscore_blsub),
#     delta_control_poly_zscore_blsubdist  = mean(delta_control_poly_zscore_blsubdist)
#   )
#
# df %>%
#   write_csv('./data/fig04_sfig05/fig04_peth_subjects.csv')
```

---

# data import
```{r eval=FALSE}
# FP subject-level data — used for fig04e–h and all sfig05 FP panels
# stim_id values: 'lha' / 'no_stim' (raw); solution: 'water' / 'nacl100' (raw)
df <- read.csv(str_c(dir_data, 'fig04_peth_subjects.csv')) %>%
  mutate(region = factor(region, levels = key_regions$region_label %>% unique()))

# Licking trial-level data — used for fig04d
# stim_id values: 'No stim' / 'Stim' (formatted); solution: 'Water' / '1M NaCl' (formatted)
plt_data_licking_trial <- read.csv(str_c(dir_data, 'fig04_licking_trial.csv'))
```

---

# fig04

## fig04b: lick raster — representative subjects
```{r eval=FALSE}
dir_output_b <- str_c(dir_output, 'b/')
fn_stem_b    <- 'time_vs_trialsorted_raster'

# solution column combined with stim_id before raster (as in source preprocessing)
data_plt_raster <- read.csv(str_c(dir_data, 'fig04b_licking_raster_rep.csv')) %>%
  mutate(solution = str_c(solution, stim_id))

plt_raster(
  df              = data_plt_raster,
  x               = 'event_ts_rel',
  y               = 'trial_num_solution_stim',
  id              = 'subject',
  facet_x         = 'group_combined',
  facet_y         = 'solution',
  xlab            = 'Time (ms)',
  ylab            = 'Trial Number',
  plt_y_lims      = c(0, 40),
  plt_x_lims      = c(0, 3000),
  plt_dims        = c(2, 1.5),
  var_color       = 'stim_id',
  plt_scale_color = 'mako'
) +
  scale_color_manual(values = c('black', '#00B0F0'))

save_pdf(dir_output_b, str_c(fn_stem_b, '.pdf'), 8, 8)
data_plt_raster %>% write_csv(str_c(dir_output_b, fn_stem_b, '_data.csv'))
```

---

## fig04c: binned lick rate trace
```{r eval=FALSE}
dir_output_c <- str_c(dir_output, 'c/')
fn_stem_c    <- 'time_vs_binnedlickrate'

# stim_id values: 'No Stim' / 'Stim' (capital S on both)
data_plt_binned <- read.csv(str_c(dir_data, 'fig04c_binned_lick_subject.csv')) %>%
  mutate(stim_id = factor(stim_id, levels = c('No Stim', 'Stim')))

plt <- data_plt_binned %>%
  ggplot(aes(time_bin, binned_lick_rate, color = stim_id, fill = stim_id)) +
  stat_summary(fun.data = 'mean_se', geom = 'ribbon', aes(group = stim_id),
               alpha = 1/3, color = NA) +
  stat_summary(fun = 'mean', geom = 'line', aes(group = stim_id)) +
  scale_color_manual(values = c('black', '#00B0F0')) +
  scale_fill_manual(values  = c('black', '#00B0F0')) +
  scale_y_continuous(breaks = c(0, 2)) +
  scale_x_continuous(breaks = c(0, 1)) +
  theme_ag01() +
  facet_grid(solution ~ group_combined) +
  force_panelsizes(rows = unit(3, 'cm'), cols = unit(2, 'cm')) +
  xlab('Time (s)') +
  ylab('Lick Rate (Hz)')

plt %>%
  add_scale_bar(origin = c(0, 0), x_len = 1, y_len = 2)

save_pdf(dir_output_c, str_c(fn_stem_c, '.pdf'), 8, 8)
data_plt_binned %>% write_csv(str_c(dir_output_c, fn_stem_c, '_data.csv'))
```

---

## fig04d: mean trial lick count (stim vs no stim)
```{r eval=FALSE}
dir_output_d <- str_c(dir_output, 'd/')
fn_stem_d    <- 'stim_vs_lickcount_line'

# aggregate to session level: mean lick count per subject × solution × stim_id
plt_data_d <- plt_data_licking_trial %>%
  mutate(stim_id = factor(stim_id, levels = c('No stim', 'Stim'))) %>%
  group_by(group_combined, subject, solution, stim_id) %>%
  summarise(lick_count = mean(lick_count, na.rm = TRUE), .groups = 'drop')

plt_data_d %>%
  select(group_combined, subject) %>%
  unique() %>%
  group_by(group_combined) %>%
  summarise(subject_count = n())

plt_data_d %>%
  ggplot(aes(stim_id, lick_count, color = solution)) +
  annotate('rect', xmin = 1.75, xmax = 2.25, ymin = -Inf, ymax = Inf,
           alpha = 1/3, fill = 'lightblue') +
  geom_line(aes(group = interaction(subject, solution)), alpha = 1/3) +
  stat_summary(fun = 'mean', geom = 'line', aes(group = solution)) +
  stat_summary(fun.data = 'mean_se', geom = 'errorbar', aes(group = solution), width = 0.1) +
  facet_grid(. ~ group_combined) +
  theme_ag01() +
  theme(strip.text = element_text(margin = margin(b = 10))) +
  coord_cartesian(xlim = c(0.5, 2.5), ylim = c(0, 25), expand = FALSE) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3)) +
  scale_color_manual(values = c('red', 'black')) +
  force_panelsizes(rows = unit(plt_dims[1], 'cm'), cols = unit(plt_dims[2] / 3, 'cm')) +
  xlab('') +
  ylab('Mean trial lick count')

save_pdf(dir_output_d, str_c(fn_stem_d, '.pdf'), 8, 8)
plt_data_d %>% write_csv(str_c(dir_output_d, fn_stem_d, '_data.csv'))
```

```{r eval=FALSE}
# stats: 3-way RM ANOVA (group_combined × solution × stim_id)
stats_list_d <- plt_data_d %>%
  aov_rm_one_between_two_within(dir_output_d, fn_stem_d,
                                'subject', 'lick_count',
                                'group_combined', 'solution', 'stim_id')

# post-hoc: within-solution, within-group stim comparisons
stats_list_d[[3]] %>%
  filter(
    contrast1_within1 == contrast2_within1,
    contrast1_between == contrast2_between
  ) %>%
  select(starts_with('contrast'), sig_symbol)
```

---

## fig04e: FP trace — stim vs no-stim difference (distant baseline, −9 to 12 s)
```{r eval=FALSE}
dir_output_e <- str_c(dir_output, 'e/')
fn_stem_e    <- 'inh_access_prelaserbl_trace'

plt_data_e <- df %>%
  filter(time_rel >= -9, time_rel <= 12) %>%
  select(group_combined, subject, region, solution, stim_id, time_rel,
         zscore = delta_signal_poly_zscore_blsubdist) %>%
  format_vars() %>%
  spread(stim_id, zscore) %>%
  mutate(diff = Stim - `No stim`) %>%
  group_by(group_combined, region, solution, time_rel) %>%
  summarise(
    diff_sem = sd(diff, na.rm = TRUE) / sqrt(sum(!is.na(diff))),
    diff     = mean(diff, na.rm = TRUE),
    .groups  = 'drop'
  )

plt <- plt_data_e %>%
  ggplot(aes(time_rel, diff, color = region, fill = region)) +
  annotate('rect', xmin = -6, xmax = 9, ymin = -Inf, ymax = Inf,
           alpha = 1/8, fill = '#2baee4') +
  annotate('rect', xmin = 0,  xmax = 3, ymin = -Inf, ymax = Inf,
           alpha = 1/3, fill = 'darkgrey') +
  geom_hline(yintercept = 0, color = 'darkgrey', size = 0.5) +
  geom_ribbon(aes(ymax = diff + diff_sem, ymin = diff - diff_sem),
              color = NA, alpha = 1/3) +
  geom_line() +
  facet_grid(solution ~ group_combined) +
  theme_ag01() +
  scale_color_manual(values = color_values_regions_da) +
  scale_fill_manual(values  = color_values_regions_da)

plt <- plt %>%
  add_scale_bar(origin = c(-9, -1), x_len = 1, y_len = 1)

plt +
  force_panelsizes(cols = unit(4.3, 'cm'), rows = unit(2.5955, 'cm'))

save_pdf(dir_output_e, str_c(fn_stem_e, '.pdf'), 8, 4)
plt_data_e %>% write_csv(str_c(dir_output_e, fn_stem_e, '_data.csv'))
```

---

## fig04f: FP summary bar — region vs stim/no-stim difference (0–2 s, distant baseline)
```{r eval=FALSE}
dir_output_f <- str_c(dir_output, 'f/')
fn_stem_f    <- 'inh_access_prelaserbl_region_vs_difference'

plt_data_f_summary <- df %>%
  filter(time_rel > 0, time_rel < 2) %>%
  group_by(subject, region, stim_id, group_combined, solution) %>%
  summarise(zscore = mean(delta_signal_poly_zscore_blsubdist, na.rm = TRUE), .groups = 'drop')

plt_data_f_delta <- plt_data_f_summary %>%
  format_vars() %>%
  spread(stim_id, zscore) %>%
  mutate(diff = Stim - `No stim`)

plt_data_f_summary %>%
  select(group_combined, region, subject) %>%
  unique() %>%
  group_by(group_combined, region) %>%
  summarise(count_fibers = n()) %>%
  spread(group_combined, count_fibers)

plt_data_f_delta %>%
  ggplot(aes(region, diff, color = group_combined, fill = group_combined)) +
  geom_hline(yintercept = 0, alpha = 1/3) +
  stat_summary(fun.data = 'mean_se', geom = 'errorbar', aes(group = group_combined),
               width = 0.3, position = position_dodge(width = 0.75)) +
  stat_summary(fun = 'mean', geom = 'bar', color = NA, aes(group = group_combined),
               alpha = 1/2, width = 0.6, position = position_dodge(width = 0.75)) +
  geom_jitter(shape = 21, color = 'white', size = 1.5, stroke = 0.25,
              position = position_jitterdodge(jitter.width = 0.04, dodge.width = 0.75)) +
  theme_ag01() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3)) +
  scale_color_manual(values = color_group_combined) +
  scale_fill_manual(values  = color_group_combined) +
  coord_cartesian(xlim = c(0.5, 6.5), ylim = c(-2, 2), expand = FALSE) +
  facet_grid(solution ~ .) +
  force_panelsizes(cols = unit(plt_dims[1] * 1.25, 'cm'), rows = unit(plt_dims[2] * 2/3, 'cm')) +
  theme(panel.spacing.y = unit(0.8, 'lines')) +
  ylab('Z-Score difference') +
  xlab('')

save_pdf(dir_output_f, str_c(fn_stem_f, '.pdf'), 8, 4)
plt_data_f_delta %>% write_csv(str_c(dir_output_f, fn_stem_f, '_data.csv'))
```

```{r eval=FALSE}
# stats: Wilcoxon unpaired per region × solution (control vs vgat_inh, control vs vglut2_inh)
# Bonferroni: p_value × 2 (two comparisons per cell)
loop_regions   <- plt_data_f_delta %>% pull(region)   %>% unique()
loop_solutions <- plt_data_f_delta %>% pull(solution) %>% unique()

combined_result_f <- NULL

for (loop_solution in loop_solutions) {
  for (loop_region in loop_regions) {
    plt_data_wide <- plt_data_f_delta %>%
      filter(solution == loop_solution) %>%
      select(region, subject, group_combined, diff) %>%
      spread(group_combined, diff) %>%
      filter(region == loop_region)

    loop_result <- bind_rows(
      plt_data_wide %>%
        tidy_wilcox_unpaired('control', 'vgat_inh') %>%
        mutate(comparision = 'control_vs_vgat'),
      plt_data_wide %>%
        tidy_wilcox_unpaired('control', 'vglut2_inh') %>%
        mutate(comparision = 'control_vs_vglut2')
    ) %>%
      clean_names() %>%
      mutate(region = loop_region, solution = loop_solution) %>%
      select(solution, region, comparision, everything()) %>%
      mutate(p_value = p_value * 2) %>%
      quick_sig()

    combined_result_f <- bind_rows(combined_result_f, loop_result)
  }
}

combined_result_f %>%
  mutate(region = factor(region, levels = key_regions$region_label)) %>%
  ggplot(aes(region, comparision, label = sig_symbol)) +
  facet_grid(solution ~ .) +
  geom_text()

combined_result_f %>%
  write_csv(str_c(dir_output_f, fn_stem_f, '_stats_ph.csv'))
```

---

## fig04g: fiber placement maps — 3D only (per group, averaged across solutions)
```{r eval=FALSE}
dir_output_g <- str_c(dir_output, 'g/')
fn_stem_g    <- 'inh_access_prelaserbl_placement_vs_deltasummary'

plt_data_g_delta <- df %>%
  filter(time_rel > 0, time_rel < 2) %>%
  group_by(subject, region, stim_id, group_combined, solution) %>%
  summarise(zscore = mean(delta_signal_poly_zscore_blsubdist, na.rm = TRUE), .groups = 'drop') %>%
  spread(stim_id, zscore) %>%
  mutate(diff = lha - no_stim)

plt_data_g_mean <- plt_data_g_delta %>%
  group_by(group_combined, subject, region) %>%
  summarise(diff = mean(diff, na.rm = TRUE), .groups = 'drop') %>% 
  left_join(log_placements %>% select(subject, region = target, hit_ap, hit_ml, hit_dv))

for (loop_group in c('control', 'vgat_inh', 'vglut2_inh')) {
  df_loop      <- plt_data_g_mean %>% filter(group_combined == loop_group)
  var_color    <- 'diff'
  color_limits <- c(-1, 1)

  tryCatch(
    plt_str_3d(
      df           = df_loop,
      var_color    = var_color,
      color_limits = color_limits,
      dir_output   = dir_output_g,
      fn_stem      = str_c(fn_stem_g, '_', loop_group),
      toggle_save  = 1
    ),
    error = function(e) message('plt_str_3d skipped (kaleido): ', conditionMessage(e))
  )
}

plt_data_g_mean %>% write_csv(str_c(dir_output_g, fn_stem_g, '_data.csv'))
```

---

## fig04h: placement × response correlation (AP / ML / DV)
```{r eval=FALSE}
dir_output_h <- str_c(dir_output, 'h/')
fn_stem_h    <- 'inh_access_prelaserbl_placement_vs_deltasummary'

plt_list_h <- plt_corr(
  df            = plt_data_g_mean,
  ylim_all      = c(-2, 2),
  xlim_ap       = c(-3, 0, 3),
  xlim_ml       = c(0, 2, 4),
  xlim_dv       = c(-6, -4, -2),
  var_dep       = 'diff',
  var_dep_label = 'Delta',
  plt_dims      = c(3, 3 * 2/3)
)

plt_list_h[['AP']] +
  plt_list_h[['ML']] +
  plt_list_h[['DV']] +
  plot_layout(nrow = 1, widths = unit(3 * 2/3, 'cm'), heights = unit(4, 'cm'),
              guides = 'collect')

save_pdf(dir_output_h, str_c(fn_stem_h, '_corr.pdf'), 6, 3.5)
plt_list_h[['stats_output']] %>%
  write_csv(str_c(dir_output_h, fn_stem_h, '_corr_stats.csv'))
```

---

# sfig05

## sfig05a: baseline subtraction depiction — 3 panels (acd09, DLS, control)
```{r eval=FALSE}
dir_output_sfig05a <- str_c(dir_output, 'sfig05a/')

# stim_id values: 'lha' / 'no_stim' (raw); lha = '#2baee4', no_stim = 'black'
df_plt_sbj <- read.csv(str_c(dir_data, 'sfig05a_peth_rep.csv'))

# ── panel 1: no baseline subtraction ──────────────────────────────────────────
fn_stem_sfig05a_1 <- 'preprocessing_examplesubject_nobaseline'

plt01 <- df_plt_sbj %>%
  filter(time_rel > -9, time_rel < 12) %>%
  ggplot(aes(time_rel, delta_signal_poly_zscore, color = stim_id)) +
  annotate('rect', xmin = -6, xmax = 9, ymin = -Inf, ymax = Inf,
           alpha = 1/8, fill = '#2baee4') +
  annotate('rect', xmin = 0,  xmax = 3, ymin = -Inf, ymax = Inf,
           alpha = 1/3, fill = 'darkgrey') +
  geom_line() +
  facet_grid(group_combined ~ subject) +
  ggtitle('No baseline subtraction') +
  ylab('Z-score') +
  xlab('Time relative to access start (s)') +
  theme_ag01() +
  scale_color_manual(values = c('#2baee4', 'black')) +
  force_panelsizes(rows = unit(2.5, 'cm'), cols = unit(2.5, 'cm'))

plt01 %>%
  add_scale_bar(origin = c(-9, -0.5), x_len = 1, y_len = 1)

save_pdf(dir_output_sfig05a, str_c(fn_stem_sfig05a_1, '.pdf'), 4, 4)
df_plt_sbj %>%
  select(subject, group_combined, region, stim_id, time_rel,
         delta_signal_poly_zscore) %>%
  write_csv(str_c(dir_output_sfig05a, fn_stem_sfig05a_1, '_data.csv'))

# ── panel 2: pre-laser baseline subtraction (blsubdist) ───────────────────────
fn_stem_sfig05a_2 <- 'preprocessing_examplesubject_prelaser'

plt02 <- df_plt_sbj %>%
  filter(time_rel > -9, time_rel < 12) %>%
  ggplot(aes(time_rel, delta_signal_poly_zscore_blsubdist, color = stim_id)) +
  annotate('rect', xmin = -6, xmax = 9, ymin = -Inf, ymax = Inf,
           alpha = 1/8, fill = '#2baee4') +
  annotate('rect', xmin = 0,  xmax = 3, ymin = -Inf, ymax = Inf,
           alpha = 1/3, fill = 'darkgrey') +
  geom_line() +
  facet_grid(group_combined ~ subject) +
  ggtitle('Pre-laser baseline subtraction') +
  ylab('Z-score') +
  xlab('Time relative to access start (s)') +
  theme_ag01() +
  scale_color_manual(values = c('#2baee4', 'black')) +
  force_panelsizes(rows = unit(2.5, 'cm'), cols = unit(2.5, 'cm'))

plt02 %>%
  add_scale_bar(origin = c(-9, -0.5), x_len = 1, y_len = 1)

save_pdf(dir_output_sfig05a, str_c(fn_stem_sfig05a_2, '.pdf'), 4, 4)
df_plt_sbj %>%
  select(subject, group_combined, region, stim_id, time_rel,
         delta_signal_poly_zscore_blsubdist) %>%
  write_csv(str_c(dir_output_sfig05a, fn_stem_sfig05a_2, '_data.csv'))

# ── panel 3: pre-access baseline subtraction (blsub) ─────────────────────────
fn_stem_sfig05a_3 <- 'preprocessing_examplesubject_preaccess'

plt03 <- df_plt_sbj %>%
  filter(time_rel > -9, time_rel < 12) %>%
  ggplot(aes(time_rel, delta_signal_poly_zscore_blsub, color = stim_id)) +
  annotate('rect', xmin = -6, xmax = 9, ymin = -Inf, ymax = Inf,
           alpha = 1/8, fill = '#2baee4') +
  annotate('rect', xmin = 0,  xmax = 3, ymin = -Inf, ymax = Inf,
           alpha = 1/3, fill = 'darkgrey') +
  geom_line() +
  facet_grid(group_combined ~ subject) +
  ggtitle('Pre-access baseline subtraction') +
  ylab('Z-score') +
  xlab('Time relative to access start (s)') +
  theme_ag01() +
  scale_color_manual(values = c('#2baee4', 'black')) +
  force_panelsizes(rows = unit(2.5, 'cm'), cols = unit(2.5, 'cm'))

plt03 %>%
  add_scale_bar(origin = c(-9, -0.5), x_len = 1, y_len = 1)

save_pdf(dir_output_sfig05a, str_c(fn_stem_sfig05a_3, '.pdf'), 4, 4)
df_plt_sbj %>%
  select(subject, group_combined, region, stim_id, time_rel,
         delta_signal_poly_zscore_blsub) %>%
  write_csv(str_c(dir_output_sfig05a, fn_stem_sfig05a_3, '_data.csv'))
```

---

## sfig05b: inhibition baseline effect — group mean trace (−9 to 0 s, distant baseline)
```{r eval=FALSE}
dir_output_sfig05b <- str_c(dir_output, 'sfig05b/')
fn_stem_sfig05b  <- 'inh_baseline_prelaserbl_trace'

plt_data_sfig05b <- df %>%
  filter(time_rel >= -9, time_rel <= 0) %>%
  select(group_combined, subject, region, solution, stim_id, time_rel,
         zscore = delta_signal_poly_zscore_blsubdist) %>%
  spread(stim_id, zscore) %>%
  mutate(diff = lha - no_stim) %>%
  group_by(group_combined, region, solution, time_rel) %>%
  summarise(
    diff_sem = sd(diff, na.rm = TRUE) / sqrt(sum(!is.na(diff))),
    diff     = mean(diff, na.rm = TRUE),
    .groups  = 'drop'
  ) %>%
  mutate(solution = case_when(
    solution == 'nacl100' ~ '1M NaCl',
    solution == 'water'   ~ 'Water',
    TRUE                  ~ solution
  ))

plt <- plt_data_sfig05b %>%
  ggplot(aes(time_rel, diff, color = region, fill = region)) +
  annotate('rect', xmin = -6, xmax = 0, ymin = -Inf, ymax = Inf,
           alpha = 1/8, fill = '#2baee4') +
  geom_hline(yintercept = 0, color = 'darkgrey', size = 0.5) +
  geom_ribbon(aes(ymax = diff + diff_sem, ymin = diff - diff_sem),
              color = NA, alpha = 1/3) +
  geom_line() +
  facet_grid(solution ~ group_combined) +
  theme_ag01() +
  scale_color_manual(values = color_values_regions_da) +
  scale_fill_manual(values  = color_values_regions_da)

plt <- plt %>%
  add_scale_bar(origin = c(-9, -1), x_len = 1, y_len = 1)

plt +
  force_panelsizes(cols = unit(4.3553, 'cm'), rows = unit(2.5955, 'cm'))

save_pdf(dir_output_sfig05b, str_c(fn_stem_sfig05b, '.pdf'), 8, 4)
plt_data_sfig05b %>% write_csv(str_c(dir_output_sfig05b, fn_stem_sfig05b, '_data.csv'))
```

---

## sfig05c: inhibition baseline effect — summary bar (−5 to 0 s, distant baseline)
```{r eval=FALSE}
dir_output_sfig05c <- str_c(dir_output, 'sfig05c/')
fn_stem_sfig05c    <- 'inh_baseline_region_vs_difference'

# no solution grouping — averaged across solutions
plt_data_sfig05c <- df %>%
  filter(time_rel > -5, time_rel < 0) %>%
  group_by(subject, region, stim_id, group_combined) %>%
  summarise(zscore = mean(delta_signal_poly_zscore_blsubdist, na.rm = TRUE), .groups = 'drop') %>%
  spread(stim_id, zscore) %>%
  mutate(diff = lha - no_stim)

plt_data_sfig05c %>%
  ggplot(aes(region, diff, color = group_combined, fill = group_combined)) +
  geom_hline(yintercept = 0, alpha = 1/3) +
  stat_summary(fun.data = 'mean_se', geom = 'errorbar', aes(group = group_combined),
               width = 0.3, position = position_dodge(width = 0.75)) +
  stat_summary(fun = 'mean', geom = 'bar', color = NA, aes(group = group_combined),
               alpha = 1/2, width = 0.6, position = position_dodge(width = 0.75)) +
  geom_jitter(shape = 21, color = 'white', size = 1.5, stroke = 0.25,
              position = position_jitterdodge(jitter.width = 0.04, dodge.width = 0.75)) +
  theme_ag01() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3)) +
  scale_color_manual(values = color_group_combined) +
  scale_fill_manual(values  = color_group_combined) +
  coord_cartesian(xlim = c(0.5, 6.5), ylim = c(-2, 1.5), expand = F) +
  scale_y_continuous(breaks = seq(-2, 1.5, 0.5)) +
  force_panelsizes(cols = unit(plt_dims[1] * 1.25, 'cm'), rows = unit(4.1758, 'cm')) +
  ylab('Z-Score difference') +
  xlab('')

save_pdf(dir_output_sfig05c, str_c(fn_stem_sfig05c, '.pdf'), 4, 4)
plt_data_sfig05c %>% write_csv(str_c(dir_output_sfig05c, fn_stem_sfig05c, '_data.csv'))
```

```{r eval=FALSE}
# stats: Wilcoxon unpaired per region (no solution split; control vs vgat_inh, control vs vglut2_inh)
loop_regions <- plt_data_sfig05c %>% pull(region) %>% unique()

combined_result_sfig05c <- NULL

for (loop_region in loop_regions) {
  plt_data_wide <- plt_data_sfig05c %>%
    select(region, subject, group_combined, diff) %>%
    spread(group_combined, diff) %>%
    filter(region == loop_region)

  loop_result <- bind_rows(
    plt_data_wide %>%
      tidy_wilcox_unpaired('control', 'vgat_inh') %>%
      mutate(comparision = 'control_vs_vgat'),
    plt_data_wide %>%
      tidy_wilcox_unpaired('control', 'vglut2_inh') %>%
      mutate(comparision = 'control_vs_vglut2')
  ) %>%
    clean_names() %>%
    mutate(region = loop_region) %>%
    select(region, comparision, everything()) %>%
    mutate(p_value = p_value * 2) %>%
    quick_sig()

  combined_result_sfig05c <- bind_rows(combined_result_sfig05c, loop_result)
}

combined_result_sfig05c %>%
  mutate(region = factor(region, levels = key_regions$region_label)) %>%
  ggplot(aes(region, comparision, label = sig_symbol)) +
  geom_text()

combined_result_sfig05c %>%
  write_csv(str_c(dir_output_sfig05c, fn_stem_sfig05c, '_stats_ph.csv'))
```

---

## sfig05d: FP trace — consumption effect, proximal baseline (−3 to 6 s)
```{r eval=FALSE}
dir_output_sfig05d <- str_c(dir_output, 'sfig05d/')
fn_stem_sfig05d    <- 'inh_access_preaccessbl_trace'

plt_data_sfig05d <- df %>%
  filter(time_rel >= -3, time_rel <= 6) %>%
  select(group_combined, subject, region, solution, stim_id, time_rel,
         zscore = delta_signal_poly_zscore_blsub) %>%
  spread(stim_id, zscore) %>%
  mutate(diff = lha - no_stim) %>%
  group_by(group_combined, region, solution, time_rel) %>%
  summarise(
    diff_sem = sd(diff, na.rm = TRUE) / sqrt(sum(!is.na(diff))),
    diff     = mean(diff, na.rm = TRUE),
    .groups  = 'drop'
  ) %>%
  mutate(solution = case_when(
    solution == 'nacl100' ~ '1M NaCl',
    solution == 'water'   ~ 'Water',
    TRUE                  ~ solution
  ))

plt <- plt_data_sfig05d %>%
  ggplot(aes(time_rel, diff, color = region, fill = region)) +
  annotate('rect', xmin = -3, xmax = 6, ymin = -Inf, ymax = Inf,
           alpha = 1/8, fill = '#2baee4') +
  annotate('rect', xmin = 0,  xmax = 3, ymin = -Inf, ymax = Inf,
           alpha = 1/3, fill = 'darkgrey') +
  geom_hline(yintercept = 0, color = 'darkgrey', size = 0.5) +
  geom_ribbon(aes(ymax = diff + diff_sem, ymin = diff - diff_sem),
              color = NA, alpha = 1/3) +
  geom_line() +
  facet_grid(solution ~ group_combined) +
  theme_ag01() +
  scale_color_manual(values = color_values_regions_da) +
  scale_fill_manual(values  = color_values_regions_da)

plt <- plt %>%
  add_scale_bar(origin = c(-3, -1), x_len = 1, y_len = 1)

plt +
  force_panelsizes(cols = unit(4.3553, 'cm'), rows = unit(2.5955, 'cm'))

save_pdf(dir_output_sfig05d, str_c(fn_stem_sfig05d, '.pdf'), 8, 4)
plt_data_sfig05d %>% write_csv(str_c(dir_output_sfig05d, fn_stem_sfig05d, '_data.csv'))
```

---

## sfig05e: FP summary bar — consumption effect, proximal baseline (0–2 s)
```{r eval=FALSE}
dir_output_sfig05e <- str_c(dir_output, 'sfig05e/')
fn_stem_sfig05e    <- 'inh_access_preaccessbl_region_vs_difference'

plt_data_sfig05e_summary <- df %>%
  filter(time_rel > 0, time_rel < 2) %>%
  group_by(subject, region, stim_id, group_combined, solution) %>%
  summarise(zscore = mean(delta_signal_poly_zscore_blsub, na.rm = TRUE), .groups = 'drop')

plt_data_sfig05e <- plt_data_sfig05e_summary %>%
  spread(stim_id, zscore) %>%
  mutate(diff = lha - no_stim) %>%
  mutate(solution = case_when(
    solution == 'nacl100' ~ '1M NaCl',
    solution == 'water'   ~ 'Water',
    TRUE                  ~ solution
  ))

plt <- plt_data_sfig05e %>%
  ggplot(aes(region, diff, color = group_combined, fill = group_combined)) +
  geom_hline(yintercept = 0, alpha = 1/3) +
  stat_summary(fun.data = 'mean_se', geom = 'errorbar', aes(group = group_combined),
               width = 0.3, position = position_dodge(width = 0.75)) +
  stat_summary(fun = 'mean', geom = 'bar', color = NA, aes(group = group_combined),
               alpha = 1/2, width = 0.6, position = position_dodge(width = 0.75)) +
  theme_ag01() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3)) +
  scale_color_manual(values = color_group_combined) +
  scale_fill_manual(values  = color_group_combined) +
  facet_grid(solution ~ .) +
  force_panelsizes(cols = unit(plt_dims[1] * 1.25, 'cm'), rows = unit(plt_dims[2] * 2/3, 'cm')) +
  theme(panel.spacing.y = unit(0.8, 'lines')) +
  ylab('Z-Score difference') +
  xlab('')

plt +
  geom_jitter(shape = 21, color = 'white', size = 1.5, stroke = 0.25,
              position = position_jitterdodge(jitter.width = 0.04, dodge.width = 0.75)) +
  coord_cartesian(xlim = c(0.5, 6.5), ylim = c(-1.5, 1), expand = F)

save_pdf(dir_output_sfig05e, str_c(fn_stem_sfig05e, '.pdf'), 4, 4)
plt_data_sfig05e %>% write_csv(str_c(dir_output_sfig05e, fn_stem_sfig05e, '_data.csv'))
```

```{r eval=FALSE}
# stats: Wilcoxon unpaired per region × solution (control vs vgat_inh, control vs vglut2_inh)
loop_regions   <- plt_data_sfig05e %>% pull(region)   %>% unique()
loop_solutions <- plt_data_sfig05e %>% pull(solution) %>% unique()

combined_result_sfig05e <- NULL

for (loop_solution in loop_solutions) {
  for (loop_region in loop_regions) {
    plt_data_wide <- plt_data_sfig05e %>%
      filter(solution == loop_solution) %>%
      select(region, subject, group_combined, diff) %>%
      spread(group_combined, diff) %>%
      filter(region == loop_region)

    loop_result <- bind_rows(
      plt_data_wide %>%
        tidy_wilcox_unpaired('control', 'vgat_inh') %>%
        mutate(comparision = 'control_vs_vgat'),
      plt_data_wide %>%
        tidy_wilcox_unpaired('control', 'vglut2_inh') %>%
        mutate(comparision = 'control_vs_vglut2')
    ) %>%
      clean_names() %>%
      mutate(region = loop_region, solution = loop_solution) %>%
      select(solution, region, comparision, everything()) %>%
      mutate(p_value = p_value * 2) %>%
      quick_sig()

    combined_result_sfig05e <- bind_rows(combined_result_sfig05e, loop_result)
  }
}

combined_result_sfig05e %>%
  mutate(region = factor(region, levels = key_regions$region_label)) %>%
  ggplot(aes(region, comparision, label = sig_symbol)) +
  facet_grid(solution ~ .) +
  geom_text()

combined_result_sfig05e %>%
  write_csv(str_c(dir_output_sfig05e, fn_stem_sfig05e, '_stats_ph.csv'))
```
