---
title: "fig08"
author: "adam gordon-fennell"
date: '2026-06-15'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = normalizePath('../'))
```

# setup
## libraries
```{r}
library(tidyverse)
library(afex)
library(emmeans)
library(janitor)
library(broom)
library(ggh4x)
library(pals)
library(patchwork)
library(DescTools)
library(arrow)
library(readxl)

source('./functions/params.R')
source('./functions/theme.R')
source('./functions/general.R')
source('./functions/r_general.R')
source('./functions/r_plots.R')
source('./functions/stats.R')
source('./functions/analysis_peth.R')
```

## directories
```{r}
dir_data   <- './data/fig08/'
dir_output <- './analysis_and_plots/fig08/'

dir.create(dir_output, recursive = TRUE, showWarnings = FALSE)
```

## local functions
```{r}
get_regionstim_label <- function(df){
  join_regionstim_label <- tibble(
    regionstim       = c('vta', 'nac', 'dms', 'dls', 'ts', 'all'),
    regionstim_label = c('VTA', 'NAcCC', 'DMS', 'DLS', 'TS', 'All STR')
  )
  df %>%
    left_join(join_regionstim_label, by = c('regionstim')) %>%
    mutate(regionstim_label = factor(regionstim_label, levels = join_regionstim_label$regionstim_label))
}
```

---

# fa laser [fig08A-D]

```{r eval=FALSE}
color_laserstate <- c('#808080', '#00aeef')  # off=grey, on=blue

plt_regions <- c('vta', 'nac', 'dms', 'dls', 'ts', 'all')
plt_vars    <- c('mean_sesssion_lick_count', 'mean_bout_lick_count', 'mean_bout_n')

summary_bout_session <- read.csv(str_c(dir_data, 'free_access_summary_data.csv')) %>%
  mutate(regionstim = factor(regionstim, levels = plt_regions))
```

## fig08C: representative subject
### left — cumulative session lick
```{r eval=FALSE}
dir_output_c <- str_c(dir_output, 'c/')
dir.create(dir_output_c, recursive = TRUE, showWarnings = FALSE)

plt_data_c_session <- read.csv(str_c(dir_data, 'free_access_rep_sbj_cummulative_session.csv'))

shade_df <- tibble(
  xmin = seq(0, 36, by = 4),
  xmax = seq(2, 38, by = 4)
)

plt_data_c_session %>%
  ggplot(aes(event_ts / 1000 / 60, cummulative_lick / 1000, color = blockname, group = blockname)) +
  geom_rect(data = shade_df, aes(xmin = xmin, xmax = xmax, ymin = 0, ymax = 2.5),
            inherit.aes = FALSE, fill = '#0075bf', alpha = 0.2) +
  geom_line() +
  theme_ag01() +
  scale_color_manual(values = c('#0075bf', '#808285')) +
  xlab('Time (min)') +
  ylab('Cumulative lick count (x1k)') +
  coord_cartesian(xlim = c(0, 40), ylim = c(0, 2.5), expand = F, clip = 'off') +
  force_panelsizes(rows = unit(2, 'cm'), cols = unit(2, 'cm'))

save_pdf(dir_output_c, 'rep_sbj_cummulative_lick.pdf', h = 4, w = 4)
```

### right — cumulative block lick
```{r eval=FALSE}
plt_data_c_block <- read.csv(str_c(dir_data, 'free_access_rep_sbj_cummulative_block.csv'))

plt <- plt_data_c_block %>%
  mutate(time_rel = event_ts - tm_block_start) %>%
  ggplot(aes(time_rel / 1000 / 60, cummulative_lick_block, color = blockname)) +
  geom_line(aes(group = interaction(block_num, blockname))) +
  facet_grid(. ~ interaction(laser_state, blockname)) +
  scale_color_manual(values = c('#0075bf', '#808285')) +
  theme_ag01() +
  force_panelsizes(rows = unit(2, 'cm'), cols = unit(1, 'cm'))

plt %>%
  add_scale_bar(c(-0.2, -20), 1, 100)

save_pdf(dir_output_c, 'rep_sbj_cummulative_lick_block.pdf', h = 4, w = 12)
```

---

## fig08D: summary — lick count and bout structure
```{r eval=FALSE}
dir_output_d <- str_c(dir_output, 'd/')
dir.create(dir_output_d, recursive = TRUE, showWarnings = FALSE)

plt_n_stats_licktriggered_fa_line <- function(summary_bout_session, plt_var, plt_region, dir_output){

  prefix <- str_c(plt_region, '_', plt_var)

  df <- summary_bout_session %>%
    filter(regionstim == plt_region)

  plt_line <- df %>%
    ggplot(aes(laser_state, !!as.name(plt_var), color = group)) +
    annotate("rect", xmin = 1.8, xmax = 2.2, ymin = -Inf, ymax = Inf, fill = color_laserstate[2], alpha = 1/3) +
    geom_line(aes(group = subject), alpha = 1/3) +
    stat_summary(fun = 'mean', geom = 'line', aes(group = group)) +
    stat_summary(fun.data = 'mean_se', geom = 'errorbar', aes(group = group), width = 0) +
    theme_ag01() +
    scale_color_manual(values = c('#0075bf', '#808285'), guide = "none") +
    facet_grid(regionstim ~ group)

  plt_line <- plt_line %>%
    remove_x_all()

  plt_line_export <- plt_line +
    theme(panel.spacing = unit(0.1, "cm")) +
    force_panelsizes(rows = unit(1.0, 'cm'), cols = unit(0.5, 'cm'))

  ggsave(
    filename = str_c(dir_output, prefix, '_plt.pdf'),
    plot     = plt_line_export,
    width    = 2, height = 3, units = 'in', dpi = 300, useDingbats = FALSE
  )

  sbj_count <- summary_bout_session %>%
    filter(regionstim == plt_region) %>%
    select(group, subject) %>%
    unique() %>%
    group_by(group) %>%
    summarise(n_sbj = n())

  if(nrow(sbj_count) > 1 & min(sbj_count$n_sbj) > 1){
    stats_summary <- aov_rm_one_between_one_within(
      df            = df,
      dir_output    = dir_output,
      prefix        = prefix,
      var_id        = 'subject',
      var_dependent = plt_var,
      var_between   = 'group',
      var_within    = 'laser_state'
    )
  } else {
    stats_summary <- replicate(3, data.frame(), simplify = FALSE)
  }

  return(list(plt = plt_line, stats = stats_summary))
}
```

```{r eval=FALSE}
nested <- map(plt_regions, function(reg) {
  map(plt_vars, function(v) {
    x <- plt_n_stats_licktriggered_fa_line(summary_bout_session, v, reg, dir_output_d)
    list(
      plt        = x$plt,
      stats_main = x$stats[[2]] %>% mutate(region = reg, var = v) %>% select(region, var, everything()),
      stats_hsd  = x$stats[[3]] %>% mutate(region = reg, var = v) %>% select(region, var, everything())
    )
  }) |> set_names(plt_vars)
}) |> set_names(plt_regions)
```

```{r eval=FALSE}
for(plt_var in plt_vars){
  for(plt_region in plt_regions){

    plt_loop <- nested[[plt_region]][[plt_var]]$plt
    hsd_loop <- nested[[plt_region]][[plt_var]]$stats_hsd

    y_range <- case_when(
      plt_var == 'mean_sesssion_lick_count' ~ c(0, 2500),
      plt_var == 'mean_bout_lick_count'     ~ c(0, 20),
      plt_var == 'mean_bout_n'              ~ c(0, 400)
    )

    plt_loop <- plt_loop +
      coord_cartesian(xlim = c(0.8, 2.2), ylim = y_range, expand = F, clip = 'off')

    if(plt_region != plt_regions[[1]]){
      plt_loop <- plt_loop %>% remove_y_all()
    }

    if(plt_var == plt_vars[[1]]){
      title <- case_when(
        plt_region == 'vta' ~ 'VTA',
        plt_region == 'nac' ~ 'NAcCC',
        plt_region == 'dms' ~ 'DMS',
        plt_region == 'dls' ~ 'DLS',
        plt_region == 'ts'  ~ 'TS',
        plt_region == 'all' ~ 'All STR'
      )
      plt_loop <- plt_loop + ggtitle(title)
    }

    plt_loop <- plt_loop + theme(strip.text.y = element_blank())

    if(plt_var != plt_vars[[1]]){
      plt_loop <- plt_loop + theme(strip.text.x = element_blank())
    } else {
      plt_loop <- plt_loop + theme(
        strip.text         = element_text(size = 6),
        strip.text.x       = element_text(margin = margin(t = 5, b = 5)),
        panel.spacing.x    = unit(1, "lines"),
        strip.background   = element_blank(),
        strip.clip         = "off"
      )
    }

    if(plt_region == plt_regions[[1]]){
      str_ylab <- case_when(
        plt_var == 'mean_sesssion_lick_count' ~ 'Session lick count',
        plt_var == 'mean_bout_lick_count'     ~ 'Bout lick count',
        plt_var == 'mean_bout_n'              ~ 'Bout count'
      )
      plt_loop <- plt_loop + ylab(str_ylab)
    } else {
      plt_loop <- plt_loop + ylab('')
    }

    if(nrow(hsd_loop) > 0){
      annotation_within <- hsd_loop %>%
        filter(contrast1_between == contrast2_between) %>%
        mutate(group = contrast1_between) %>%
        mutate(sig_symbol = ifelse(sig_symbol == 'n.s.', '', sig_symbol)) %>%
        select(group, sig_symbol)

      y_pos <- y_range[2] * 0.92

      plt_loop <- plt_loop +
        geom_text(data = annotation_within, aes(label = sig_symbol), x = 1.5, y = y_pos, size = 4)
    }

    if(plt_region == plt_regions[[1]] & plt_var == plt_vars[[1]]){
      plt_combined <- plt_loop
    } else {
      plt_combined <- plt_combined + plt_loop
    }
  }
}

plt_combined +
  plot_layout(
    ncol    = length(plt_regions),
    nrow    = length(plt_vars),
    widths  = unit(1, 'cm'),
    heights = unit(1.5, 'cm')
  )

save_pdf(dir_output_d, 'analysis_summary.pdf', 6, 6)
```

---

## summation analysis [text only — no paper figure]
```{r eval=FALSE}
summary_bout_session_summation <- summary_bout_session %>%
  filter(!subject %in% c('aco07')) %>% # a fiber was excluded -> excluded for summation
  filter(regionstim %in% c('nac', 'dms', 'dls', 'ts')) %>%
  select(-regionstim) %>%
  group_by(subject, group, laser_state) %>%
  summarise_all(.funs = 'mean', .groups = drop) %>%
  mutate(regionstim = 'summation') %>%
  bind_rows(summary_bout_session, .)

summary_bout_session_summation_delta <- summary_bout_session_summation %>%
  gather(var_id, var_value, mean_sesssion_lick_count:mean_bout_n) %>%
  select(subject, group, regionstim, laser_state, var_id, var_value) %>%
  spread(laser_state, var_value) %>%
  mutate(delta = on - off)
```

```{r eval=FALSE}
dir_output_summation <- str_c(dir_output, 'summation/')
dir.create(dir_output_summation, recursive = TRUE, showWarnings = FALSE)


plt_data_sum <- summary_bout_session_summation %>%
  filter(group == 'ChR2') %>%
  filter(regionstim %in% c('all', 'summation')) 


plt_id <- 'fa_stim_all_vs_summation_delta'

plt_data_sum2 <- plt_data_sum %>%
  select(subject, laser_state, regionstim, mean_sesssion_lick_count) %>%
  spread(laser_state, mean_sesssion_lick_count) %>%
  mutate(delta = on - off)

plt_data_sum2 %>%
  mutate(regionstim = ifelse(regionstim == 'all', 'All STR', 'Summation')) %>%
  mutate(regionstim = factor(regionstim, levels = c('All STR', 'Summation'))) %>%
  ggplot(aes(regionstim, delta, group = 1)) +
  geom_hline(yintercept = 0, linewidth = 1/2, color = 'darkgrey') +
  geom_line(aes(group = subject), alpha = 1/2) +
  stat_summary(fun = 'mean', geom = 'line') +
  stat_summary(fun.data = 'mean_se', geom = 'errorbar', width = 0) +
  theme_ag01() +
  coord_cartesian(xlim = c(0.8, 2.2), ylim = c(-500, 500), expand = F, clip = 'off') +
  theme(
    axis.text.x  = element_text(angle = 45, hjust = 1, vjust = 1),
    axis.title.x = element_blank()
  ) +
  ylab('Delta licking (on - off)') +
  force_panelsizes(rows = unit(3, 'cm'), cols = unit(1, 'cm'))

save_pdf(dir_output_summation, 'delta_licking.pdf', h = 4, w = 4)

plt_data_sum2 %>%
  select(subject, regionstim, delta) %>%
  spread(regionstim, delta) %>%
  tidy_ttest_paired(dir_output_summation, 'delta_licking', 'all', 'summation')

mean_summary <- plt_data_sum2 %>%
  group_by(regionstim) %>%
  summarise(
    delta_sem = sd(delta)/sqrt(n()),
    delta_mean = delta %>% mean()
  )

mean_summary %>% write_csv(str_c(dir_output_summation, 'delta_licking_means.csv'))
```

---

# brief access laser [fig08E-H]

```{r eval=FALSE}
color_laserstate <- c('#00aeef', '#808080')  # laser=blue, no_laser=grey

plt_regions <- c('vta', 'nac', 'dms', 'dls', 'ts', 'all')
plt_vars    <- c('trial_lick_count', 'trial_lick_prop')

summary_trial_laser <- read.csv(str_c(dir_data, 'brief_access_summary_data.csv')) %>%
  mutate(laser_state = factor(laser_state, levels = c('no_laser', 'laser'))) %>%
  mutate(regionstim  = factor(regionstim,  levels = plt_regions))
```

## fig08F: representative subject raster
```{r eval=FALSE}
dir_output_f <- str_c(dir_output, 'f/')
dir.create(dir_output_f, recursive = TRUE, showWarnings = FALSE)

plt_data_f <- read.csv(str_c(dir_data, 'brief_access_rep_sbj_raster_data.csv'))

shade_df <- tibble(
  ymin = seq(10, 90,  by = 20),
  ymax = seq(20, 100, by = 20)
)

plt <- plt_data_f %>%
  mutate(event_unique = row_number()) %>%
  mutate(trial_num  = trial_num - 1) %>%
  mutate(y_dummy    = trial_num + 1) %>%
  gather('id', 'y_pos', trial_num, y_dummy) %>%
  ggplot(aes(event_ts_rel, y_pos, color = group, group = event_unique)) +
  geom_rect(data = shade_df, aes(ymin = ymin, ymax = ymax, xmin = 0, xmax = 3000),
            inherit.aes = FALSE, fill = '#0075bf', alpha = 0.2) +
  geom_line() +
  scale_color_manual(values = color_laserstate) +
  facet_grid(. ~ group) +
  theme_ag01() +
  coord_cartesian(xlim = c(0, 3000), ylim = c(0, 100), expand = F, clip = 'off') +
  force_panelsizes(rows = unit(6, 'cm'), cols = unit(3, 'cm'))

plt %>%
  add_scale_bar(c(-100, -5), 1000, 10)

save_pdf(dir_output_f, 'rep_sbj_raster.pdf', h = 4, w = 12)
```

---

## fig08G: summary — trial lick count and lick proportion
```{r eval=FALSE}
dir_output_g <- str_c(dir_output, 'g/')
dir.create(dir_output_g, recursive = TRUE, showWarnings = FALSE)

plt_n_stats_licktriggered_ba_line <- function(summary_trial_laser, plt_var, plt_region, dir_output){

  prefix <- str_c(plt_region, '_', plt_var)

  df <- summary_trial_laser %>%
    mutate(laser_state = factor(laser_state, levels = c('no_laser', 'laser'))) %>%
    filter(regionstim == plt_region)

  plt_line <- df %>%
    ggplot(aes(laser_state, !!as.name(plt_var), color = group)) +
    annotate("rect", xmin = 1.8, xmax = 2.2, ymin = -Inf, ymax = Inf, fill = color_laserstate[1], alpha = 1/3) +
    geom_line(aes(group = subject), size = 1/2, alpha = 1/3) +
    stat_summary(fun = 'mean', geom = 'line', size = 1/2, aes(group = group)) +
    stat_summary(fun.data = 'mean_se', geom = 'errorbar', size = 1/2, aes(group = group), width = 0) +
    scale_color_manual(values = c('#0075bf', '#808285'), guide = "none") +
    theme_ag01() +
    facet_grid(regionstim ~ group)

  plt_line_export <- plt_line +
    force_panelsizes(rows = unit(3, 'cm'), cols = unit(0.5, 'cm'))

  ggsave(
    filename = str_c(dir_output, prefix, '_plt.pdf'),
    plot     = plt_line_export,
    width    = 2, height = 3, units = 'in', dpi = 300, useDingbats = FALSE
  )

  sbj_count <- summary_trial_laser %>%
    filter(regionstim == plt_region) %>%
    select(group, subject) %>%
    unique() %>%
    group_by(group) %>%
    summarise(n_sbj = n())

  if(nrow(sbj_count) > 1 & min(sbj_count$n_sbj) > 1){
    stats_summary <- aov_rm_one_between_one_within(
      df            = df,
      dir_output    = dir_output,
      prefix        = prefix,
      var_id        = 'subject',
      var_dependent = plt_var,
      var_between   = 'group',
      var_within    = 'laser_state'
    )
  } else {
    stats_summary <- replicate(3, data.frame(), simplify = FALSE)
  }

  return(list(plt = plt_line, stats = stats_summary))
}
```

```{r eval=FALSE}
nested <- map(plt_regions, function(reg) {
  map(plt_vars, function(v) {
    x <- plt_n_stats_licktriggered_ba_line(summary_trial_laser, v, reg, dir_output_g)
    list(
      plt        = x$plt,
      stats_main = x$stats[[2]] %>% mutate(region = reg, var = v) %>% select(region, var, everything()),
      stats_hsd  = x$stats[[3]] %>% mutate(region = reg, var = v) %>% select(region, var, everything())
    )
  }) |> set_names(plt_vars)
}) |> set_names(plt_regions)
```

```{r eval=FALSE}
for(plt_var in plt_vars){
  for(plt_region in plt_regions){

    plt_loop <- nested[[plt_region]][[plt_var]]$plt
    hsd_loop <- nested[[plt_region]][[plt_var]]$stats_hsd

    y_range <- case_when(
      plt_var == 'trial_lick_count' ~ c(0, 20),
      plt_var == 'trial_lick_prop'  ~ c(0, 1)
    )

    plt_loop <- plt_loop +
      coord_cartesian(xlim = c(0.8, 2.2), ylim = y_range, expand = F)

    if(plt_region != plt_regions[[1]]){
      plt_loop <- plt_loop %>% remove_y_all()
    }

    if(plt_var == plt_vars[[1]]){
      title <- case_when(
        plt_region == 'vta' ~ 'VTA',
        plt_region == 'nac' ~ 'NAcCC',
        plt_region == 'dms' ~ 'DMS',
        plt_region == 'dls' ~ 'DLS',
        plt_region == 'ts'  ~ 'TS',
        plt_region == 'all' ~ 'STR'
      )
      plt_loop <- plt_loop + ggtitle(title)
    }

    plt_loop <- plt_loop + theme(strip.text.y = element_blank())

    if(plt_var != plt_vars[[1]]){
      plt_loop <- plt_loop + theme(strip.text.x = element_blank())
    } else {
      plt_loop <- plt_loop + theme(
        strip.text         = element_text(size = 6),
        strip.text.x       = element_text(margin = margin(t = 5, b = 5)),
        panel.spacing.x    = unit(1, "lines"),
        strip.background   = element_blank(),
        strip.clip         = "off"
      )
    }

    if(plt_region == plt_regions[[1]]){
      str_ylab <- case_when(
        plt_var == 'trial_lick_count' ~ 'Trial lick count',
        plt_var == 'trial_lick_prop'  ~ 'Proportion of trials\nwith lick'
      )
      plt_loop <- plt_loop + ylab(str_ylab)
    } else {
      plt_loop <- plt_loop + ylab('')
    }

    if(nrow(hsd_loop) > 0){
      annotation_within <- hsd_loop %>%
        filter(contrast1_between == contrast2_between) %>%
        mutate(group = contrast1_between) %>%
        mutate(sig_symbol = ifelse(sig_symbol == 'n.s.', '', sig_symbol)) %>%
        select(group, sig_symbol)

      y_pos <- y_range[2] * 0.92

      plt_loop <- plt_loop +
        geom_text(data = annotation_within, aes(label = sig_symbol), x = 1.5, y = y_pos, size = 4)
      
      plt_loop <- plt_loop %>%
        remove_x_all()
    }

    if(plt_region == plt_regions[[1]] & plt_var == plt_vars[[1]]){
      plt_combined <- plt_loop
    } else {
      plt_combined <- plt_combined + plt_loop
    }
  }
}

plt_combined +
  plot_layout(
    ncol    = length(plt_regions),
    nrow    = length(plt_vars),
    widths  = unit(1, 'cm'),
    heights = unit(1.5, 'cm'),
    guides  = 'collect'
  )

save_pdf(dir_output_g, 'analysis_summary.pdf', 12, 6)
```

---

## fig08H: change over block — P(lick)
```{r eval=FALSE}
dir_output_h <- str_c(dir_output, 'h/')
dir.create(dir_output_h, recursive = TRUE, showWarnings = FALSE)

regionstim_levels_h <- c('VTA', 'NAcCC', 'DMS', 'DLS', 'TS', 'STR')

df_summary <- read.csv(str_c(dir_data, 'brief_access_trial_data.csv')) %>%
  rename(trial_lick = p_lick) %>%
  mutate(regionstim = factor(regionstim, levels = regionstim_levels_h))
```

```{r eval=FALSE}
# [fig08h]
df_summary %>%
  ggplot(aes(trial_num_block, trial_lick, color = group, fill = group, alpha = laser_state)) +
  stat_summary(fun = 'mean', geom = 'line', aes(group = interaction(group, laser_state))) +
  stat_summary(fun.data = 'mean_se', geom = 'errorbar', aes(group = interaction(group, laser_state)), width = 0) +
  facet_grid(group ~ regionstim) +
  scale_color_manual(values = c('#0075bf', '#808285')) +
  scale_fill_manual(values  = c('#0075bf', '#808285')) +
  scale_alpha_discrete(range = c(1, 0.5)) +
  ylab('P(lick)') +
  xlab('Block trial') +
  theme_ag01(6) +
  coord_cartesian(ylim = c(0.5, 1), xlim = c(1, 10), expand = F, clip = 'off') +
  scale_x_continuous(breaks = c(1, 10)) +
  scale_y_continuous(breaks = c(0.5, 0.75, 1.0)) +
  theme(panel.spacing.x = unit(1, "lines"), panel.spacing.y = unit(1, "lines")) +
  force_panelsizes(rows = unit(1, 'cm'), cols = unit(1.4, 'cm'))

save_pdf(dir_output_h, 'analysis_bintrials_plick.pdf', h = 3, w = 7)
```

---

# DA correlation with initiation [text only — no paper figure]

## logs / keys
```{r eval=FALSE}
log_analysis_subjects <- read_xlsx('./logs_and_keys/log_data_analysis.xlsx', sheet = 'subjects', na = c('NA', ''))
log_analysis_fp       <- read_xlsx('./logs_and_keys/log_data_analysis.xlsx', sheet = 'fp',       na = c('NA', ''))
log_placements        <- read.csv('./logs_and_keys/log_fiber_placements.csv', na.strings = c('', 'NA'))

subjects <- log_analysis_subjects %>%
  filter(inclusion_consumption == 1) %>%
  pull(subject)

log_data <- log_analysis_fp %>%
  filter(exclude != 1 | is.na(exclude)) %>%
  filter(subject %in% subjects) %>%
  get_set_id() %>%
  filter(set_id == 'wrnacl')
```

## preprocessing
```{r eval=FALSE}
# requires: data/sessions/<blockname>/<blockname>_streams_peth_preprocessed.feather
#           data/sessions/<blockname>/<blockname>_data_trial_summary.csv
#           data/sessions/<blockname>/<blockname>_quality_metrics.csv
#           log_analysis_fp (blockname, set_id)
#           log_analysis_subjects (inclusion_consumption, remove)
#           log_placements (exclude_da_consumption)
# output:   fig08/corr_initiation/pre/df_peth_summary_combined.csv
# NOTE: comment out after fig08/corr_initiation/pre/ CSVs have been generated

toggle_process <- 0

dir_output_corr     <- str_c(dir_output, 'corr_initiation/')
dir_output_corr_pre <- str_c(dir_output_corr, 'pre/')
dir.create(dir_output_corr_pre, recursive = TRUE, showWarnings = FALSE)

peth_tm_bins <- tibble(
  tm_bin_id    = c('access'),
  tm_bin_start = c(       0),
  tm_bin_end   = c(       3)
)

grouping_vars <- c('blockname', 'region', 'trial_num', 'time_bin')

if (toggle_process) {
  fns_qc_metrics      <- list.files('./data/sessions/', pattern = 'quality_metrics.csv', recursive = TRUE, full.names = TRUE)
  combined_qc_metrics <- bind_rows(lapply(fns_qc_metrics, read.csv))

  bns <- log_data %>%
    pull(blockname)

  for (bn in bns) {
    df_peth <- read_feather(str_c('./data/sessions/', bn, '/', bn, '_streams_peth_preprocessed.feather')) %>%
      filter(event_id_char %in% c('access_period', 'spout_extended')) %>%
      left_join(log_data %>% select(blockname, subject), by = 'blockname') %>%
      filter_qc_metrics(combined_qc_metrics, removal_type = 1) %>%
      get_region_labels() %>%
      filter_placements('exclude_da_consumption')

    df_trial <- read.csv(str_c('./data/sessions/', bn, '/', bn, '_data_trial_summary.csv')) %>%
      select(blockname, trial_num, solution, lick_count, lick_ts_first, trial_lick) %>%
      mutate(
        trial_lick_lead    = trial_lick    %>% lead(),
        lick_ts_first_lead = lick_ts_first %>% lead()
      ) %>%
      select(-trial_lick, -lick_ts_first)

    df_peth_summary <- df_peth %>%
      rename(trial_num = event_number) %>%
      get_peth_binned_summary(peth_tm_bins, grouping_vars)

    suppressMessages(
      df_peth_summary <- df_peth_summary %>%
        left_join(df_trial, by = c('blockname', 'trial_num')) %>%
        left_join(log_data %>% select(blockname, set_id), by = 'blockname') %>%
        format_set_id(key_set_id) %>%
        select(set_id, everything())
    )

    if (bn == bns[1]) {
      df_peth_summary_combined <- df_peth_summary
    } else {
      df_peth_summary_combined <- bind_rows(df_peth_summary_combined, df_peth_summary)
    }
  }

  df_peth_summary_combined %>%
    filter(!region %>% str_detect('LHA')) %>%
    write_csv(str_c(dir_output_corr_pre, 'df_peth_summary_combined.csv'))
} else {
  df_peth_summary_combined <- read.csv(str_c(dir_output_corr_pre, 'df_peth_summary_combined.csv'))
}

```

## sustained DA vs lick on next trial
```{r eval=FALSE}
df2 <- df_peth_summary_combined %>%
  filter(!is.na(trial_lick_lead)) %>%
  left_join(log_data %>% select(blockname, subject), by = 'blockname') 
```

```{r eval=FALSE}
coef_by_region <- df2 %>%
  filter(set_id == 'WR:NaCl') %>%
  group_by(region) %>%
  group_modify(~{
    m <- glm(trial_lick_lead ~ zscore_blsub_mean, data = .x, family = binomial())
    tidy(m, conf.int = TRUE, exponentiate = TRUE)
  }) %>%
  ungroup()

coef_by_region <- coef_by_region %>%
  rename(odds_ratio = estimate,
         or_low     = conf.low,
         or_high    = conf.high) %>%
  clean_names() %>%
  mutate(region = factor(region, unique(key_regions$region_label)))

trial_counts <- df2 %>%
  filter(set_id == 'WR:NaCl') %>%
  filter(!region %>% str_detect('LHA')) %>%
  group_by(region) %>%
  summarise(
    n_trials   = n(),
    n_subjects = n_distinct(subject)
  ) %>%
  mutate(region = factor(region, unique(key_regions$region_label))) %>%
  arrange(region)

coef_by_region <- coef_by_region %>%
  left_join(trial_counts, by = join_by(region)) %>%
  mutate(region = region %>% factor(levels = key_regions$region_label %>% unique())) %>%
  arrange(region, term)

coef_by_region %>%
  write_csv(str_c(dir_output_corr, 'coef_by_region.csv'))

coef_by_region %>%
  filter(term == 'zscore_blsub_mean') %>%
  quick_sig() %>%
  mutate(p_value_fmt = formatC(p_value, format = 'e', digits = 2)) %>%
  mutate(odds_ratio = odds_ratio %>% round(2)) %>%
  ggplot() +
  geom_text(aes(region, 0, label = odds_ratio)) +
  geom_text(aes(region, 1, label = p_value_fmt)) +
  geom_text(aes(region, 2, label = sig_symbol)) +
  geom_text(aes(region, 3, label = n_subjects)) +
  geom_text(aes(region, 4, label = n_trials)) +
  scale_y_continuous(
    breaks = c(0, 1, 2, 3, 4),
    labels = c('or', 'p', 'sig', 'n subj', 'n trials')
  )

save_pdf(dir_output_corr, 'coef_by_region_summary.pdf', h = 3, w = 6)
```
