---
title: "fig02 / sfig04"
author: "adam gordon-fennell"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# run all chunks from the project root so relative paths resolve correctly
knitr::opts_knit$set(root.dir = normalizePath('../'))
```

# setup
## libraries
```{r}
source('./logs_and_keys/key_local_directories.R')
Sys.unsetenv("RETICULATE_PYTHON_FALLBACK")
Sys.unsetenv("RETICULATE_PYTHON")
reticulate::use_python(path_python, required = TRUE)

library(tidyverse)
library(afex)
library(emmeans)
library(janitor)
library(readxl)
library(ggh4x)
library(arrow)
library(zoo)
library(lubridate)
library(patchwork)
library(ggbeeswarm)
library(ggpubr)
library(pals)
library(boot)
library(corrplot)
library(Hmisc)
library(plotly)

arrow::set_cpu_count(4)

source('./functions/params.R')
source('./functions/theme.R')
source('./functions/general.R')
source('./functions/r_general.R')
source('./functions/r_plots.R')
source('./functions/stats.R')
source('./functions/pca.R')
source('./functions/analysis_peth.R')
source('./functions/plotting_placements.R')
```

## directories
```{r eval=FALSE}
dir_output    <- './analysis_and_plots/fig02_sfig04/'
dir_data_stim <- './data/fig02_sfig04/stimulation/'
dir_data_inh  <- './data/fig02_sfig04/inhibition/'

dir.create(dir_output,                           recursive = TRUE, showWarnings = FALSE)
dir.create(str_c(dir_output, 'b/'),              recursive = TRUE, showWarnings = FALSE)
dir.create(str_c(dir_output, 'c/'),              recursive = TRUE, showWarnings = FALSE)
dir.create(str_c(dir_output, 'd_sfig04abc/'),    recursive = TRUE, showWarnings = FALSE)
dir.create(str_c(dir_output, 'e/'),              recursive = TRUE, showWarnings = FALSE)
dir.create(str_c(dir_output, 'sfig04d/'),         recursive = TRUE, showWarnings = FALSE)
dir.create(str_c(dir_output, 'sfig04e/'),         recursive = TRUE, showWarnings = FALSE)
dir.create(str_c(dir_output, 'g/'),              recursive = TRUE, showWarnings = FALSE)
dir.create(str_c(dir_output, 'h/'),              recursive = TRUE, showWarnings = FALSE)
dir.create(str_c(dir_output, 'i/'),              recursive = TRUE, showWarnings = FALSE)
dir.create(str_c(dir_output, 'j/'),              recursive = TRUE, showWarnings = FALSE)
dir.create(str_c(dir_output, 'sfig04g/'),       recursive = TRUE, showWarnings = FALSE)
dir.create(str_c(dir_output, 'sfig04h/'),       recursive = TRUE, showWarnings = FALSE)

dir_data_interaction  <- './data/fig02_sfig04/interaction/'
```

## logs / keys
```{r eval=FALSE}
# Fiber placement log — used by join_placements() and filter_placements()
log_placements <- read.csv('./logs_and_keys/log_fiber_placements.csv', na.strings = c('', 'NA'))

# log_subject (subject × line × group) is loaded from Google Sheets inside the
# preprocessing blocks below. It is not needed to regenerate plots from pre-computed CSVs.
```

## keys (fig02-specific)
```{r eval=FALSE}
# Override the repo-wide key_regions with the 6 striatal regions used in this experiment.
# Note: this shadows the key_regions defined in params.R for the duration of this session.
key_regions <- tibble(
  region       = c('nac',    'nac_corr', 'nac_shelllat', 'dms', 'dls', 'ts'),
  region_label = c('NAcCR',  'NAcCC',    'NAcShL',       'DMS', 'DLS', 'TS')
)

# Panel dimensions (cm) used throughout this figure
plt_dims <- c(3, 3)

# Group color palette — alias for repo-wide color_values_groupcombined
# Order: Control, LHA GABA (vgat), LHA Glut (vglut2)
color_group_combined <- color_values_groupcombined   # c('darkgrey', '#CC2029', '#70BF46')
```

## functions (fig02-specific)
```{r eval=FALSE}
# ── format_group_combined ──────────────────────────────────────────────────────
# Creates the group_combined column from the raw 'line' and 'group' columns.
# Produces internal codes: 'control', 'vgat_stim'/'vglut2_stim' (stimulation)
#                          or 'vgat_inh'/'vglut2_inh' (inhibition).
# NOTE: this overrides the display-rename version in params.R, which is intentional —
# the plot/stats code in this figure references these internal codes directly.
format_group_combined <- function(df) {
  df %>%
    mutate(group_combined = ifelse(line %>% str_detect('vglut2'), 'vglut2', NA)) %>%
    mutate(group_combined = ifelse(line %>% str_detect('vgat'),   'vgat',   group_combined)) %>%
    mutate(group_combined = ifelse(tolower(group) == 'mcherry',   'control', group_combined)) %>%
    mutate(group_combined = ifelse(tolower(group) == 'chrimson',  group_combined %>% str_c('_stim'), group_combined)) %>%
    mutate(group_combined = ifelse(tolower(group) == 'hr',        group_combined %>% str_c('_inh'),  group_combined))
}

# ── join_placements (fig02 version) ───────────────────────────────────────────
# Joins fiber coordinates from log_placements using the 'target' column as region key.
# Distinct from the repo's join_placements() in plotting_placements.R which uses 'region'.
join_placements <- function(df) {
  df %>%
    left_join(log_placements %>% select(subject, region = target, hit_ap, hit_ml, hit_dv),
              by = c('subject', 'region'))
}

# ── format_df (preprocessing only) ────────────────────────────────────────────
# Joins subject metadata and formats regions and group labels.
# Requires log_subject (loaded from Google Sheets in preprocessing blocks).
format_df <- function(df) {
  df %>%
    left_join(log_subject %>% select(subject, line, group)) %>%
    format_group_combined() %>%
    format_regions('region', key_regions)
}

# ── filter_placements (preprocessing only) ────────────────────────────────────
# Filters out fibers excluded from opto characterization analysis.
filter_placements <- function(df) {
  df %>%
    left_join(log_placements %>%
                select(subject, region = target, exclude_optochar, hit_ap, hit_ml, hit_dv)) %>%
    filter(exclude_optochar != 1) %>%
    select(-exclude_optochar)
}

# ── tidy correlation helpers (used by plt_corr) ───────────────────────────────
tidy_cor_output_reshape <- function(df, n_table, var_name) {
  df_tidy <- df[[n_table]] %>% as_tibble()
  df_tidy %>%
    mutate(var_y = colnames(df_tidy)) %>%
    gather('var_x', !!as.name(var_name), -var_y)
}

tidy_cor_output <- function(df) {
  tidy_cor_output_reshape(df, 1, 'r') %>%
    left_join(tidy_cor_output_reshape(df, 2, 'n'), by = c('var_y', 'var_x')) %>%
    left_join(tidy_cor_output_reshape(df, 3, 'p'), by = c('var_y', 'var_x'))
}

get_cormatrix <- function(df) {
  df_corr <- rcorr(as.matrix(df))
  tidy_cor_output(df_corr)
}

# ── plt_corr ──────────────────────────────────────────────────────────────────
# Plots fiber placement (AP/ML/DV mm) vs. response (z-score), faceted by group_combined.
# Returns a list with 'AP', 'ML', 'DV' ggplot objects and 'stats_output' (Pearson r table).
plt_corr <- function(df, ylim_all, xlim_ap, xlim_ml, xlim_dv,
                     var_dep, var_dep_label, plt_dims, cor_text_y) {

  plt_data <- df %>%
    gather('dim', 'mm', starts_with('hit')) %>%
    mutate(dim = case_when(
      dim == 'hit_ap' ~ 'AP',
      dim == 'hit_ml' ~ 'ML',
      dim == 'hit_dv' ~ 'DV'
    )) %>%
    mutate(dim = dim %>% factor(levels = c('AP', 'ML', 'DV')))

  f_plt <- function(plt_data, ylim_all, xlim_ap, xlim_ml, xlim_dv,
                    var_dep, var_dep_label, plt_dims, plt_dim) {
    plt <- plt_data %>%
      filter(dim == plt_dim) %>%
      ggplot(aes(mm, zscore, color = group_combined, fill = group_combined)) +
      geom_hline(yintercept = 0, color = 'darkgrey', size = 0.5) +
      geom_smooth(method = 'lm', size = 0.3, alpha = 1/5) +
      geom_jitter(shape = 21, size = 2, color = 'white', stroke = 1/3, height = 0, width = 0.2) +
      facet_grid(group_combined ~ dim, scales = 'free') +
      theme_ag01(6) +
      scale_color_manual(values = color_group_combined) +
      scale_fill_manual(values = color_group_combined) +
      xlab('MM Relative to bregma') +
      ylab(var_dep_label) +
      theme(strip.text.y = element_blank()) +
      theme(panel.spacing.y = unit(0.75, 'lines'))

    if (plt_dim == 'AP') {
      plt <- plt +
        coord_cartesian(ylim = ylim_all, xlim = c(min(xlim_ap), max(xlim_ap)), expand = F, clip = 'off') +
        stat_cor(method = 'pearson', label.y = cor_text_y, label.x = -3, size = 2) +
        scale_x_continuous(breaks = xlim_ap) +
        theme(axis.title.x = element_blank())
    }
    if (plt_dim == 'ML') {
      plt <- plt +
        coord_cartesian(ylim = ylim_all, xlim = c(min(xlim_ml), max(xlim_ml)), expand = F, clip = 'off') +
        stat_cor(method = 'pearson', label.y = cor_text_y, label.x = 0, size = 2) +
        scale_x_continuous(breaks = xlim_ml)
      plt <- plt %>% remove_y_all
    }
    if (plt_dim == 'DV') {
      plt <- plt +
        coord_cartesian(ylim = ylim_all, xlim = c(min(xlim_dv), max(xlim_dv)), expand = F, clip = 'off') +
        stat_cor(method = 'pearson', label.y = cor_text_y, label.x = -6, size = 2) +
        scale_x_continuous(breaks = xlim_dv) +
        theme(axis.title.x = element_blank())
      plt <- plt %>% remove_y_all
    }
    return(plt)
  }

  plt_list <- list()
  for (plt_dim in c('AP', 'ML', 'DV')) {
    plt_list[[plt_dim]] <- f_plt(plt_data, ylim_all, xlim_ap, xlim_ml, xlim_dv,
                                  var_dep, var_dep_label, plt_dims, plt_dim)
  }

  # Pearson r statistics (grouped by dim and group_combined)
  plt_list[['stats_output']] <- plt_data %>%
    tidy_cor('mm', 'zscore', 'dim', 'group_combined')

  return(plt_list)
}
```


```{r eval=FALSE}
# Used in the preprocessing blocks below; not needed for figure rendering from saved data.

# ── return_stim_params (preprocessing only) ───────────────────────────────────
# Extracts stim parameters (frequency, pulse duration, train duration) from
# extracted serial data. 
return_stim_params <- function(import_fns, dir_extracted, file_format_output) {
  data_list <- combined_import(
    import_directory = dir_extracted,
    filter_strings   = import_fns,
    prefixes         = NA,
    suffixes         = c(str_c('_param_dynamic.', file_format_output))
  )

  stim_params <- data_list[[1]] %>%
    select(blockname, param_dynamic, param_ts, param_value) %>%
    filter(param_dynamic %in% c('trial_stim_frequency',
                                'trial_stim_pulse_duration',
                                'trial_stim_train_duration')) %>%
    arrange(blockname, param_ts) %>%
    spread(param_dynamic, param_value) %>%
    group_by(blockname) %>%
    mutate(stim_num = row_number())

  return(stim_params)
}

  
```

---

# Opto stimulation (fig2b, fig2c, fig2d, sfig04d, sfig04e)

## preprocessing
```{r eval=FALSE}
# ── PREPROCESSING NOTE ────────────────────────────────────────────────────────
# The block below documents how the pre-computed CSVs in data/fig02/stimulation/ were
# produced. It requires raw FP data from network storage and Google Sheets credentials.
# All paths are absolute, relative to the abo experiment root:
#   dir_exp_abo
#
# Source files:
#   npm processed FP:  str_c(dir_npm, 'data_processed/')
#   arduino extracted: str_c(dir_exp_abo, 'data/arduino/extracted/')
#   antijoin events:   str_c(dir_exp_abo, 'antijoin_events.csv')
#   log_subject:       Google Sheet (url_sheet_subject)
#   log_npm:           Google Sheet (url_sheet_npm)
# ─────────────────────────────────────────────────────────────────────────────

# preprocess <- 1
# 
# if (preprocess) {
#   library(googlesheets4)
#   log_npm     <- read_sheet(url_sheet_npm, na = c('', 'NA'))
#   log_subject <- read_sheet(url_sheet_subject, na = c('', 'NA'))
#
#   dir_output_abo_stim <- str_c(dir_exp_abo, 'analysis_output_final/stimulation/')
#   dir_arduino_extraction <- str_c(dir_exp_abo, 'data/arduino/extracted/')
#   dir_npm_processed      <- str_c(dir_npm, 'data_processed/')
#   file_format_output     <- 'csv'
# 
#   # ── identify sessions ──────────────────────────────────────────────────────
#   import_fns <- log_npm %>%
#     filter(experiment == 'abo') %>%
#     filter(procedure == 'opto_characterization') %>%
#     pull(blockname) %>% unique()
# 
#   # ── build stim parameter table ─────────────────────────────────────────────
#   stim_params <- return_stim_params(import_fns, dir_arduino_extraction, file_format_output)
#   stim_params <- stim_params %>%
#     select(blockname, stim_num, trial_stim_frequency) %>%
#     filter(trial_stim_frequency != 0) %>%
#     arrange(blockname, stim_num) %>%
#     group_by(blockname) %>%
#     mutate(event_number_arduino = ifelse(
#       blockname %>% str_detect('2023_07_29'), row_number(), stim_num))
# 
#   # ── import raw FP streams ──────────────────────────────────────────────────
#   data_list <- combined_import(
#     import_directory = dir_npm_processed,
#     filter_strings   = import_fns,
#     prefixes  = NA,
#     suffixes  = c('streams_session.feather', 'streams_peth.feather', 'events.feather'),
#     verbose   = 0
#   )
#   streams      <- data_list[[1]]
#   streams_peth <- data_list[[2]]
#   events       <- data_list[[3]]
# 
#   streams      <- streams      %>% mutate(subject = blockname %>% str_sub(12, 16))
#   streams_peth <- streams_peth %>% mutate(subject = blockname %>% str_sub(12, 16))
# 
#   streams_peth <- streams_peth %>%
#     left_join(log_npm %>% select(blockname, branch_id, region)) %>%
#     mutate(region = region %>% factor(
#       levels = c('nac_shelllat', 'nac', 'nac_corr', 'dms', 'dls', 'ts')))
# 
#   streams_peth <- streams_peth %>%
#     left_join(log_subject %>% select(subject, line)) %>%
#     filter(time_rel > -3, time_rel < 12)
# 
#   # ── remove excluded stimulation events ────────────────────────────────────
#   antijoin_events <- read_csv(str_c(dir_exp_abo, 'antijoin_events.csv'))
#   events <- events %>% anti_join(antijoin_events)
# 
#   events <- events %>%
#     group_by(blockname) %>%
#     filter(event_id_char %in% c('opto_stim', 'trial_start')) %>%
#     arrange(blockname, event_ts) %>%
#     mutate(event_number_arduino = row_number()) %>%
#     left_join(stim_params, by = c('blockname', 'event_number_arduino'))
# 
#   streams_peth <- streams_peth %>%
#     left_join(events %>% select(blockname, event_number, trial_stim_frequency)) %>%
#     filter(!is.na(trial_stim_frequency))
# 
#   # ── local z-score (baseline: -3 to 0 s) ───────────────────────────────────
#   local_zs_window <- c(-3, 0)
#   streams_peth <- streams_peth %>%
#     group_by(blockname, signal_wavelength, region) %>%
#     filter(time_rel > local_zs_window[1], time_rel < local_zs_window[2]) %>%
#     summarise(
#       delta_signal_poly_local_bl_mu = mean(delta_signal_poly),
#       delta_signal_poly_local_bl_sd = sd(delta_signal_poly),
#       .groups = 'drop') %>%
#     left_join(streams_peth, ., by = c('blockname', 'signal_wavelength', 'region')) %>%
#     mutate(delta_signal_poly_zscore_local =
#              (delta_signal_poly - delta_signal_poly_local_bl_mu) /
#              delta_signal_poly_local_bl_sd) %>%
#     select(-delta_signal_poly_local_bl_mu, -delta_signal_poly_local_bl_sd)
# 
#   # ── subtract per-trial pre-stimulus baseline ───────────────────────────────
#   streams_peth <- streams_peth %>%
#     filter(time_rel > -3, time_rel < 0) %>%
#     group_by(blockname, event_number, region, signal_wavelength) %>%
#     summarise(bl = mean(delta_signal_poly_zscore_local), .groups = 'drop') %>%
#     left_join(streams_peth, .) %>%
#     mutate(delta_signal_poly_zscore_local = delta_signal_poly_zscore_local - bl) %>%
#     select(-bl) %>%
#     left_join(log_subject %>% select(subject, group), by = 'subject')
# 
#   # ── apply group labels, region labels, and placement filter ───────────────
#   streams_peth <- streams_peth %>% format_df()
#   streams_peth <- streams_peth %>% filter_placements()
# 
#   # ── compute summary data frames ───────────────────────────────────────────
#   streams_peth_summary <- streams_peth %>%
#     filter(time_rel > 0, time_rel < 3) %>%
#     group_by(blockname, subject, group_combined, line, group, trial_stim_frequency, region) %>%
#     summarise(delta_signal_poly_zscore_local = mean(delta_signal_poly_zscore_local),
#               .groups = 'drop') %>%
#     mutate(trial_stim_frequency =
#              as.character(trial_stim_frequency) %>% factor(levels = c(0,1,2,5,10,20,40)))
# 
#   streams_peth <- streams_peth %>%
#     mutate(region = region %>% factor(levels = key_regions$region_label))
#   streams_peth_summary <- streams_peth_summary %>%
#     mutate(region = region %>% factor(levels = key_regions$region_label))
# 
#   streams_peth_subject <- streams_peth %>%
#     format_group_combined() %>%
#     group_by(group_combined, subject, region, time_rel, trial_stim_frequency) %>%
#     summarise(delta_signal_poly_zscore_local = mean(delta_signal_poly_zscore_local),
#               .groups = 'drop')
# 
#   streams_peth_group <- streams_peth %>%
#     format_group_combined() %>%
#     group_by(group_combined, region, time_rel, trial_stim_frequency) %>%
#     summarise(
#       delta_signal_poly_zscore_local_sem = sd(delta_signal_poly_zscore_local) / sqrt(n()),
#       delta_signal_poly_zscore_local     = mean(delta_signal_poly_zscore_local),
#       .groups = 'drop')
# 
#   # ── save pre-computed outputs ─────────────────────────────────────────────
#   streams_peth %>%
#     select(blockname, line, group, group_combined, subject, branch_id, region,
#            time, time_rel, event_number, trial_stim_frequency,
#            delta_signal_poly_zscore_local) %>%
#     write_csv(str_c(dir_output_abo_stim, 'data_streams_peth_full.csv'))
# 
#   streams_peth_summary        %>% write_csv(str_c(dir_output_abo_stim, 'data_streams_peth_summary.csv'))
#   streams_peth_subject        %>% write_csv(str_c(dir_output_abo_stim, 'data_streams_peth_summary_trace_subject.csv'))
#   streams_peth_group          %>% write_csv(str_c(dir_output_abo_stim, 'data_streams_peth_summary_trace_group.csv'))
# 
# }
```

## import pre-computed data
```{r eval=FALSE}
# ~ individual trial data not necessary for plotting and analysis
# streams_peth <- read.csv(str_c(dir_data_stim, 'data_streams_peth_full.csv')) %>%
#   format_group_combined() %>%
#   mutate(region = region %>% factor(levels = key_regions$region_label)) %>%
#   mutate(trial_stim_frequency =
#            as.character(trial_stim_frequency) %>% factor(levels = c(0,1,2,5,10,20,40)))

streams_peth_summary <- read.csv(str_c(dir_data_stim, 'data_streams_peth_summary.csv')) %>%
  mutate(region = region %>% factor(levels = key_regions$region_label)) %>%
  mutate(trial_stim_frequency =
           as.character(trial_stim_frequency) %>% factor(levels = c(0,1,2,5,10,20,40)))

streams_peth_subject <- read.csv(str_c(dir_data_stim, 'data_streams_peth_summary_trace_subject.csv')) %>%
  mutate(region = region %>% factor(levels = key_regions$region_label))

streams_peth_group <- read.csv(str_c(dir_data_stim, 'data_streams_peth_summary_trace_group.csv')) %>%
  mutate(region = region %>% factor(levels = key_regions$region_label)) %>%
  mutate(trial_stim_frequency =
           as.character(trial_stim_frequency) %>% factor(levels = c(0,1,2,5,10,20,40)))
```

## summary of data in analysis
### fiber counts
```{r eval=FALSE}
streams_peth_summary %>%
  select(group_combined, region, subject) %>%
  unique() %>%
  group_by(group_combined, region) %>%
  summarise(region_count = n()) %>%
  ggplot(aes(region, group_combined, label = region_count)) +
  geom_text() +
  theme_ag01() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3)) +
  xlab('') + ylab('') +
  force_panelsizes(rows = unit(2, 'cm'), cols = unit(4, 'cm'))
```

---

## fig2b: stim trace (20 Hz, group mean ± SEM)
```{r eval=FALSE}
dir_output_b <- str_c(dir_output, 'b/')
fn_stem_b    <- 'opto_stim_trace_20hz'

plt_data <- streams_peth_group %>%
  filter(trial_stim_frequency == 20) %>%
  filter(time_rel > -3, time_rel < 6)

plt <- plt_data %>%
  ggplot(aes(time_rel, delta_signal_poly_zscore_local, color = region, fill = region)) +
  annotate('rect', xmin = 0, xmax = 3, ymin = -Inf, ymax = Inf, alpha = 1/3, fill = 'darkgrey') +
  geom_hline(yintercept = 0, color = 'darkgrey', size = 0.5) +
  geom_ribbon(aes(ymax = delta_signal_poly_zscore_local + delta_signal_poly_zscore_local_sem,
                  ymin = delta_signal_poly_zscore_local - delta_signal_poly_zscore_local_sem),
              color = NA, alpha = 1/3) +
  geom_line() +
  facet_grid(. ~ group_combined) +
  theme_ag01() +
  scale_color_manual(values = color_values_regions_da) +
  scale_fill_manual(values = color_values_regions_da)

plt <- plt %>%
  add_scale_bar(origin = c(-3, -2), x_len = 1, y_len = 1)

plt +
  force_panelsizes(cols = unit(plt_dims[1], 'cm'), rows = unit(plt_dims[2] * 1.8, 'cm'))

save_pdf(dir_output_b, str_c(fn_stem_b, '.pdf'), 12, 6)
plt_data %>% write_csv(str_c(dir_output_b, fn_stem_b, '_data.csv'))
```

---

## fig2c: 20 Hz summary bars
### top: initial response (0–1 s)
```{r eval=FALSE}
dir_output_c <- str_c(dir_output, 'c/')
fn_stem_c_initial <- 'opto_stim_20hz_region_bar_initial'

plt_data <- streams_peth_subject %>%
  filter(time_rel > 0, time_rel <= 1) %>%
  group_by(subject, group_combined, line, group, trial_stim_frequency, region) %>%
  summarise(delta_signal_poly_zscore_local = mean(delta_signal_poly_zscore_local),
            .groups = 'drop') %>%
  mutate(trial_stim_frequency =
           as.character(trial_stim_frequency) %>% factor(levels = c(0,1,2,5,10,20,40))) %>%
  filter(trial_stim_frequency == 20) %>%
  rename(zscore = delta_signal_poly_zscore_local)

plt_data %>%
  ggplot(aes(region, zscore, color = group_combined, fill = group_combined)) +
  geom_hline(yintercept = 0, alpha = 1/3) +
  stat_summary(fun.data = 'mean_se', geom = 'errorbar', aes(group = group_combined),
               width = 0.3, position = position_dodge(width = 0.75)) +
  stat_summary(fun = 'mean', geom = 'bar', color = NA, aes(group = group_combined),
               alpha = 1/2, width = 0.6, position = position_dodge(width = 0.75)) +
  geom_jitter(shape = 21, color = 'white', size = 1.5, stroke = 0.25,
              position = position_jitterdodge(jitter.width = 0.04, jitter.height = 0,
                                              dodge.width = 0.75)) +
  theme_ag01(6) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3)) +
  scale_color_manual(values = color_group_combined) +
  scale_fill_manual(values = color_group_combined) +
  coord_cartesian(xlim = c(0.5, 6.5), ylim = c(-5, 20), expand = F) +
  force_panelsizes(cols = unit(3, 'cm'), rows = unit(1.4, 'cm')) +
  ylab('Z-Score') + xlab('') + ggtitle('Initial (0–1s)')

save_pdf(dir_output_c, str_c(fn_stem_c_initial, '.pdf'), 8, 6)
plt_data %>% write_csv(str_c(dir_output_c, fn_stem_c_initial, '_data.csv'))
```

```{r eval=FALSE}
# ── Wilcoxon unpaired: control vs. vgat_stim and vglut2_stim per region ───────
loop_regions <- plt_data %>% pull(region) %>% unique()

for (loop_region in loop_regions) {
  plt_data_wide <- plt_data %>%
    select(region, subject, group_combined, zscore) %>%
    spread(group_combined, zscore) %>%
    filter(region == loop_region)

  loop_result <- bind_rows(
    plt_data_wide %>%
      tidy_wilcox_unpaired('control', 'vgat_stim') %>%
      mutate(comparision = 'control_vs_vgat'),
    plt_data_wide %>%
      tidy_wilcox_unpaired('control', 'vglut2_stim') %>%
      mutate(comparision = 'control_vs_vglut2')
  ) %>%
    clean_names() %>%
    mutate(region = loop_region) %>%
    select(region, comparision, everything()) %>%
    mutate(p_value = p_value * 2) %>%
    quick_sig()

  if (loop_region == loop_regions[1]) {
    combined_result <- loop_result
  } else {
    combined_result <- bind_rows(combined_result, loop_result)
  }
}

combined_result %>%
  mutate(region = region %>% factor(levels = key_regions$region_label)) %>%
  ggplot(aes(region, comparision, label = sig_symbol)) +
  geom_text()

combined_result %>% write_csv(str_c(dir_output_c, fn_stem_c_initial, '_stats.csv'))
```

### bottom: sustained response (2–3 s)
```{r eval=FALSE}
fn_stem_c_sust <- 'opto_stim_20hz_region_bar_sustained'

plt_data <- streams_peth_subject %>%
  filter(time_rel > 2, time_rel <= 3) %>%
  group_by(subject, group_combined, line, group, trial_stim_frequency, region) %>%
  summarise(delta_signal_poly_zscore_local = mean(delta_signal_poly_zscore_local),
            .groups = 'drop') %>%
  mutate(trial_stim_frequency =
           as.character(trial_stim_frequency) %>% factor(levels = c(0,1,2,5,10,20,40))) %>%
  filter(trial_stim_frequency == 20) %>%
  rename(zscore = delta_signal_poly_zscore_local)

plt_data %>%
  ggplot(aes(region, zscore, color = group_combined, fill = group_combined)) +
  geom_hline(yintercept = 0, alpha = 1/3) +
  stat_summary(fun.data = 'mean_se', geom = 'errorbar', aes(group = group_combined),
               width = 0.3, position = position_dodge(width = 0.75)) +
  stat_summary(fun = 'mean', geom = 'bar', color = NA, aes(group = group_combined),
               alpha = 1/2, width = 0.6, position = position_dodge(width = 0.75)) +
  geom_jitter(shape = 21, color = 'white', size = 1.5, stroke = 0.25,
              position = position_jitterdodge(jitter.width = 0.04, jitter.height = 0,
                                              dodge.width = 0.75)) +
  theme_ag01(6) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3)) +
  scale_color_manual(values = color_group_combined) +
  scale_fill_manual(values = color_group_combined) +
  coord_cartesian(xlim = c(0.5, 6.5), ylim = c(-10, 30), expand = F, clip = 'off') +
  force_panelsizes(cols = unit(3, 'cm'), rows = unit(1.4, 'cm')) +
  ylab('Z-Score') + xlab('') + ggtitle('Sustained (2–3s)')

save_pdf(dir_output_c, str_c(fn_stem_c_sust, '.pdf'), 8, 6)
plt_data %>% write_csv(str_c(dir_output_c, fn_stem_c_sust, '_data.csv'))
```

```{r eval=FALSE}
# ── Wilcoxon unpaired: control vs. vgat_stim and vglut2_stim per region ───────
loop_regions <- plt_data %>% pull(region) %>% unique()

for (loop_region in loop_regions) {
  plt_data_wide <- plt_data %>%
    select(region, subject, group_combined, zscore) %>%
    spread(group_combined, zscore) %>%
    filter(region == loop_region)

  loop_result <- bind_rows(
    plt_data_wide %>%
      tidy_wilcox_unpaired('control', 'vgat_stim') %>%
      mutate(comparision = 'control_vs_vgat'),
    plt_data_wide %>%
      tidy_wilcox_unpaired('control', 'vglut2_stim') %>%
      mutate(comparision = 'control_vs_vglut2')
  ) %>%
    clean_names() %>%
    mutate(region = loop_region) %>%
    select(region, comparision, everything()) %>%
    mutate(p_value = p_value * 2) %>%
    quick_sig()

  if (loop_region == loop_regions[1]) {
    combined_result <- loop_result
  } else {
    combined_result <- bind_rows(combined_result, loop_result)
  }
}

combined_result %>%
  mutate(region = region %>% factor(levels = key_regions$region_label)) %>%
  ggplot(aes(region, comparision, label = sig_symbol)) +
  geom_text()

combined_result %>% write_csv(str_c(dir_output_c, fn_stem_c_sust, '_stats.csv'))
```

---

## fig2d / sfig4 a-c: placement maps (3D and 2D, sustained z-score at 20 Hz)
```{r eval=FALSE}
dir_output_d <- str_c(dir_output, 'd_sfig04abc/')

fn_stem_d <- 'placement_vs_zscore_sustained'

for (loop_group in c('control', 'vgat_stim', 'vglut2_stim')) {

  df <- streams_peth_subject %>%
    filter(group_combined == loop_group) %>%
    filter(time_rel > 2, time_rel <= 3) %>%
    group_by(subject, group_combined, line, group, trial_stim_frequency, region) %>%
    summarise(delta_signal_poly_zscore_local = mean(delta_signal_poly_zscore_local),
              .groups = 'drop') %>%
    mutate(trial_stim_frequency =
             as.character(trial_stim_frequency) %>% factor(levels = c(0,1,2,5,10,20,40))) %>%
    filter(trial_stim_frequency == 20) %>%
    rename(zscore = delta_signal_poly_zscore_local) %>%
    join_placements() %>%
    select(subject, group_combined, region, zscore, starts_with('hit')) %>%
    mutate(region = region %>% factor(levels = key_regions$region_label))

  var_color    <- 'zscore'
  color_limits <- c(-6, 6)

  for (plt_plane in c('sagittal', 'horizontal', 'coronal')) {
    plt_str(
      df           = df,
      var_color    = !!sym(var_color),
      var_color_name = 'z-score',
      vars_facet   = c('.', '.'),
      plt_plane    = plt_plane,
      plt_dim_base = 3,
      color_limits = color_limits
    )
    save_pdf(dir_output_d,
             str_c(fn_stem_d, '_', loop_group, '_', plt_plane, '.pdf'), 6, 6)
  }

  tryCatch(
    plt_str_3d(
      df           = df,
      var_color    = var_color,
      color_limits = color_limits,
      dir_output   = dir_output_d,
      fn_stem      = str_c(fn_stem_d, '_', loop_group),
      toggle_save  = 1
    ),
    error = function(e) message('plt_str_3d skipped (kaleido): ', conditionMessage(e))
  )
}
```

---

## fig2e: placement × response correlation (sustained z-score at 20 Hz)
```{r eval=FALSE}
dir_output_e <- str_c(dir_output, 'e/')
fn_stem_e    <- 'placement_vs_zscore_sustained_corr'

# Build plt_data: sustained z-score (2–3 s) at 20 Hz with placement coordinates
plt_data <- streams_peth_subject %>%
  filter(time_rel > 2, time_rel <= 3) %>%
  group_by(subject, group_combined, line, group, trial_stim_frequency, region) %>%
  summarise(delta_signal_poly_zscore_local = mean(delta_signal_poly_zscore_local),
            .groups = 'drop') %>%
  mutate(trial_stim_frequency =
           as.character(trial_stim_frequency) %>% factor(levels = c(0,1,2,5,10,20,40))) %>%
  filter(trial_stim_frequency == 20) %>%
  rename(zscore = delta_signal_poly_zscore_local) %>%
  join_placements() %>%
  select(subject, group_combined, region, zscore, starts_with('hit')) %>%
  mutate(region = region %>% factor(levels = key_regions$region_label))

plt_list <- plt_corr(
  df             = plt_data,
  ylim_all       = c(-10, 30),
  xlim_ap        = c(-3, 0, 3),
  xlim_ml        = c(0, 2, 4),
  xlim_dv        = c(-6, -4, -2),
  var_dep        = 'zscore',
  var_dep_label  = 'Z-Score',
  plt_dims       = c(3, 3 * 2/3),
  cor_text_y     = 30
)

plt_list[['AP']] +
  plt_list[['ML']] +
  plt_list[['DV']] +
  plot_layout(nrow = 1, widths = unit(1.5, 'cm'), heights = unit(3, 'cm'),
              guides = 'collect')

save_pdf(dir_output_e, str_c(fn_stem_e, '.pdf'), 6, 6)
plt_data                      %>% write_csv(str_c(dir_output_e, fn_stem_e, '_data.csv'))
plt_list[['stats_output']]    %>% write_csv(str_c(dir_output_e, fn_stem_e, '_stats.csv'))
```

---

## sfig04d: all-frequency traces (group mean ± SEM, facet by region)
```{r eval=FALSE}
dir_output_sfig04d <- str_c(dir_output, 'sfig04d/')
fn_stem_sfig04d    <- 'opto_stim_trace_all_freq'

plt_data <- streams_peth_group %>%
  filter(time_rel > -1, time_rel < 6)

plt <- plt_data %>%
  ggplot(aes(time_rel, delta_signal_poly_zscore_local,
             color = trial_stim_frequency, fill = trial_stim_frequency,
             group = trial_stim_frequency)) +
  annotate('rect', xmin = 0, xmax = 3, ymin = -Inf, ymax = Inf, alpha = 1/3, fill = 'darkgrey') +
  geom_hline(yintercept = 0, color = 'darkgrey', size = 0.5) +
  geom_ribbon(aes(ymax = delta_signal_poly_zscore_local + delta_signal_poly_zscore_local_sem,
                  ymin = delta_signal_poly_zscore_local - delta_signal_poly_zscore_local_sem),
              color = NA, alpha = 1/3) +
  geom_line() +
  facet_grid(group_combined ~ region) +
  theme_ag01() +
  scale_color_viridis_d(option = 'inferno', end = 0.8) +
  scale_fill_viridis_d(option = 'inferno', end = 0.8)

plt <- plt %>%
  add_scale_bar(origin = c(-3, -2), x_len = 1, y_len = 1)

plt +
  force_panelsizes(cols = unit(plt_dims[1] * 1/2.1, 'cm'), rows = unit(plt_dims[2], 'cm'))

save_pdf(dir_output_sfig04d, str_c(fn_stem_sfig04d, '.pdf'), 12, 8)
plt_data %>% write_csv(str_c(dir_output_sfig04d, fn_stem_sfig04d, '_data.csv'))
```

---

## sfig04e: freq × region heat maps (initial 0-1 s; sustained 2-3 s)
```{r eval=FALSE}
dir_output_sfig04e <- str_c(dir_output, 'sfig04e/')

# ── initial (0–1 s) ───────────────────────────────────────────────────────────
fn_stem_sfig04e_initial <- 'opto_stim_freq_region_heat_initial'

streams_peth_summary_initial <- streams_peth_subject %>%
  filter(time_rel > 0, time_rel <= 1) %>%
  group_by(blockname, subject, line, group, trial_stim_frequency, region) %>%
  summarise(delta_signal_poly_zscore_local = mean(delta_signal_poly_zscore_local),
            .groups = 'drop') %>%
  mutate(trial_stim_frequency =
           as.character(trial_stim_frequency) %>% factor(levels = c(0,1,2,5,10,20,40)))

streams_peth_summary_group_initial <- streams_peth_summary_initial %>%
  format_group_combined() %>%
  group_by(group_combined, trial_stim_frequency, region) %>%
  summarise(delta_signal_poly_zscore_local = mean(delta_signal_poly_zscore_local),
            .groups = 'drop') %>%
  mutate(trial_stim_frequency =
           as.character(trial_stim_frequency) %>% factor(levels = c(0,1,2,5,10,20,40)))

plt_data <- streams_peth_summary_group_initial %>%
  rename(zscore = delta_signal_poly_zscore_local)

plt_data %>%
  ggplot(aes(trial_stim_frequency, region, fill = zscore)) +
  geom_tile() +
  scale_fill_gradientn(colors = c('blue', 'white', 'red'), limits = c(-6, 6),
                       oob = scales::squish) +
  theme_ag01() +
  facet_grid(group_combined ~ .) +
  coord_cartesian(xlim = c(0.5, 5.5), ylim = c(0.5, 6.5), expand = F) +
  force_panelsizes(cols = unit(plt_dims[1], 'cm'), rows = unit(plt_dims[2], 'cm')) +
  ylab('GRAB-DA Region') + xlab('LHA Stim Freq (Hz)') +
  ggtitle('Initial (0–1s)')

save_pdf(dir_output_sfig04e, str_c(fn_stem_sfig04e_initial, '.pdf'), 12, 6)
plt_data %>% write_csv(str_c(dir_output_sfig04e, fn_stem_sfig04e_initial, '_data.csv'))

# ── sustained (2–3 s) ─────────────────────────────────────────────────────────
fn_stem_sfig04e_sust <- 'opto_stim_freq_region_heat_sustained'

streams_peth_summary_sust <- streams_peth_subject %>%
  filter(time_rel > 2, time_rel <= 3) %>%
  group_by(blockname, subject, group_combined, line, group, trial_stim_frequency, region) %>%
  summarise(delta_signal_poly_zscore_local = mean(delta_signal_poly_zscore_local),
            .groups = 'drop') %>%
  mutate(trial_stim_frequency =
           as.character(trial_stim_frequency) %>% factor(levels = c(0,1,2,5,10,20,40)))

streams_peth_summary_group_sust <- streams_peth_summary_sust %>%
  group_by(group_combined, trial_stim_frequency, region) %>%
  summarise(delta_signal_poly_zscore_local = mean(delta_signal_poly_zscore_local),
            .groups = 'drop') %>%
  mutate(trial_stim_frequency =
           as.character(trial_stim_frequency) %>% factor(levels = c(0,1,2,5,10,20,40)))

plt_data <- streams_peth_summary_group_sust %>%
  rename(zscore = delta_signal_poly_zscore_local)

plt_data %>%
  ggplot(aes(trial_stim_frequency, region, fill = zscore)) +
  geom_tile() +
  scale_fill_gradientn(colors = c('blue', 'white', 'red'), limits = c(-6, 6),
                       oob = scales::squish) +
  theme_ag01() +
  facet_grid(group_combined ~ .) +
  coord_cartesian(xlim = c(0.5, 5.5), ylim = c(0.5, 6.5), expand = F) +
  force_panelsizes(cols = unit(plt_dims[1], 'cm'), rows = unit(plt_dims[2], 'cm')) +
  ylab('GRAB-DA Region') + xlab('LHA Stim Freq (Hz)') +
  ggtitle('Sustained (2–3s)')

save_pdf(dir_output_sfig04e, str_c(fn_stem_sfig04e_sust, '.pdf'), 12, 6)
plt_data %>% write_csv(str_c(dir_output_sfig04e, fn_stem_sfig04e_sust, '_data.csv'))
```

---

# Opto inhibition (fig2g, fig2h, fig2i, fig2j)

## preprocessing
```{r eval=FALSE}
# ── PREPROCESSING NOTE ────────────────────────────────────────────────────────
# The block below documents how the pre-computed CSVs in data/fig02/inhibition/ were
# produced. It requires TDT FP data from network storage and Google Sheets credentials.
# All paths are absolute, relative to the abo experiment root:
#   dir_exp_abo
#
# Source files:
#   TDT processed FP:  str_c(dir_tdt, 'data_processed/')
#   arduino extracted: str_c(dir_exp_abo, 'data/arduino/extracted/')
#   log_tdt:           Google Sheet (url_sheet_tdt)
#   log_subject:       Google Sheet (url_sheet_subject, sheet = 'subject')
# ─────────────────────────────────────────────────────────────────────────────

# preprocess <- 1
# 
# if (preprocess) {
#   library(googlesheets4)
#   log_tdt <- read_sheet(url_sheet_tdt, na = c('', 'NA'))
#   log_subject <- read_sheet(url_sheet_subject, sheet = 'subject', na = c('', 'NA'))
#
#   dir_output_abo_inh     <- str_c(dir_exp_abo, 'analysis_output_final/inhibition/')
#   dir_tdt_processed      <- str_c(dir_tdt, 'data_processed/')
#   dir_arduino_extraction <- str_c(dir_exp_abo, 'data/arduino/extracted/')
#   file_format_output  <- 'csv'
# 
#   # ── identify sessions (acd experiment, second session per subject) ─────────
#   import_fns <- log_tdt %>%
#     filter(experiment %in% c('acd')) %>%
#     filter(procedure == 'opto_characterization_inhibition') %>%
#     group_by(subject) %>%
#     filter(date == max(date)) %>%
#     pull(blockname) %>% unique()
# 
#   # ── build stim parameter table ─────────────────────────────────────────────
#   stim_params <- return_stim_params(import_fns, dir_arduino_extraction, file_format_output)
#   stim_params <- stim_params %>%
#     select(blockname, stim_num, trial_stim_frequency) %>%
#     filter(trial_stim_frequency != 0) %>%
#     arrange(blockname, stim_num)
# 
#   # ── import TDT streams ─────────────────────────────────────────────────────
#   data_list <- combined_import(
#     import_directory = dir_tdt_processed,
#     filter_strings   = import_fns,
#     prefixes  = NA,
#     suffixes  = c('streams_session.feather', 'streams_peth.feather', 'events.feather'),
#     verbose   = 0
#   )
#   streams      <- data_list[[1]] %>% ungroup()
#   streams_peth <- data_list[[2]] %>% ungroup()
#   events       <- data_list[[3]] %>% ungroup()
# 
#   # ── join region identity from log_tdt (TDT uses fiber_id01/02) ────────────
#   join_region <- log_tdt %>%
#     filter(experiment %in% c('acd')) %>%
#     filter(procedure == 'opto_characterization_inhibition') %>%
#     select(blockname, fiber_id01, fiber_id02) %>%
#     gather(fiber_id, region, starts_with('fiber_id')) %>%
#     mutate(fiber_id = fiber_id %>% str_remove('fiber_id0'))
# 
#   streams      <- streams      %>% left_join(join_region, join_by(blockname, fiber_id))
#   streams_peth <- streams_peth %>% left_join(join_region, join_by(blockname, fiber_id))
# 
#   streams_peth <- streams_peth %>%
#     left_join(log_tdt     %>% select(blockname, subject)) %>%
#     left_join(log_subject %>% select(subject, line)) %>%
#     filter(time_rel > -3, time_rel < 20)
# 
#   # ── local z-score (baseline: -3 to 0 s) ───────────────────────────────────
#   local_zs_window <- c(-3, 0)
#   streams_peth <- streams_peth %>%
#     group_by(blockname, signal_wavelength, region) %>%
#     filter(time_rel > local_zs_window[1], time_rel < local_zs_window[2]) %>%
#     summarise(
#       delta_signal_poly_local_bl_mu = mean(delta_signal_poly),
#       delta_signal_poly_local_bl_sd = sd(delta_signal_poly),
#       .groups = 'drop') %>%
#     left_join(streams_peth, ., by = c('blockname', 'signal_wavelength', 'region')) %>%
#     mutate(delta_signal_poly_zscore_local =
#              (delta_signal_poly - delta_signal_poly_local_bl_mu) /
#              delta_signal_poly_local_bl_sd) %>%
#     select(-delta_signal_poly_local_bl_mu, -delta_signal_poly_local_bl_sd)
# 
#   # ── subtract per-trial pre-stimulus baseline ───────────────────────────────
#   streams_peth <- streams_peth %>%
#     filter(time_rel > -3, time_rel < 0) %>%
#     group_by(blockname, event_number, region, signal_wavelength) %>%
#     summarise(bl = mean(delta_signal_poly_zscore_local), .groups = 'drop') %>%
#     left_join(streams_peth, .) %>%
#     mutate(delta_signal_poly_zscore_local = delta_signal_poly_zscore_local - bl) %>%
#     select(-bl) %>%
#     left_join(log_subject %>% select(subject, group), by = 'subject')
# 
#   # ── apply group labels, region labels, and placement filter ───────────────
#   streams_peth <- streams_peth %>% format_df()
#   streams_peth <- streams_peth %>% filter_placements()
# 
#   # ── compute summary data frames ───────────────────────────────────────────
#   streams_peth_summary <- streams_peth %>%
#     filter(time_rel > 2, time_rel < 10) %>%
#     group_by(blockname, subject, group_combined, line, group, region) %>%
#     summarise(delta_signal_poly_zscore_local = mean(delta_signal_poly_zscore_local),
#               .groups = 'drop')
# 
#   streams_peth <- streams_peth %>%
#     mutate(region = region %>% factor(levels = key_regions$region_label))
#   streams_peth_summary <- streams_peth_summary %>%
#     mutate(region = region %>% factor(levels = key_regions$region_label))
# 
#   streams_peth_subject <- streams_peth %>%
#     format_group_combined() %>%
#     group_by(group_combined, subject, region, time_rel) %>%
#     summarise(delta_signal_poly_zscore_local = mean(delta_signal_poly_zscore_local),
#               .groups = 'drop')
# 
#   streams_peth_group <- streams_peth %>%
#     format_group_combined() %>%
#     group_by(group_combined, region, time_rel) %>%
#     summarise(
#       delta_signal_poly_zscore_local_sem = sd(delta_signal_poly_zscore_local) / sqrt(n()),
#       delta_signal_poly_zscore_local     = mean(delta_signal_poly_zscore_local),
#       .groups = 'drop')
# 
#   # ── save pre-computed outputs ─────────────────────────────────────────────
#   streams_peth %>%
#     select(blockname, line, group, subject, fiber_id, region,
#            time, time_rel, event_number, delta_signal_poly_zscore_local) %>%
#     write_csv(str_c(dir_output_abo_inh, 'data_streams_peth_full.csv'))
# 
#   streams_peth_summary        %>% write_csv(str_c(dir_output_abo_inh, 'data_streams_peth_summary.csv'))
#   streams_peth_subject        %>% write_csv(str_c(dir_output_abo_inh, 'data_streams_peth_summary_trace_subject.csv'))
#   streams_peth_group          %>% write_csv(str_c(dir_output_abo_inh, 'data_streams_peth_summary_trace_group.csv'))
# 
# }
```

## import pre-computed data
```{r eval=FALSE}
# Note: group_combined is already in the summary CSVs; call format_group_combined()
# on the full trace data (line/group columns present, group_combined absent).
streams_peth <- read.csv(str_c(dir_data_inh, 'data_streams_peth_full.csv')) %>%
  format_group_combined() %>%
  mutate(region = region %>% factor(levels = key_regions$region_label))

streams_peth_summary <- read.csv(str_c(dir_data_inh, 'data_streams_peth_summary.csv')) %>%
  mutate(region = region %>% factor(levels = key_regions$region_label))

streams_peth_subject <- read.csv(str_c(dir_data_inh, 'data_streams_peth_summary_trace_subject.csv')) %>%
  mutate(region = region %>% factor(levels = key_regions$region_label))

streams_peth_group <- read.csv(str_c(dir_data_inh, 'data_streams_peth_summary_trace_group.csv')) %>%
  mutate(region = region %>% factor(levels = key_regions$region_label))
```

## summary of data in analysis
### fiber counts
```{r eval=FALSE}
streams_peth_summary %>%
  select(group_combined, region, subject) %>%
  unique() %>%
  group_by(group_combined, region) %>%
  summarise(region_count = n()) %>%
  ggplot(aes(region, group_combined, label = region_count)) +
  geom_text() +
  theme_ag01() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3)) +
  xlab('') + ylab('') +
  force_panelsizes(rows = unit(2, 'cm'), cols = unit(4, 'cm'))
```

---

## fig2g: inhibition trace (group mean ± SEM)
```{r eval=FALSE}
dir_output_g <- str_c(dir_output, 'g/')
fn_stem_g    <- 'opto_inh_trace'

plt_data <- streams_peth_group %>%
  filter(time_rel > -3, time_rel < 20)

plt <- plt_data %>%
  ggplot(aes(time_rel, delta_signal_poly_zscore_local, color = region, fill = region)) +
  annotate('rect', xmin = 0, xmax = 10, ymin = -Inf, ymax = Inf, alpha = 1/3, fill = 'darkgrey') +
  geom_hline(yintercept = 0, color = 'darkgrey', size = 0.5) +
  geom_ribbon(aes(ymax = delta_signal_poly_zscore_local + delta_signal_poly_zscore_local_sem,
                  ymin = delta_signal_poly_zscore_local - delta_signal_poly_zscore_local_sem),
              color = NA, alpha = 1/3) +
  geom_line() +
  facet_grid(. ~ group_combined) +
  theme_ag01() +
  scale_color_manual(values = color_values_regions_da) +
  scale_fill_manual(values = color_values_regions_da)

plt <- plt %>%
  add_scale_bar(origin = c(-3, -2), x_len = 1, y_len = 1)

plt +
  force_panelsizes(cols = unit(plt_dims[1], 'cm'), rows = unit(plt_dims[2] * 1.8, 'cm'))

save_pdf(dir_output_g, str_c(fn_stem_g, '.pdf'), 12, 6)
plt_data %>% write_csv(str_c(dir_output_g, fn_stem_g, '_data.csv'))
```

---

## fig2h: inhibition summary bar (sustained 2–10 s)
```{r eval=FALSE}
dir_output_h <- str_c(dir_output, 'h/')
fn_stem_h    <- 'opto_inh_region_bar_sustained'

plt_data <- streams_peth_summary %>%
  rename(zscore = delta_signal_poly_zscore_local)

plt_data %>%
  ggplot(aes(region, zscore, color = group_combined, fill = group_combined)) +
  geom_hline(yintercept = 0, alpha = 1/3) +
  geom_hline(yintercept = -6.96) +
  stat_summary(fun.data = 'mean_se', geom = 'errorbar', aes(group = group_combined),
               width = 0.3, position = position_dodge(width = 0.75)) +
  stat_summary(fun = 'mean', geom = 'bar', color = NA, aes(group = group_combined),
               alpha = 1/2, width = 0.6, position = position_dodge(width = 0.75)) +
  geom_jitter(shape = 21, color = 'white', size = 1.5, stroke = 0.25,
              position = position_jitterdodge(jitter.width = 0.04, jitter.height = 0,
                                              dodge.width = 0.75)) +
  theme_ag01(6) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3)) +
  scale_color_manual(values = color_group_combined) +
  scale_fill_manual(values = color_group_combined) +
  coord_cartesian(xlim = c(0.5, 6.5), ylim = c(-10, 5), expand = F, clip = 'off') +
  force_panelsizes(cols = unit(3, 'cm'), rows = unit(2.5+1.25, 'cm')) +
  scale_y_continuous(breaks = c(-6.96,-5, -2.5,0,2.5, 5)) +
  ylab('Z-Score') + xlab('') + ggtitle('Sustained (2–10s)')

save_pdf(dir_output_h, str_c(fn_stem_h, '.pdf'), 8, 6)
plt_data %>% write_csv(str_c(dir_output_h, fn_stem_h, '_data.csv'))
```

```{r eval=FALSE}
# ── Wilcoxon unpaired: control vs. vgat_inh and vglut2_inh per region ─────────
loop_regions <- plt_data %>% pull(region) %>% unique()

for (loop_region in loop_regions) {
  plt_data_wide <- plt_data %>%
    select(region, subject, group_combined, zscore) %>%
    spread(group_combined, zscore) %>%
    filter(region == loop_region)

  loop_result <- bind_rows(
    plt_data_wide %>%
      tidy_wilcox_unpaired('control', 'vgat_inh') %>%
      mutate(comparision = 'control_vs_vgat'),
    plt_data_wide %>%
      tidy_wilcox_unpaired('control', 'vglut2_inh') %>%
      mutate(comparision = 'control_vs_vglut2')
  ) %>%
    clean_names() %>%
    mutate(region = loop_region) %>%
    select(region, comparision, everything()) %>%
    mutate(p_value = p_value * 2) %>%
    quick_sig()

  if (loop_region == loop_regions[1]) {
    combined_result <- loop_result
  } else {
    combined_result <- bind_rows(combined_result, loop_result)
  }
}

combined_result %>%
  mutate(region = region %>% factor(levels = key_regions$region_label)) %>%
  ggplot(aes(region, comparision, label = sig_symbol)) +
  geom_text()

combined_result %>% write_csv(str_c(dir_output_h, fn_stem_h, '_stats.csv'))
```

---

## fig2i: placement maps (3D and 2D, sustained z-score 2–10 s)
```{r eval=FALSE}
dir_output_i <- str_c(dir_output, 'i/')

fn_stem_i <- 'placement_vs_zscore_sustained'

for (loop_group in c('control', 'vgat_inh', 'vglut2_inh')) {

  df <- streams_peth_summary %>%
    filter(group_combined == loop_group) %>%
    rename(zscore = delta_signal_poly_zscore_local) %>%
    join_placements() %>%
    select(subject, group_combined, region, zscore, starts_with('hit')) %>%
    mutate(region = region %>% factor(levels = key_regions$region_label))

  var_color    <- 'zscore'
  color_limits <- c(-3, 3)

  for (plt_plane in c('sagittal', 'horizontal', 'coronal')) {
    plt_str(
      df           = df,
      var_color    = !!sym(var_color),
      var_color_name = 'z-score',
      vars_facet   = c('.', '.'),
      plt_plane    = plt_plane,
      plt_dim_base = 3,
      color_limits = color_limits
    )
    save_pdf(dir_output_i,
             str_c(fn_stem_i, '_', loop_group, '_', plt_plane, '.pdf'), 6, 6)
  }

  tryCatch(
    plt_str_3d(
      df           = df,
      var_color    = var_color,
      color_limits = color_limits,
      dir_output   = dir_output_i,
      fn_stem      = str_c(fn_stem_i, '_', loop_group),
      toggle_save  = 1
    ),
    error = function(e) message('plt_str_3d skipped (kaleido): ', conditionMessage(e))
  )
}
```

---

## fig2j: placement × response correlation (sustained z-score 2–10 s)
```{r eval=FALSE}
dir_output_j <- str_c(dir_output, 'j/')
fn_stem_j    <- 'placement_vs_zscore_sustained_corr'

plt_data <- streams_peth_summary %>%
  rename(zscore = delta_signal_poly_zscore_local) %>%
  join_placements()

plt_list <- plt_corr(
  df             = plt_data,
  ylim_all       = c(-4, 4),
  xlim_ap        = c(-3, 0, 3),
  xlim_ml        = c(0, 2, 4),
  xlim_dv        = c(-6, -4, -2),
  var_dep        = 'zscore',
  var_dep_label  = 'Z-Score',
  plt_dims       = c(3, 3 * 2/3),
  cor_text_y     = 4
)

plt_list[['AP']] +
  plt_list[['ML']] +
  plt_list[['DV']] +
  plot_layout(nrow = 1, widths = unit(1.5, 'cm'), heights = unit(3, 'cm'),
              guides = 'collect')

save_pdf(dir_output_j, str_c(fn_stem_j, '.pdf'), 6, 6)
plt_data                   %>% write_csv(str_c(dir_output_j, fn_stem_j, '_data.csv'))
plt_list[['stats_output']] %>% write_csv(str_c(dir_output_j, fn_stem_j, '_stats.csv'))
```


---

# Integration: +/- CNO inhbition & opto stim characterization (sfig04g, sfig04h)

## preprocessing
```{r eval=FALSE}
# ── PREPROCESSING NOTE ────────────────────────────────────────────────────────
# The block below documents how the pre-computed CSVs in data/fig02_sfig04/acp/ were
# produced. It requires raw FP data from network storage and Google Sheets credentials.
# All paths are absolute, relative to the acp experiment root:
#   dir_exp_acp
#
# Source files:
#   npm processed FP:  str_c(dir_npm, 'data_processed/')
#   arduino extracted: str_c(dir_exp_acp, 'data/arduino/extracted/')
#   log_npm:           Google Sheet (url_sheet_npm)
#   log_subject:       Google Sheet (url_sheet_subject)
#   log_placements:    Google Sheet (url_sheet_placements)
#
# Note: filter_placements() here has a different signature from the fig02-local version:
#   filter_placements(df, log_placements, values_inclusion = c(0, 3))
#   Keeps fibers where exclude_da_consumption is 0 (keep) or 3 (ok for this analysis).
# ─────────────────────────────────────────────────────────────────────────────

# preprocess <- 1
#
# if (preprocess) {
#   library(googlesheets4)
#   log_npm        <- read_sheet(url_sheet_npm, na = c('', 'NA'))
#   log_subject    <- read_sheet(url_sheet_subject, na = c('', 'NA'))
#   log_placements <- read_sheet(url_sheet_placements, na = c('', 'NA'))
#
#   dir_output_acp         <- str_c(dir_exp_acp, 'analysis_output_final/')
#   dir_npm_processed      <- str_c(dir_npm, 'data_processed/')
#   dir_arduino_extraction <- str_c(dir_exp_acp, 'data/arduino/extracted/')
#   file_format_output     <- 'csv'
#
#   # ── identify sessions ──────────────────────────────────────────────────────
#   import_fns <- log_npm %>%
#     filter(experiment %in% c('acp')) %>%
#     filter(procedure %in% c(
#       'stim_characterization_01_veh',
#       'stim_characterization_02_cno',
#       'stim_characterization_03_veh'
#     )) %>%
#     pull(blockname) %>% unique()
#
#   stim_params <- return_stim_params(import_fns, dir_arduino_extraction, file_format_output)
#   stim_params <- stim_params %>%
#     select(blockname, stim_num, trial_stim_frequency) %>%
#     filter(trial_stim_frequency != 0) %>%
#     arrange(blockname, stim_num) %>%
#     group_by(blockname)
#
#   # ── import raw FP streams ──────────────────────────────────────────────────
#   data_list <- combined_import(
#     import_directory = dir_npm_processed,
#     filter_strings   = import_fns,
#     prefixes  = NA,
#     suffixes  = c('streams_session.feather', 'streams_peth.feather', 'events.feather'),
#     verbose   = 0
#   )
#   streams      <- data_list[[1]]
#   streams_peth <- data_list[[2]]
#   events       <- data_list[[3]]
#   rm(data_list)
#
#   streams <- streams %>%
#     mutate(subject = blockname %>% str_sub(12, 16)) %>%
#     left_join(log_npm %>% select(blockname, branch_id, region)) %>%
#     mutate(region = region %>% factor(
#       levels = c('nac_shelllat', 'nac', 'nac_corr', 'dms', 'dls', 'ts'))) %>%
#     format_regions('region', key_regions)
#
#   streams_peth <- streams_peth %>%
#     mutate(subject = blockname %>% str_sub(12, 16)) %>%
#     left_join(log_npm %>% select(blockname, branch_id, region)) %>%
#     mutate(region = region %>% factor(
#       levels = c('nac_shelllat', 'nac', 'nac_corr', 'dms', 'dls', 'ts'))) %>%
#     filter(time_rel > -3, time_rel < 12)
#
#   events <- events %>%
#     group_by(blockname) %>%
#     filter(event_id_char %in% c('opto_stim', 'trial_start')) %>%
#     arrange(blockname, event_ts) %>%
#     mutate(stim_num = row_number()) %>%
#     left_join(stim_params, by = c('blockname', 'stim_num'))
#
#   streams_peth <- streams_peth %>%
#     left_join(events %>% select(blockname, event_number, trial_stim_frequency)) %>%
#     filter(!is.na(trial_stim_frequency))
#
#   # ── local z-score (baseline: -3 to 0 s) ───────────────────────────────────
#   local_zs_window <- c(-3, 0)
#   streams_peth <- streams_peth %>%
#     group_by(blockname, signal_wavelength, region) %>%
#     filter(time_rel > local_zs_window[1], time_rel < local_zs_window[2]) %>%
#     summarise(
#       delta_signal_poly_local_bl_mu = mean(delta_signal_poly),
#       delta_signal_poly_local_bl_sd = sd(delta_signal_poly),
#       .groups = 'drop'
#     ) %>%
#     left_join(streams_peth, ., by = c('blockname', 'signal_wavelength', 'region')) %>%
#     mutate(delta_signal_poly_zscore_local =
#              (delta_signal_poly - delta_signal_poly_local_bl_mu) /
#              delta_signal_poly_local_bl_sd) %>%
#     select(-delta_signal_poly_local_bl_mu, -delta_signal_poly_local_bl_sd)
#
#   # ── subtract per-trial pre-stimulus baseline ───────────────────────────────
#   streams_peth <- streams_peth %>%
#     filter(time_rel > -3, time_rel < 0) %>%
#     group_by(blockname, event_number, region, signal_wavelength) %>%
#     summarise(bl = mean(delta_signal_poly_zscore_local), .groups = 'drop') %>%
#     left_join(streams_peth, .) %>%
#     mutate(delta_signal_poly_zscore_local = delta_signal_poly_zscore_local - bl) %>%
#     select(-bl)
#
#   # ── join group, procedure; format regions; filter placements ──────────────
#   streams_peth <- streams_peth %>%
#     left_join(log_subject %>% select(subject, group), by = 'subject') %>%
#     left_join(log_npm %>% select(blockname, procedure) %>% unique()) %>%
#     format_regions('region', key_regions)
#
#   streams_peth <- streams_peth %>%
#     filter_placements(log_placements, values_inclusion = c(0, 3))
#
#   # ── compute summary data frames ───────────────────────────────────────────
#   streams_peth_summary <- streams_peth %>%
#     filter(time_rel > 0, time_rel < 3) %>%
#     group_by(blockname, procedure, subject, group, trial_stim_frequency, region) %>%
#     summarise(delta_signal_poly_zscore_local = mean(delta_signal_poly_zscore_local), .groups = 'drop') %>%
#     mutate(trial_stim_frequency =
#              as.character(trial_stim_frequency) %>% factor(levels = c(0,1,2,5,10,20,40)))
#
#   streams_peth <- streams_peth %>%
#     mutate(region = region %>% factor(levels = key_regions$region_label))
#   streams_peth_summary <- streams_peth_summary %>%
#     mutate(region = region %>% factor(levels = key_regions$region_label))
#
#   streams_peth_subject <- streams_peth %>%
#     group_by(group, procedure, subject, region, time_rel, trial_stim_frequency) %>%
#     summarise(delta_signal_poly_zscore_local = mean(delta_signal_poly_zscore_local), .groups = 'drop')
#
#   streams_peth_group <- streams_peth %>%
#     group_by(group, procedure, region, time_rel, trial_stim_frequency) %>%
#     summarise(
#       delta_signal_poly_zscore_local_sem = sd(delta_signal_poly_zscore_local) / sqrt(n()),
#       delta_signal_poly_zscore_local     = mean(delta_signal_poly_zscore_local),
#       .groups = 'drop')
#
#   # ── save pre-computed outputs ─────────────────────────────────────────────
#   streams_peth %>%
#     select(blockname, group, procedure, subject, branch_id, region,
#            time, time_rel, event_number, trial_stim_frequency,
#            delta_signal_poly_zscore_local) %>%
#     write_csv(str_c(dir_output_acp, 'data_streams_peth_full.csv'))
#
#   streams_peth_summary       %>% write_csv(str_c(dir_output_acp, 'data_streams_peth_summary.csv'))
#   streams_peth_subject       %>% write_csv(str_c(dir_output_acp, 'data_streams_peth_summary_trace_subject.csv'))
#   streams_peth_group         %>% write_csv(str_c(dir_output_acp, 'data_streams_peth_summary_trace_group.csv'))
#
# }
```

## import pre-computed data
```{r eval=FALSE}
streams_peth <- read.csv(str_c(dir_data_interaction, 'data_streams_peth_full.csv')) %>%
  mutate(region = region %>% factor(levels = key_regions$region_label))

streams_peth_summary <- read.csv(str_c(dir_data_interaction, 'data_streams_peth_summary.csv')) %>%
  mutate(region = region %>% factor(levels = key_regions$region_label))

streams_peth_subject <- read.csv(str_c(dir_data_interaction, 'data_streams_peth_summary_trace_subject.csv')) %>%
  mutate(region = region %>% factor(levels = key_regions$region_label))

streams_peth_group <- read.csv(str_c(dir_data_interaction, 'data_streams_peth_summary_trace_group.csv')) %>%
  mutate(region = region %>% factor(levels = key_regions$region_label))
```

## keys (interaction specific)
```{r eval=FALSE}
# Group color palette: EYFP (control) = darkgrey, hM4Di (CNO-sensitive) = darkblue
color_group <- c('darkgrey', 'darkblue')

# format_procedures: converts raw procedure string to ordered factor label
format_procedures <- function(df) {
  key_procedures <- tibble(
    procedure       = c('stim_characterization_01_veh', 'stim_characterization_02_cno',
                        'stim_characterization_03_veh', 'stim_characterization_04_veh',
                        'stim_characterization_05_dcz'),
    procedure_label = c('Veh', 'CNO', 'Veh Post', 'V', 'DCZ')
  )
  df %>%
    left_join(key_procedures, by = 'procedure') %>%
    mutate(procedure_label = factor(procedure_label, levels = key_procedures$procedure_label)) %>%
    select(-procedure) %>%
    rename(procedure = procedure_label) %>%
    select(procedure, everything())
}
```

---

## sfig04g: CNO delta trace (20 Hz)
```{r eval=FALSE}
dir_output_sfig04g <- str_c(dir_output, 'sfig04g/')
fn_stem_sfig04g    <- 'opto20hz_timerel_vs_delta_trace'

plt_data <- streams_peth_subject %>%
  format_procedures() %>%
  filter(trial_stim_frequency == 20) %>%
  filter(time_rel > -1, time_rel < 6) %>%
  filter(procedure %in% c('Veh', 'CNO')) %>%
  select(subject, group, region, time_rel, procedure, delta_signal_poly_zscore_local) %>%
  spread(procedure, delta_signal_poly_zscore_local) %>%
  mutate(cno_minus_veh = CNO - Veh)

plt <- plt_data %>%
  ggplot(aes(time_rel, cno_minus_veh, color = group, fill = group, group = group)) +
  annotate('rect', xmin = 0, xmax = 3, ymin = -Inf, ymax = Inf, alpha = 1/3, fill = 'darkgrey') +
  geom_hline(yintercept = 0, color = 'darkgrey', size = 0.5) +
  stat_summary(fun.data = 'mean_se', geom = 'ribbon', color = NA, alpha = 1/3) +
  stat_summary(fun = 'mean', geom = 'line') +
  scale_color_manual(values = color_group) +
  scale_fill_manual(values = color_group) +
  facet_grid(. ~ region) +
  theme_ag01()

plt <- plt %>%
  add_scale_bar(origin = c(-1, -2), x_len = 1, y_len = 1)

plt +
  force_panelsizes(cols = unit(1, 'cm'), rows = unit(5, 'cm'))

save_pdf(dir_output_sfig04g, str_c(fn_stem_sfig04g, '.pdf'), 12, 6)
plt_data %>% write_csv(str_c(dir_output_sfig04g, fn_stem_sfig04g, '_data.csv'))
```

---

## sfig04h: CNO delta summary (sustained 0-3 s)
```{r eval=FALSE}
dir_output_sfig04h <- str_c(dir_output, 'sfig04h/')
fn_stem_sfig04h    <- 'opto20hz_timerel_vs_delta_summary'

plt_data <- streams_peth %>%
  filter(time_rel > 0, time_rel <= 3) %>%
  group_by(subject, procedure, group, trial_stim_frequency, region, branch_id) %>%
  summarise(delta_signal_poly_zscore_local = mean(delta_signal_poly_zscore_local), .groups = 'drop') %>%
  mutate(trial_stim_frequency =
           as.character(trial_stim_frequency) %>% factor(levels = c(0,1,2,5,10,20,40))) %>%
  rename(zscore = delta_signal_poly_zscore_local) %>%
  format_procedures()

plt_data_diff <- plt_data %>%
  filter(trial_stim_frequency == 20) %>%
  filter(procedure %in% c('Veh', 'CNO')) %>%
  spread(procedure, zscore) %>%
  mutate(cno_minus_veh = CNO - Veh)

plt_data_diff %>%
  ggplot(aes(region, cno_minus_veh, color = group, fill = group)) +
  geom_hline(yintercept = 0, alpha = 1/3) +
  stat_summary(fun.data = 'mean_se', geom = 'errorbar', aes(group = group),
               width = 0.3, position = position_dodge(width = 0.75)) +
  stat_summary(fun = 'mean', geom = 'bar', color = NA, aes(group = group),
               alpha = 1/2, width = 0.6, position = position_dodge(width = 0.75)) +
  geom_jitter(shape = 21, color = 'white', size = 1.5, stroke = 0.25,
              position = position_jitterdodge(jitter.width = 0.04, jitter.height = 0,
                                              dodge.width = 0.75)) +
  theme_ag01(6) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3)) +
  scale_color_manual(values = color_group) +
  scale_fill_manual(values = color_group) +
  coord_cartesian(xlim = c(0.5, 6.5), ylim = c(-12, 4), expand = F, clip = 'off') +
  force_panelsizes(cols = unit(45, 'mm'), rows = unit(20, 'mm')) +
  ylab('CNO - Veh.') + xlab('') + ggtitle('Full (0-3s)')

save_pdf(dir_output_sfig04h, str_c(fn_stem_sfig04h, '.pdf'), 12, 6)
plt_data_diff %>% write_csv(str_c(dir_output_sfig04h, fn_stem_sfig04h, '_data.csv'))
```

```{r eval=FALSE}
# ── fiber × region counts ──────────────────────────────────────────────────────
plt_data_diff %>%
  group_by(group, region) %>%
  summarise(count = n(), .groups = 'drop') %>%
  spread(region, count)
```

```{r eval=FALSE}
# ── two-between ANOVA: group × region on CNO - Veh delta ──────────────────────
plt_data_diff %>%
  mutate(subject = subject %>% str_c(row_number())) %>%
  aov_rm_two_between(dir_output_sfig04h, fn_stem_sfig04h,
                     'subject', 'cno_minus_veh', 'group', 'region')
```
