---
title: "fig07"
author: "adam gordon-fennell"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = normalizePath('../'))
```

# setup
## libraries
```{r eval=FALSE}
library(tidyverse)
library(afex)
library(emmeans)
library(janitor)
library(readxl)
library(ggh4x)
library(arrow)
library(zoo)
library(lubridate)
library(patchwork)
library(ggbeeswarm)
library(ggpubr)
library(pals)
library(boot)
library(corrplot)
library(Hmisc)
library(plotly)

arrow::set_cpu_count(4)

source('./functions/params.R')
source('./functions/theme.R')
source('./functions/general.R')
source('./functions/r_general.R')
source('./functions/r_plots.R')
source('./functions/stats.R')
source('./functions/pca.R')
source('./functions/analysis_peth.R')
source('./functions/plotting_placements.R')
```

## directories
```{r eval=FALSE}
dir_sessions_combined_subject <- './data/sessions_combined_subject/'
dir_output                    <- './analysis_and_plots/fig07/'

dir.create(dir_output, recursive = TRUE, showWarnings = FALSE)
```

## logs / keys
```{r eval=FALSE}
log_placements <- read.csv('./logs_and_keys/log_fiber_placements.csv', na.strings = c('', 'NA'))
```

## local functions
```{r eval=FALSE}
# plt_line_pairwise: NOT in repo functions (repo has plt_bar_pairwise which uses aov_rm_one_between)
# this version uses aov_rm_one_within for within-subject stats per region
plt_line_pairwise <- function(df, dir_output, fn_stem, var_id = 'subject', var_dv, var_within, ylims, heat_range = NA) {

  n_within <- df %>%
    pull(!!as.name(var_within)) %>%
    unique() %>%
    length()

  pltline <- df %>%
    ggplot(aes(region, !!as.name(var_dv))) +
    geom_line(aes(group = !!as.name(var_id)), alpha = 1/4) +
    stat_summary(fun = 'mean', geom = 'line', aes(group = 1)) +
    stat_summary(fun.data = 'mean_se', geom = 'errorbar', aes(group = 1), width = 0) +
    theme_ag01(6) +
    theme(axis.title.x = element_blank(),
          axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3)) +
    coord_cartesian(xlim = c(0.5, n_within + 0.5), ylim = ylims, expand = F)

  stats_results <- df %>%
    aov_rm_one_within(dir_output, fn_stem, var_id, var_dv, var_within)

  df_pairs <- stats_results[[3]] %>%
    format_regions('contrast1_within', key_regions) %>%
    format_regions('contrast2_within', key_regions)

  plt_comparisions <- plt_hsd_matrix_2contrasts(df_pairs, heat_range)

  return(list(stats_results, pltline, plt_comparisions))
}
```

---

# STR correlation [fig7 B-F]
## preprocessing
```{r eval=FALSE}
toggle_process <- 0   # 1 = load from sessions_combined_subject and save  |  0 = CSVs already exist

dir_output_pre <- str_c(dir_output, 'pre/')
dir.create(dir_output_pre, recursive = TRUE, showWarnings = FALSE)
```

```{r eval=FALSE}
if (toggle_process == 1) {

  # ── 1. STR baseline correlation ───────────────────────────────────────────────
  fns_streams_bl_corr <- list.files(dir_sessions_combined_subject,
                                    pattern = 'streams_baseline_corr.csv',
                                    recursive = T, full.names = T)
  fns_streams_bl_corr <- fns_streams_bl_corr[!fns_streams_bl_corr %>% str_detect('lhastr')]

  bind_rows(lapply(fns_streams_bl_corr, read.csv)) %>%
    filter(set_id %in% c('wrnacl', 'wrsuc', 'frsuc')) %>%
    format_set_id(key_set_id) %>%
    mutate(
      var_x = var_x %>% factor(levels = key_regions$region_label %>% unique()),
      var_y = var_y %>% factor(levels = key_regions$region_label %>% unique())
    ) %>%
    write_csv(str_c(dir_output_pre, 'str_baseline_corr.csv'))

  # ── 2. STR peth corr timerel ──────────────────────────────────────────────────
  fns_streams_peth_corr_timerel <- list.files(dir_sessions_combined_subject,
                                              pattern = 'streams_peth_corr_timerel.csv',
                                              recursive = T, full.names = T)
  fns_streams_peth_corr_timerel <- fns_streams_peth_corr_timerel[!fns_streams_peth_corr_timerel %>% str_detect('lhastr')]

  bind_rows(lapply(fns_streams_peth_corr_timerel, read.csv)) %>%
    filter(set_id %in% c('wrnacl', 'wrsuc', 'frsuc')) %>%
    format_set_id(key_set_id) %>%
    mutate(
      var_x = var_x %>% factor(levels = key_regions$region_label %>% unique()),
      var_y = var_y %>% factor(levels = key_regions$region_label %>% unique())
    ) %>%
    write_csv(str_c(dir_output_pre, 'str_peth_corr_timerel.csv'))

  # ── 3. STR peth corr windows ─────────────────────────────────────────────────
  fns_streams_peth_corr_windows <- list.files(dir_sessions_combined_subject,
                                              pattern = 'streams_peth_corr_windows.csv',
                                              recursive = T, full.names = T)
  fns_streams_peth_corr_windows <- fns_streams_peth_corr_windows[!fns_streams_peth_corr_windows %>% str_detect('lhastr')]

  bind_rows(lapply(fns_streams_peth_corr_windows, read.csv)) %>%
    filter(set_id %in% c('wrnacl', 'wrsuc', 'frsuc')) %>%
    format_set_id(key_set_id) %>%
    mutate(
      var_x = var_x %>% factor(levels = key_regions$region_label %>% unique()),
      var_y = var_y %>% factor(levels = key_regions$region_label %>% unique())
    ) %>%
    write_csv(str_c(dir_output_pre, 'str_peth_corr_windows.csv'))

  # ── 4. placement distances ────────────────────────────────────────────────────
  loop_log_placements <- log_placements %>%
    select(subject, region = target, starts_with('hit'))

  df_distances <- loop_log_placements %>%
    group_by(subject) %>%
    group_modify(~ calculate_pairwise_distances(.x)) %>%
    mutate(region1 = region1 %>% factor(levels = levels_region)) %>%
    mutate(region2 = region2 %>% factor(levels = levels_region))

  df_distances <- df_distances %>%
    rename(region2_dummy = region1) %>%
    rename(region1 = region2) %>%
    rename(region2 = region2_dummy) %>%
    bind_rows(df_distances) %>%
    unique() %>%
    mutate(region1 = region1 %>% as.character(),
           region2 = region2 %>% as.character())

  df_distances %>%
    write_csv(str_c(dir_output_pre, 'placement_distances.csv'))

} else {
  message('toggle_process = 0: preprocessing CSVs will be read by each section')
}
```

---

## fig7b: mean r peth trace
```{r eval=FALSE}
dir_output_b <- str_c(dir_output, 'b/')
dir.create(dir_output_b, recursive = TRUE, showWarnings = FALSE)

fn_stem <- 'cor_peth_setid'

plt_data <- read.csv(str_c(dir_output_pre, 'str_peth_corr_timerel.csv')) %>%
  mutate(
    set_id = set_id %>% factor(levels = key_set_id$set_id_label %>% unique()),
    var_x  = var_x  %>% factor(levels = key_regions$region_label %>% unique()),
    var_y  = var_y  %>% factor(levels = key_regions$region_label %>% unique())
  ) %>%
  filter(var_x != var_y) %>%
  group_by(subject, set_id, time_rel) %>%
  summarise(r = mean(r))

plt_data %>%
  ggplot(aes(time_rel, r, color = set_id, fill = set_id, group = set_id)) +
  geom_hline(yintercept = c(0.2, 0.4, 0.6), color = 'darkgrey', size = 1/3) +
  annotate("rect", xmin = 0, xmax = 3, ymin = -Inf, ymax = Inf, alpha = 1/3, fill = "darkgrey") +
  stat_summary(fun.data = 'mean_se', geom = 'ribbon', color = NA, alpha = 1/3) +
  stat_summary(fun = 'mean', geom = 'line') +
  scale_color_manual(values = color_values_experiment_set) +
  scale_fill_manual(values = color_values_experiment_set) +
  theme_ag01(6) +
  force_panelsizes(rows = unit(2, 'cm'), cols = unit(2, 'cm')) +
  coord_cartesian(xlim = c(-3, 9), ylim = c(0, 0.6), expand = F) +
  scale_y_continuous(breaks = seq(0, 0.6, 0.2)) +
  ylab('Mean R') +
  xlab('Time (s)')

save_pdf(dir_output_b, str_c(fn_stem, '_trace.pdf'), 6, 4)
plt_data %>% write_csv(str_c(dir_output_b, fn_stem, '_trace_data.csv'))
```

---

## fig7c: consumption correlation heat map (WR:NaCl, Sustained)
```{r eval=FALSE}
dir_output_c <- str_c(dir_output, 'c/')
dir.create(dir_output_c, recursive = TRUE, showWarnings = FALSE)

fn_stem <- 'cor_peth_setid'

plt_data_windows <- read.csv(str_c(dir_output_pre, 'str_peth_corr_windows.csv')) %>%
  mutate(
    set_id       = set_id       %>% factor(levels = c('FR:Suc', 'WR:Suc', 'WR:NaCl')),
    time_rel_bin = time_rel_bin %>% factor(levels = c('Pre', 'Sustained', 'Post')),
    var_x        = var_x        %>% factor(levels = key_regions$region_label %>% unique()),
    var_y        = var_y        %>% factor(levels = key_regions$region_label %>% unique())
  )

plt_data_summary <- plt_data_windows %>%
  filter(set_id == 'WR:NaCl', time_rel_bin == 'Sustained') %>%
  group_by(set_id, time_rel_bin, var_x, var_y) %>%
  summarise(r = mean(r), .groups = 'drop')

plt_corrmatrix(plt_data_summary) +
  facet_grid(time_rel_bin ~ set_id) +
  ggtitle('Consumption correlation /n') +
  coord_cartesian(xlim = c(0.5, 6.5), ylim = c(0.5, 6.5), expand = F) +
  force_panelsizes(rows = unit(2, 'cm'), cols = unit(2, 'cm'))

save_pdf(dir_output_c, str_c(fn_stem, '_heat.pdf'), 6, 4)
plt_data_summary %>% write_csv(str_c(dir_output_c, fn_stem, '_heat_data.csv'))
```

---

## fig7d: set_id vs mean R (sustained)
```{r eval=FALSE}
dir_output_d <- str_c(dir_output, 'd/')
dir.create(dir_output_d, recursive = TRUE, showWarnings = FALSE)

fn_stem <- 'cor_peth_setid'

plt_data_subject <- read.csv(str_c(dir_output_pre, 'str_peth_corr_windows.csv')) %>%
  mutate(
    set_id       = set_id       %>% factor(levels = c('FR:Suc', 'WR:Suc', 'WR:NaCl')),
    time_rel_bin = time_rel_bin %>% factor(levels = c('Pre', 'Sustained', 'Post')),
    var_x        = var_x        %>% factor(levels = key_regions$region_label %>% unique()),
    var_y        = var_y        %>% factor(levels = key_regions$region_label %>% unique())
  ) %>%
  filter(var_x != var_y) %>%
  group_by(subject, set_id, time_rel_bin, var_x, var_y) %>%
  summarise(r = mean(r), .groups = 'drop') %>%
  group_by(subject, set_id, time_rel_bin) %>%
  summarise(r = mean(r), .groups = 'drop')

plt_data_temp <- plt_data_subject %>%
  filter(time_rel_bin == 'Sustained')

plt_data_temp %>%
  ggplot(aes(set_id, r, group = 1)) +
  geom_line(aes(group = subject), alpha = 1/3, size = 1/3) +
  stat_summary(fun = 'mean', geom = 'line') +
  stat_summary(fun.data = 'mean_se', geom = 'errorbar', width = 0) +
  theme_ag01(6) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3)) +
  coord_cartesian(xlim = c(0.5, 3.5), ylim = c(0, 1), expand = F) +
  scale_y_continuous(breaks = seq(0, 1, 0.25)) +
  xlab('') +
  ylab('Mean R') +
  force_panelsizes(rows = unit(2, 'cm'), cols = unit(1, 'cm'))

save_pdf(dir_output_d, str_c(fn_stem, '_summary_sustained.pdf'), 6, 4)
plt_data_temp %>% write_csv(str_c(dir_output_d, fn_stem, '_summary_sustained_data.csv'))
```

```{r eval=FALSE}
plt_data_temp %>%
  aov_rm_one_within(dir_output_d, str_c(fn_stem, '_summary_sustained'), 'subject', 'r', 'set_id')
```

---

## fig7e: region vs pairwise mean R (sustained)
```{r eval=FALSE}
dir_output_e <- str_c(dir_output, 'e/')
dir.create(dir_output_e, recursive = TRUE, showWarnings = FALSE)

fn_stem <- 'cor_peth_sustained_pairwisecor'

# build pairwise correlation data from peth windows (sustained)
plt_data_windows <- read.csv(str_c(dir_output_pre, 'str_peth_corr_windows.csv')) %>%
  mutate(
    set_id       = set_id       %>% factor(levels = c('FR:Suc', 'WR:Suc', 'WR:NaCl')),
    time_rel_bin = time_rel_bin %>% factor(levels = c('Pre', 'Sustained', 'Post')),
    var_x        = var_x        %>% factor(levels = key_regions$region_label %>% unique()),
    var_y        = var_y        %>% factor(levels = key_regions$region_label %>% unique())
  ) %>%
  filter(var_x != var_y, time_rel_bin == 'Sustained', set_id =='WR:NaCl')

regions <- unique(plt_data_windows$var_x)

for (region in regions) {
  loop_df <- plt_data_windows %>%
    filter(var_x == region | var_y == region) %>%
    mutate(pairwise_region01 = region) %>%
    mutate(pairwise_region02 = case_when(
      var_x == region ~ var_y,
      var_y == region ~ var_x
    )) %>%
    select(-var_x, -var_y)

  if (region == regions[1]) {
    cor_pairwise <- loop_df
  } else {
    cor_pairwise <- bind_rows(cor_pairwise, loop_df)
  }
}

cor_pairwise <- cor_pairwise %>%
  group_by(subject, pairwise_region01, pairwise_region02) %>%
  summarise(r = mean(r), .groups = 'drop') %>%
  mutate(pairwise_region01 = pairwise_region01 %>% factor(levels = key_regions$region_label %>% unique()))

plt_data_summary <- cor_pairwise %>%
  group_by(subject, pairwise_region01) %>%
  summarise(r = mean(r), .groups = 'drop')

key_regions_crosswise <- key_regions %>%
  filter(region != 'nacsh_lat')

plt_pairwise <- plt_line_pairwise(
  df         = plt_data_summary %>% left_join(key_regions_crosswise %>% rename(pairwise_region01 = region_label)),
  dir_output = dir_output_e,
  fn_stem    = fn_stem,
  var_dv     = 'r',
  var_within = 'region',
  ylims      = c(-1, 1)
)

plt_line <- plt_data_summary %>%
  ggplot(aes(pairwise_region01, r, group = 1)) +
  geom_hline(yintercept = 0, color = 'darkgrey', size = 1/3) +
  geom_line(aes(group = subject), size = 1/2, alpha = 1/3) +
  stat_summary(fun = 'mean', geom = 'line') +
  stat_summary(fun.data = 'mean_se', geom = 'errorbar', width = 0) +
  theme_ag01(6) +
  force_panelsizes(rows = unit(3, 'cm'), cols = unit(3, 'cm')) +
  coord_cartesian(xlim = c(0, 7), ylim = c(-0.5, 1), expand = F, clip = 'off') +
  scale_color_manual(values = color_values_regions_da) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3)) +
  xlab('Pairwise Region') +
  ylab('Pairwise R')

plt_line + plt_pairwise[[3]] +
  plot_layout(ncol = 2, widths = unit(2, 'cm'), heights = unit(2, 'cm'))

cor_pairwise %>% write_csv(str_c(dir_output_e, fn_stem, '_data.csv'))
save_pdf(dir_output_e, str_c(fn_stem, '.pdf'), 6, 4)
```




---

## fig7f: pairwise ECDF + fiber distance vs pairwise R (sustained)
```{r eval=FALSE}
dir_output_f <- str_c(dir_output, 'f/')
dir.create(dir_output_f, recursive = TRUE, showWarnings = FALSE)

# build pairwise correlation data from peth windows (sustained)
plt_data_windows <- read.csv(str_c(dir_output_pre, 'str_peth_corr_windows.csv')) %>%
  mutate(
    set_id       = set_id       %>% factor(levels = c('FR:Suc', 'WR:Suc', 'WR:NaCl')),
    time_rel_bin = time_rel_bin %>% factor(levels = c('Pre', 'Sustained', 'Post')),
    var_x        = var_x        %>% factor(levels = key_regions$region_label %>% unique()),
    var_y        = var_y        %>% factor(levels = key_regions$region_label %>% unique())
  ) %>%
  filter(var_x != var_y, time_rel_bin == 'Sustained', set_id == 'WR:NaCl')

regions <- unique(plt_data_windows$var_x)

for (region in regions) {
  loop_df <- plt_data_windows %>%
    filter(var_x == region | var_y == region) %>%
    mutate(pairwise_region01 = region) %>%
    mutate(pairwise_region02 = case_when(
      var_x == region ~ var_y,
      var_y == region ~ var_x
    )) %>%
    select(-var_x, -var_y)

  if (region == regions[1]) {
    cor_pairwise <- loop_df
  } else {
    cor_pairwise <- bind_rows(cor_pairwise, loop_df)
  }
}

cor_pairwise <- cor_pairwise %>%
  group_by(subject, pairwise_region01, pairwise_region02) %>%
  summarise(r = mean(r), .groups = 'drop') %>%
  mutate(pairwise_region01 = pairwise_region01 %>% factor(levels = key_regions$region_label %>% unique()))
```

```{r eval=FALSE}
# pairwise ECDF
fn_stem <- 'cor_peth_pairwise_ecdf'

cor_pairwise %>%
  ggplot(aes(r, color = pairwise_region01)) +
  geom_vline(xintercept = 0, color = 'darkgrey', size = 1/3) +
  stat_ecdf() +
  theme_ag01(6) +
  force_panelsizes(rows = unit(2, 'cm'), cols = unit(0.5992, 'cm')) +
  coord_cartesian(xlim = c(-1, 1), ylim = c(0, 1), expand = F, clip = 'off') +
  scale_color_manual(values = color_values_regions_da) +
  theme(panel.spacing = unit(1.5, "lines")) +
  theme(strip.text = element_text(margin = margin(b = 5))) +
  xlab('Pairwise R') +
  ylab('Proportion')

cor_pairwise %>% write_csv(str_c(dir_output_f, fn_stem, '_data.csv'))
save_pdf(dir_output_f, str_c(fn_stem, '.pdf'), 6, 4)
```

```{r eval=FALSE}
# fiber pair distance vs pairwise R
fn_stem <- 'cor_peth_pairwise_cor_vs_euclidian'

df_distances <- read.csv(str_c(dir_output_pre, 'placement_distances.csv'))

plt_data_summary <- plt_data_windows %>%
  filter(var_x != var_y, time_rel_bin == 'Sustained', set_id == 'WR:NaCl') %>%
  group_by(subject, var_x, var_y) %>%
  summarise(r = mean(r), .groups = 'drop') %>%
  mutate(var_x = var_x %>% as.character(),
         var_y = var_y %>% as.character()) %>%
  left_join(df_distances %>% rename(var_x = region1, var_y = region2),
            by = join_by(var_x, var_y, subject)) %>%
  filter(r != 1) %>%
  filter_matrix_unique_combinations()

plt_data_summary %>%
  ggplot(aes(distance, r)) +
  geom_hline(yintercept = 0, color = 'darkgrey', size = 0.5) +
  geom_point(shape = 21, size = .5, color = 'white', fill = 'black', stroke = 1/4) +
  geom_smooth(method = 'lm', size = 0.3, alpha = 1/5, color = 'red', fill = 'red') +
  theme_ag01(6) +
  coord_cartesian(ylim = c(-1, 1), xlim = c(0, 5), expand = F, clip = 'off') +
  stat_cor(method = 'pearson', size = 2, label.y = 1) +
  xlab('Euclidean distance (mm)') +
  ylab('R') +
  force_panelsizes(rows = unit(2, 'cm'), cols = unit(1.0526, 'cm'))

save_pdf(dir_output_f, str_c(fn_stem, '.pdf'), 6, 6)
plt_data_summary %>% write_csv(str_c(dir_output_f, fn_stem, '_data.csv'))

tidy_cor(plt_data_summary, 'distance', 'r') %>%
  write_csv(str_c(dir_output_f, fn_stem, '_stats_cor.csv'))
```

---

# LHA/STR correlation [fig7 G-I]
## preprocessing
```{r eval=FALSE}
toggle_process <- 0

filter_corrdata <- function(df) {
  df %>%
    filter(var_x %>% str_detect('LHA')) %>%
    filter(!var_y %>% str_detect('LHA')) %>%
    filter(set_id == 'WR:NaCl') %>%
    mutate(set_id = set_id %>% factor(levels = c('FR:Suc', 'WR:Suc', 'WR:NaCl'))) %>%
    mutate(var_x = var_x %>% factor(levels = c('LHA:Glut', 'LHA:GABA', 'LHA:Ratio')))
}
```

```{r eval=FALSE}
if (toggle_process == 1) {

  # ── 5. LHA/STR baseline correlation ──────────────────────────────────────────
  fns_streams_bl_corr <- list.files(dir_sessions_combined_subject,
                                    pattern = 'streams_baseline_corr.csv',
                                    recursive = T, full.names = T)
  fns_streams_bl_corr <- fns_streams_bl_corr[fns_streams_bl_corr %>% str_detect('lhastr')]

  bind_rows(lapply(fns_streams_bl_corr, read.csv)) %>%
    filter(set_id %in% c('wrnacl', 'wrsuc', 'frsuc')) %>%
    format_set_id(key_set_id) %>%
    mutate(
      var_x = var_x %>% factor(levels = key_regions$region_label %>% unique()),
      var_y = var_y %>% factor(levels = key_regions$region_label %>% unique())
    ) %>%
    filter_corrdata() %>%
    write_csv(str_c(dir_output_pre, 'lhastr_baseline_corr.csv'))

  # ── 6. LHA/STR peth corr timerel ─────────────────────────────────────────────
  fns_streams_peth_corr_timerel <- list.files(dir_sessions_combined_subject,
                                              pattern = 'streams_peth_corr_timerel.csv',
                                              recursive = T, full.names = T)
  fns_streams_peth_corr_timerel <- fns_streams_peth_corr_timerel[fns_streams_peth_corr_timerel %>% str_detect('lhastr')]

  bind_rows(lapply(fns_streams_peth_corr_timerel, read.csv)) %>%
    filter(set_id %in% c('wrnacl', 'wrsuc', 'frsuc')) %>%
    format_set_id(key_set_id) %>%
    mutate(
      var_x = var_x %>% factor(levels = key_regions$region_label %>% unique()),
      var_y = var_y %>% factor(levels = key_regions$region_label %>% unique())
    ) %>%
    filter_corrdata() %>%
    write_csv(str_c(dir_output_pre, 'lhastr_peth_corr_timerel.csv'))

  # ── 7. LHA/STR peth corr windows ─────────────────────────────────────────────
  fns_streams_peth_corr_windows <- list.files(dir_sessions_combined_subject,
                                              pattern = 'streams_peth_corr_windows.csv',
                                              recursive = T, full.names = T)
  fns_streams_peth_corr_windows <- fns_streams_peth_corr_windows[fns_streams_peth_corr_windows %>% str_detect('lhastr')]

  bind_rows(lapply(fns_streams_peth_corr_windows, read.csv)) %>%
    filter(set_id %in% c('wrnacl', 'wrsuc', 'frsuc')) %>%
    format_set_id(key_set_id) %>%
    mutate(
      var_x = var_x %>% factor(levels = key_regions$region_label %>% unique()),
      var_y = var_y %>% factor(levels = key_regions$region_label %>% unique())
    ) %>%
    filter_corrdata() %>%
    write_csv(str_c(dir_output_pre, 'lhastr_peth_corr_windows.csv'))

} else {
  message('toggle_process = 0: LHA/STR preprocessing CSVs will be read by each section')
}
```

---

## fig7h: lha/str baseline correlation (heat map + bar summary, WR:NaCl)
```{r eval=FALSE}
dir_output_h <- str_c(dir_output, 'h/')
dir.create(dir_output_h, recursive = TRUE, showWarnings = FALSE)
```

### fig7h top: heat map
```{r eval=FALSE}
fn_stem <- 'cor_baseline_setid'

streams_bl_corr <- read.csv(str_c(dir_output_pre, 'lhastr_baseline_corr.csv')) %>%
  filter(var_x != 'LHA:Ratio') %>%
  mutate(
    set_id = set_id %>% factor(levels = c('FR:Suc', 'WR:Suc', 'WR:NaCl')),
    var_x  = var_x  %>% factor(levels = c('LHA:Glut', 'LHA:GABA')),
    var_y  = var_y  %>% factor(levels = key_regions$region_label %>% unique())
  )

plt_data_summary <- streams_bl_corr %>%
  group_by(set_id, var_x, var_y) %>%
  summarise(r = mean(r), .groups = 'drop')

plt_data_summary %>%
  ggplot(aes(var_y, var_x, fill = r)) +
  geom_tile() +
  theme_ag01(6) +
  theme(
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    axis.text.x  = element_text(angle = 90, hjust = 1, vjust = 0.3)
  ) +
  facet_grid(. ~ set_id) +
  ggtitle('Baseline correlation /n') +
  coord_cartesian(xlim = c(0.5, 4.5), ylim = c(0.5, 2.5), expand = F) +
  scale_fill_viridis_c(limits = c(-0.25, 0.25), oob = scales::squish, option = 'cividis') +
  force_panelsizes(rows = unit(2 * 1/3, 'cm'), cols = unit(4 * 1/3, 'cm'))

save_pdf(dir_output_h, str_c(fn_stem, '_heat.pdf'), 6, 4)
plt_data_summary %>% write_csv(str_c(dir_output_h, fn_stem, '_heat_data.csv'))
```

### fig7h bottom: bar summary
```{r eval=FALSE}
fn_stem <- 'cor_baseline_wrnacl_lha_vs_r_facet_str_bar'

streams_bl_corr <- read.csv(str_c(dir_output_pre, 'lhastr_baseline_corr.csv')) %>%
  mutate(
    set_id = set_id %>% factor(levels = c('FR:Suc', 'WR:Suc', 'WR:NaCl')),
    var_x  = var_x  %>% factor(levels = c('LHA:Glut', 'LHA:GABA', 'LHA:Ratio')),
    var_y  = var_y  %>% factor(levels = key_regions$region_label %>% unique())
  )

stats_data <- streams_bl_corr %>%
  filter(var_x %in% c('LHA:GABA', 'LHA:Glut'))

stats_results <- stats_data %>%
  select(subject, var_x, var_y, r) %>%
  spread(var_x, r) %>%
  clean_names() %>%
  tidy_ttest_unpaired(NA, NA, 'lha_glut', 'lha_gaba', 'var_y') %>%
  quick_sig()

stats_data %>%
  ggplot(aes(var_x, r, group = 1, color = var_x, fill = var_x)) +
  geom_hline(yintercept = 0, linewidth = 1/2) +
  geom_jitter(aes(group = subject), alpha = 1/3, size = 1, width = 0.2) +
  stat_summary(fun = 'mean', geom = 'bar', alpha = 1/3, color = NA, width = 0.6) +
  stat_summary(fun.data = 'mean_se', geom = 'errorbar', width = 0) +
  theme_ag01(6) +
  scale_color_manual(values = color_values_regions[c(2, 1)]) +
  scale_fill_manual(values  = color_values_regions[c(2, 1)]) +
  facet_grid(. ~ var_y) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3)) +
  coord_cartesian(xlim = c(0.5, 2.5), ylim = c(-0.6, 0.6), expand = F, clip = 'off') +
  scale_y_continuous(breaks = seq(-0.6, 0.6, 0.3)) +
  xlab('') +
  ylab('Mean R') +
  force_panelsizes(rows = unit(2, 'cm'), cols = unit(0.5, 'cm'))

save_pdf(dir_output_h, str_c(fn_stem, '_summary.pdf'), 6, 4)
stats_results %>% write_csv(str_c(dir_output_h, fn_stem, '_summary_stats_ttest.csv'))
stats_data    %>% write_csv(str_c(dir_output_h, fn_stem, '_summary_data.csv'))
```

---

## fig7i: lha/str peth correlation (trace + bar summary, WR:NaCl)
```{r eval=FALSE}
dir_output_i <- str_c(dir_output, 'i/')
dir.create(dir_output_i, recursive = TRUE, showWarnings = FALSE)
```

```{r eval=FALSE}
# fig7i top: peth correlation trace
fn_stem <- 'peth_cor_lha_region'

streams_peth_corr_timerel <- read.csv(str_c(dir_output_pre, 'lhastr_peth_corr_timerel.csv')) %>%
  mutate(
    set_id = set_id %>% factor(levels = c('FR:Suc', 'WR:Suc', 'WR:NaCl')),
    var_x  = var_x  %>% factor(levels = c('LHA:Glut', 'LHA:GABA', 'LHA:Ratio')),
    var_y  = var_y  %>% factor(levels = key_regions$region_label %>% unique())
  )

plt_data <- streams_peth_corr_timerel %>%
  group_by(var_x, subject, set_id, time_rel) %>%
  summarise(r = mean(r), .groups = 'drop')

streams_peth_corr_timerel %>%
  filter(var_x %in% c('LHA:Glut', 'LHA:GABA')) %>%
  ggplot(aes(time_rel, r, color = var_x, fill = var_x, group = var_x)) +
  geom_hline(yintercept = c(-0.4, -0.2, 0.2, 0.4), color = 'darkgrey', size = 1/3) +
  geom_hline(yintercept = c(0), color = 'darkgrey', size = 1/2) +
  annotate("rect", xmin = 0, xmax = 3, ymin = -Inf, ymax = Inf, alpha = 1/3, fill = "darkgrey") +
  stat_summary(fun.data = 'mean_se', geom = 'ribbon', color = NA, alpha = 1/3) +
  stat_summary(fun = 'mean', geom = 'line') +
  scale_color_manual(values = color_values_regions[c(2, 1)]) +
  scale_fill_manual(values  = color_values_regions[c(2, 1)]) +
  theme_ag01(6) +
  facet_grid(set_id ~ var_y) +
  force_panelsizes(rows = unit(2, 'cm'), cols = unit(2, 'cm')) +
  coord_cartesian(xlim = c(-3, 9), ylim = c(-0.4, 0.6), expand = F, clip = 'off') +
  ylab('Mean R') +
  xlab('Time (s)')

save_pdf(dir_output_i, str_c(fn_stem, '_trace.pdf'), 6, 4)
plt_data %>% write_csv(str_c(dir_output_i, fn_stem, '_trace_data.csv'))
```

```{r eval=FALSE}
# fig7i bottom: peth correlation bar summary
fn_stem <- 'cor_peth_summary_facet_bar'

streams_peth_corr_windows <- read.csv(str_c(dir_output_pre, 'lhastr_peth_corr_windows.csv')) %>%
  mutate(
    set_id       = set_id       %>% factor(levels = c('FR:Suc', 'WR:Suc', 'WR:NaCl')),
    time_rel_bin = time_rel_bin %>% factor(levels = c('Pre', 'Sustained', 'Post')),
    var_x        = var_x        %>% factor(levels = c('LHA:Glut', 'LHA:GABA', 'LHA:Ratio')),
    var_y        = var_y        %>% factor(levels = key_regions$region_label %>% unique())
  )

streams_peth_corr_windows %>%
  filter(var_x %in% c('LHA:GABA', 'LHA:Glut')) %>%
  ggplot(aes(var_x, r, group = 1, color = var_x, fill = var_x)) +
  geom_hline(yintercept = 0, linewidth = 1/2) +
  geom_jitter(aes(group = subject), alpha = 1/3, size = 1, width = 0.2) +
  stat_summary(fun = 'mean', geom = 'bar', alpha = 1/3, color = NA, width = 0.6) +
  stat_summary(fun.data = 'mean_se', geom = 'errorbar', width = 0) +
  theme_ag01(6) +
  scale_color_manual(values = color_values_regions[c(2, 1)]) +
  scale_fill_manual(values  = color_values_regions[c(2, 1)]) +
  facet_grid(. ~ interaction(time_rel_bin, var_y)) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3)) +
  coord_cartesian(xlim = c(0.5, 2.5), ylim = c(-0.6, 0.6), expand = F, clip = 'off') +
  scale_y_continuous(breaks = seq(-0.6, 0.6, 0.3)) +
  xlab('') +
  ylab('Mean R') +
  force_panelsizes(rows = unit(2, 'cm'), cols = unit(0.5, 'cm'))

save_pdf(dir_output_i, str_c(fn_stem, '_summary.pdf'), 6, 4)
```

```{r eval=FALSE}
stats_results <- streams_peth_corr_windows %>%
  filter(var_x %in% c('LHA:GABA', 'LHA:Glut')) %>%
  select(subject, time_rel_bin, var_x, var_y, r) %>%
  spread(var_x, r) %>%
  clean_names() %>%
  tidy_ttest_unpaired(NA, NA, 'lha_glut', 'lha_gaba', 'var_y', 'time_rel_bin') %>%
  quick_sig()

stats_results %>%
  ggplot(aes(var_y, time_rel_bin, label = sig_symbol)) +
  geom_text()

stats_results            %>% write_csv(str_c(dir_output_i, fn_stem, '_stats_ttest.csv'))
streams_peth_corr_windows %>% write_csv(str_c(dir_output_i, fn_stem, '_data.csv'))
```