---
title: "sfig08"
author: "adam gordon-fennell"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = normalizePath('../'))
```

# setup
## libraries
```{r eval=FALSE}
library(tidyverse)
library(afex)
library(emmeans)
library(janitor)
library(readxl)
library(ggh4x)
library(arrow)
library(zoo)
library(lubridate)
library(patchwork)
library(ggbeeswarm)
library(ggpubr)
library(pals)
library(boot)
library(corrplot)
library(Hmisc)
library(corrr)
library(ggcorrplot)
library(FactoMineR)
library(factoextra)

arrow::set_cpu_count(4)

source('./functions/params.R')
source('./functions/theme.R')
source('./functions/general.R')
source('./functions/r_general.R')
source('./functions/r_plots.R')
source('./functions/stats.R')
source('./functions/pca.R')
source('./functions/analysis_peth.R')
source('./functions/plotting_placements.R')
```

## directories
```{r eval=FALSE}
dir_localdata_sessions        <- './data/sessions/'
dir_sessions_combined_subject <- './data/sessions_combined_subject/'
dir_output                    <- './analysis_and_plots/sfig08/'
dir_fig07_pre                 <- './analysis_and_plots/fig07/pre/'

dir.create(dir_output, recursive = TRUE, showWarnings = FALSE)
```

## logs / keys
```{r eval=FALSE}
log_analysis_subjects <- read_xlsx('./logs_and_keys/log_data_analysis.xlsx', sheet = 'subjects',    na = c('NA', ''))
log_analysis_fp       <- read_xlsx('./logs_and_keys/log_data_analysis.xlsx', sheet = 'fp',          na = c('NA', ''))
log_analysis_exp      <- read_xlsx('./logs_and_keys/log_data_analysis.xlsx', sheet = 'experiments', na = c('NA', ''))
```

## local functions
```{r eval=FALSE}
# plt_line_pairwise: NOT in repo functions (repo has plt_bar_pairwise which uses aov_rm_one_between)
# this version uses aov_rm_one_within for within-subject stats per region
plt_line_pairwise <- function(df, dir_output, fn_stem, var_id = 'subject', var_dv, var_within, ylims, heat_range = NA) {

  n_within <- df %>%
    pull(!!as.name(var_within)) %>%
    unique() %>%
    length()

  pltline <- df %>%
    ggplot(aes(region, !!as.name(var_dv))) +
    geom_line(aes(group = !!as.name(var_id)), alpha = 1/4) +
    stat_summary(fun = 'mean', geom = 'line', aes(group = 1)) +
    stat_summary(fun.data = 'mean_se', geom = 'errorbar', aes(group = 1), width = 0) +
    theme_ag01(6) +
    theme(axis.title.x = element_blank(),
          axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3)) +
    coord_cartesian(xlim = c(0.5, n_within + 0.5), ylim = ylims, expand = F)

  stats_results <- df %>%
    aov_rm_one_within(dir_output, fn_stem, var_id, var_dv, var_within)

  df_pairs <- stats_results[[3]] %>%
    format_regions('contrast1_within', key_regions) %>%
    format_regions('contrast2_within', key_regions)

  plt_comparisions <- plt_hsd_matrix_2contrasts(df_pairs, heat_range)

  return(list(stats_results, pltline, plt_comparisions))
}
```

---

# STR correlation [sfig08]
## data setup
```{r eval=FALSE}
# data generated by fig07.Rmd toggle_process = 1 — no reprocessing needed here
streams_bl_corr <- read.csv(str_c(dir_fig07_pre, 'str_baseline_corr.csv')) %>%
  mutate(
    set_id = set_id %>% factor(levels = c('FR:Suc', 'WR:Suc', 'WR:NaCl')),
    var_x  = var_x  %>% factor(levels = key_regions$region_label %>% unique()),
    var_y  = var_y  %>% factor(levels = key_regions$region_label %>% unique())
  )

df_distances <- read.csv(str_c(dir_fig07_pre, 'placement_distances.csv'))

# build pairwise correlation — shared by sfig8d and sfig8c
regions <- unique(streams_bl_corr$var_x)

for (region in regions) {
  loop_df <- streams_bl_corr %>%
    filter(var_x != var_y) %>%
    filter(var_x == region | var_y == region) %>%
    mutate(pairwise_region01 = region) %>%
    mutate(pairwise_region02 = case_when(
      var_x == region ~ var_y,
      var_y == region ~ var_x
    )) %>%
    select(-var_x, -var_y)

  if (region == regions[1]) {
    cor_pairwise <- loop_df
  } else {
    cor_pairwise <- bind_rows(cor_pairwise, loop_df)
  }
}

cor_pairwise <- cor_pairwise %>%
  filter(set_id == 'WR:NaCl') %>%
  group_by(subject, pairwise_region01, pairwise_region02) %>%
  summarise(r = mean(r), .groups = 'drop') %>%
  mutate(pairwise_region01 = pairwise_region01 %>% factor(levels = key_regions$region_label %>% unique()))
```

---

## sfig8a: baseline correlation heat
```{r eval=FALSE}
dir_output_a <- str_c(dir_output, 'a/')
dir.create(dir_output_a, recursive = TRUE, showWarnings = FALSE)

fn_stem <- 'cor_baseline_setid'

plt_data_summary <- streams_bl_corr %>%
  group_by(set_id, var_x, var_y) %>%
  summarise(r = mean(r), .groups = 'drop') %>%
  filter(set_id == 'WR:NaCl')

plt_corrmatrix(plt_data_summary) +
  facet_grid(.~set_id) +
  ggtitle('Baseline correlation \n') +
  coord_cartesian(xlim = c(0.5, 6.5), ylim = c(0.5, 6.5), expand = F) +
  force_panelsizes(rows = unit(2, 'cm'), cols = unit(2, 'cm'))

save_pdf(dir_output_a, str_c(fn_stem, '_heat.pdf'), 6, 4)
plt_data_summary %>% write_csv(str_c(dir_output_a, fn_stem, '_heat_data.csv'))
```

---

## sfig8b: baseline correlation summary
```{r eval=FALSE}
dir_output_b <- str_c(dir_output, 'b/')
dir.create(dir_output_b, recursive = TRUE, showWarnings = FALSE)

fn_stem <- 'cor_baseline_setid'

plt_data_subject <- streams_bl_corr %>%
  filter(var_x != var_y) %>%
  group_by(set_id, subject, var_x, var_y) %>%
  summarise(r = mean(r), .groups = 'drop') %>%
  group_by(set_id, subject) %>%
  summarise(r = mean(r), .groups = 'drop')

plt_data_subject %>%
  ggplot(aes(set_id, r, group = 1)) +
  geom_line(aes(group = subject), alpha = 1/3, size = 1/3) +
  stat_summary(fun = 'mean', geom = 'line') +
  stat_summary(fun.data = 'mean_se', geom = 'errorbar', width = 0) +
  theme_ag01(6) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3)) +
  coord_cartesian(xlim = c(0.5, 3.5), ylim = c(0, 0.8), expand = F) +
  xlab('') +
  ylab('Mean R') +
  force_panelsizes(rows = unit(2, 'cm'), cols = unit(1, 'cm'))

save_pdf(dir_output_b, str_c(fn_stem, '_summary.pdf'), 6, 4)
plt_data_subject %>% write_csv(str_c(dir_output_b, fn_stem, '_summary_data.csv'))

plt_data_subject %>%
  aov_rm_one_within(dir_output_b, str_c(fn_stem, '_summary'), 'subject', 'r', 'set_id')
```

---

## sfig8c: baseline mean pairwise across regions
```{r eval=FALSE}
dir_output_c <- str_c(dir_output, 'c/')
dir.create(dir_output_c, recursive = TRUE, showWarnings = FALSE)

fn_stem <- 'cor_baseline_setid_pairwise_cor'

plt_data_summary <- cor_pairwise %>%
  group_by(subject, pairwise_region01) %>%
  summarise(r = mean(r), .groups = 'drop')

plt_line <- plt_data_summary %>%
  ggplot(aes(pairwise_region01, r, group = 1)) +
  geom_hline(yintercept = 0, color = 'darkgrey', size = 1/3) +
  geom_line(aes(group = subject), size = 1/2, alpha = 1/3) +
  stat_summary(fun = 'mean', geom = 'line') +
  stat_summary(fun.data = 'mean_se', geom = 'errorbar', width = 0) +
  theme_ag01(6) +
  force_panelsizes(rows = unit(3, 'cm'), cols = unit(3, 'cm')) +
  coord_cartesian(xlim = c(0, 7), ylim = c(-.25, 1), expand = F, clip = 'off') +
  scale_color_manual(values = color_values_regions_da) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3)) +
  xlab('Pairwise Region') +
  ylab('Pairwise R')

key_regions_crosswise <- key_regions %>%
  filter(region != 'nacsh_lat')

plt_pairwise <- plt_line_pairwise(
  df         = plt_data_summary %>% left_join(key_regions_crosswise %>% rename(pairwise_region01 = region_label)),
  dir_output = dir_output_c,
  fn_stem    = fn_stem,
  var_dv     = 'r',
  var_within = 'region',
  ylims      = c(-1, 1)
)

plt_line + plt_pairwise[[3]] +
  plot_layout(ncol = 2, widths = unit(2, 'cm'), heights = unit(2, 'cm'))

cor_pairwise %>% write_csv(str_c(dir_output_c, fn_stem, '_data.csv'))
save_pdf(dir_output_c, str_c(fn_stem, '.pdf'), 6, 4)
```

---

## sfig8d: baseline pairwise ECDF (left) + fiber distance vs pairwise R (right)
```{r eval=FALSE}
dir_output_d <- str_c(dir_output, 'd/')
dir.create(dir_output_d, recursive = TRUE, showWarnings = FALSE)
```

### sfig8d left: baseline pairwise ECDF
```{r eval=FALSE}
fn_stem <- 'cor_baseline_setid_pairwise_ecdf'

cor_pairwise %>%
  ggplot(aes(r, color = pairwise_region01)) +
  geom_vline(xintercept = 0, color = 'darkgrey', size = 1/3) +
  stat_ecdf() +
  theme_ag01(6) +
  force_panelsizes(rows = unit(2, 'cm'), cols = unit(1, 'cm')) +
  coord_cartesian(xlim = c(-1, 1), ylim = c(0, 1), expand = F, clip = 'off') +
  scale_color_manual(values = color_values_regions_da) +
  theme(panel.spacing = unit(1.5, "lines")) +
  theme(strip.text = element_text(margin = margin(b = 5))) +
  xlab('Pairwise R') +
  ylab('Proportion')

cor_pairwise %>% write_csv(str_c(dir_output_d, fn_stem, '_data.csv'))
save_pdf(dir_output_d, str_c(fn_stem, '.pdf'), 6, 4)
```

### sfig8d right: fiber distance vs pairwise R
```{r eval=FALSE}
fn_stem <- 'cor_baseline_setid_pairwise_cor_vs_euclidian'

plt_data <- streams_bl_corr %>%
  filter(var_x != var_y, set_id == 'WR:NaCl') %>%
  group_by(subject, var_x, var_y) %>%
  summarise(r = mean(r), .groups = 'drop')

plt_data_summary <- plt_data %>%
  mutate(var_x = var_x %>% as.character(),
         var_y = var_y %>% as.character()) %>%
  left_join(df_distances %>% rename(var_x = region1, var_y = region2),
            by = join_by(var_x, var_y, subject)) %>%
  filter_matrix_unique_combinations()

plt_data_summary %>%
  ggplot(aes(distance, r)) +
  geom_hline(yintercept = 0, color = 'darkgrey', size = 0.5) +
  geom_point(shape = 21, size = 1, color = 'white', fill = 'black', stroke = 1/8) +
  geom_smooth(method = 'lm', size = 0.3, alpha = 1/5, color = 'red', fill = 'red') +
  theme_ag01(6) +
  coord_cartesian(ylim = c(-1, 1), xlim = c(0, 5), expand = F, clip = 'off') +
  stat_cor(method = 'pearson', size = 2, label.y = 1) +
  xlab('Euclidean distance (mm)') +
  ylab('R') +
  force_panelsizes(rows = unit(2, 'cm'), cols = unit(2, 'cm'))

plt_data_summary %>% write_csv(str_c(dir_output_d, fn_stem, '_data.csv'))
save_pdf(dir_output_d, str_c(fn_stem, '.pdf'), 6, 6)

tidy_cor(plt_data_summary, 'distance', 'r') %>%
  write_csv(str_c(dir_output_d, fn_stem, '_stats_cor.csv'))
```

---

# PCA [sfig08]
## preprocessing
```{r eval=FALSE}
toggle_process <- 0  # 1 = run PCA pipeline and save  |  0 = read saved CSVs

dir_output_pre <- str_c(dir_output, 'pre/')
dir.create(dir_output_pre, recursive = TRUE, showWarnings = FALSE)
```

```{r eval=FALSE}
compute_pairwise_distances2d <- function(com_pc1, com_pc2) {
  compute_distance <- function(x1, y1, x2, y2) sqrt((x2 - x1)^2 + (y2 - y1)^2)
  tibble(
    distance_wrsuc_frsuc  = compute_distance(com_pc1$wrsuc,  com_pc2$wrsuc,  com_pc1$frsuc,  com_pc2$frsuc),
    distance_wrsuc_wrnacl = compute_distance(com_pc1$wrsuc,  com_pc2$wrsuc,  com_pc1$wrnacl, com_pc2$wrnacl),
    distance_frsuc_wrnacl = compute_distance(com_pc1$frsuc,  com_pc2$frsuc,  com_pc1$wrnacl, com_pc2$wrnacl)
  )
}

format_pair_id <- function(df) {
  df %>%
    mutate(pair = pair %>% str_remove('distance_')) %>%
    mutate(pair = pair %>% factor(levels = c('wrsuc_frsuc', 'wrsuc_wrnacl', 'frsuc_wrnacl')))
}


if (toggle_process == 1) {

  # ── 1. subjects: inclusion_6site == 1 ────────────────────────────────────────
  subjects_pca_da <- log_analysis_subjects %>%
    filter(inclusion_6site == 1) %>%
    pull(subject)

  # ── 2. blocknames: last 4 sessions per subject × set_id ──────────────────────
  process_blocknames <- log_analysis_fp %>%
    filter(subject %in% subjects_pca_da) %>%
    filter(is.na(exclude)) %>%
    filter(last04 == 1) %>%
    get_set_id() %>%
    filter(set_id %in% c('wrnacl', 'wrsuc', 'frsuc')) %>%
    pull(blockname)

  # ── 3. import peth ────────────────────────────────────────────────────────────
  df_fp_peth <- combine_session_fp(process_blocknames, dir_localdata_sessions)
  df_temp    <- df_fp_peth %>% filter(time_rel > -3, time_rel < 11)

  # ── 4. build df_pca: filter subjects, set_id, select key columns ─────────────
  cat_vars <- c('set_id', 'subject', 'blockname', 'trial_num', 'solution',
                'lick_count', 'time', 'time_rel')

  df_pca <- df_temp %>%
    left_join(log_analysis_fp %>% select(blockname, subject)) %>%
    filter(subject %in% subjects_pca_da) %>%
    left_join(log_analysis_fp %>% select(blockname, procedure, deprivation), by = join_by(blockname)) %>%
    get_set_id() %>%
    select(all_of(cat_vars), region, zscore_blsub)

  # ── 5. remove sessions with poor signal quality ───────────────────────────────
  fns_qc_metrics      <- list.files(dir_localdata_sessions, pattern = 'quality_metrics.csv', recursive = T, full.names = T)
  combined_qc_metrics <- bind_rows(lapply(fns_qc_metrics, read.csv))

  blocknames_to_remove <- df_pca %>%
    filter(time_rel == 0) %>%
    select(subject, blockname, region) %>%
    unique() %>%
    left_join(combined_qc_metrics %>% select(blockname, region, exclude_poor_signal),
              by = c('blockname', 'region')) %>%
    filter(exclude_poor_signal != 0) %>%
    pull(blockname)

  df_pca <- df_pca %>%
    filter(!blockname %in% blocknames_to_remove)

  # ── 6. wide format, filter lick trials ───────────────────────────────────────
  df_pca_wide <- df_pca %>%
    spread(region, zscore_blsub) %>%
    filter(lick_count > 0)

  sig_vars <- colnames(df_pca_wide)
  sig_vars <- sig_vars[!sig_vars %in% cat_vars]

  # ── 6b. data summary (n samples, trials, subjects, sessions) ─────────────────
  print(str_c('samples: ', nrow(df_pca_wide)))

  df_pca_wide %>%
    filter(time_rel == 0) %>%
    select(subject) %>%
    unique() %>%
    nrow() %>%
    { print(str_c('subjects: ', .)) }

  df_pca_wide %>%
    filter(time_rel == 0) %>%
    group_by(subject) %>%
    summarise(trial_count = n(), .groups = 'drop') %>%
    summarise(
      mean_trial_count = mean(trial_count),
      min_trial_count  = min(trial_count),
      max_trial_count  = max(trial_count),
      sd_trial_count   = sd(trial_count)
    ) %>%
    print()

  df_pca_wide %>%
    filter(time_rel == 0) %>%
    select(subject, blockname) %>%
    unique() %>%
    group_by(subject) %>%
    summarise(session_count = n(), .groups = 'drop') %>%
    summarise(
      mean_session_count = mean(session_count),
      min_session_count  = min(session_count),
      max_session_count  = max(session_count),
      sd_session_count   = sd(session_count)
    ) %>%
    print()

  # ── 7. run PCA ───────────────────────────────────────────────────────────────
  df_pca_wide_numeric <- df_pca_wide %>%
    select(-all_of(cat_vars))

  pca_results <- princomp(df_pca_wide_numeric)
  pca_summary <- pca_results %>% tidy_pca_summary()

  pca_summary %>%
    write_csv(str_c(dir_output_pre, 'pca_summary.csv'))

  # ── 8. extract loadings ───────────────────────────────────────────────────────
  loadings_matrix <- loadings(pca_results)[,]

  loadings_df <- as.data.frame(loadings_matrix) %>%
    rownames_to_column(var = 'region') %>%
    clean_names() %>%
    gather(pc, loading, starts_with('comp')) %>%
    mutate(pc = pc %>% str_replace('comp_', 'pc')) %>%
    format_regions('region', key_regions)

  loadings(pca_results)[,] %>%
    write.table(str_c(dir_output_pre, 'pca_loadings_full.csv'), sep = ',')

  loadings_df %>%
    write_csv(str_c(dir_output_pre, 'pca_loadings_data.csv'))

  # ── 9. extract scores and compute group-mean trajectory ──────────────────────
  df_pca_scores <- pca_results$scores %>%
    as_tibble()

  colnames(df_pca_scores) <- colnames(df_pca_scores) %>% str_replace('Comp.', 'pc')

  df_pca_scores <- df_pca_scores %>%
    bind_cols(df_pca_wide, .)

  df_pca_scores_summary <- df_pca_scores %>%
    group_by(set_id, time_rel, solution) %>%
    summarise(across(all_of(c('pc1', 'pc2', 'pc3', sig_vars)), mean), .groups = 'drop') %>%
    rowwise() %>%
    mutate(da_mean = mean(c_across(all_of(sig_vars)))) %>%
    ungroup() %>%
    mutate(set_id = factor(set_id, levels = c('wrsuc', 'frsuc', 'wrnacl')))

  df_pca_scores_summary <- df_pca_scores_summary %>%
    select(set_id, solution, time_rel, starts_with('pc')) %>%
    arrange(set_id, solution, time_rel) %>%
    group_by(set_id, solution) %>%
    set_pc_origin3d() %>%
    left_join(df_pca_scores_summary, .)

  df_pca_scores_summary %>%
    write_csv(str_c(dir_output_pre, 'pca_scores_summary.csv'))

  # ── 10. lick count bin summary (sfig8f) ──────────────────────────────────────
  df_pca_lickbin <- df_pca_scores %>%
    filter(time_rel >= 0, time_rel <= 3, lick_count <= 20) %>%
    mutate(lick_count_bin = cut(lick_count, seq(0, 20, 2))) %>%
    filter(!is.na(lick_count_bin))

  df_pca_lickbin_summary <- df_pca_lickbin %>%
    group_by(set_id, time_rel, lick_count_bin) %>%
    summarise(across(all_of(c('pc1', 'pc2', 'pc3', sig_vars)), mean), .groups = 'drop') %>%
    rowwise() %>%
    mutate(da_mean = mean(c_across(all_of(sig_vars)))) %>%
    ungroup() %>%
    mutate(set_id = factor(set_id, levels = c('wrsuc', 'frsuc', 'wrnacl')))

  df_pca_lickbin_adj <- df_pca_lickbin_summary %>%
    select(set_id, lick_count_bin, time_rel, starts_with('pc')) %>%
    arrange(set_id, lick_count_bin, time_rel) %>%
    group_by(set_id, lick_count_bin) %>%
    set_pc_origin3d()

  df_pca_lickbin_summary <- df_pca_lickbin_summary %>%
    left_join(df_pca_lickbin_adj)

  df_pca_lickbin_summary %>%
    write_csv(str_c(dir_output_pre, 'pca_scores_lickbin_summary.csv'))

  # ── 11. lick bin pairwise distances (sfig8i) ─────────────────────────────────
  df_pca_lickbin_persubj <- df_pca_scores %>%
    filter(time_rel >= -3, time_rel <= 6, lick_count <= 20) %>%
    mutate(lick_count_bin = cut(lick_count, seq(0, 20, 2))) %>%
    filter(!is.na(lick_count_bin)) %>%
    group_by(subject, set_id, time_rel, lick_count_bin) %>%
    summarise(across(all_of(c('pc1', 'pc2', 'pc3', sig_vars)), mean), .groups = 'drop') %>%
    rowwise() %>%
    mutate(da_mean = mean(c_across(all_of(sig_vars)))) %>%
    ungroup() %>%
    mutate(set_id = factor(set_id, levels = c('wrsuc', 'frsuc', 'wrnacl')))

  df_pca_lickbin_persubj_adj <- df_pca_lickbin_persubj %>%
    select(subject, set_id, lick_count_bin, time_rel, starts_with('pc')) %>%
    arrange(subject, set_id, lick_count_bin, time_rel) %>%
    group_by(subject, set_id, lick_count_bin) %>%
    set_pc_origin3d()

  df_pca_lickbin_persubj <- df_pca_lickbin_persubj %>%
    left_join(df_pca_lickbin_persubj_adj)

  plt_data_com <- df_pca_lickbin_persubj %>%
    group_by(subject, lick_count_bin, set_id, time_rel) %>%
    summarise(
      pc1_mean = mean(pc1_adj),
      pc2_mean = mean(pc2_adj),
      pc3_mean = mean(pc3_adj),
      .groups = 'drop'
    )

  plt_data_com_pc1 <- plt_data_com %>%
    select(subject, lick_count_bin, time_rel, set_id, pc1_mean) %>%
    spread(set_id, pc1_mean)

  plt_data_com_pc2 <- plt_data_com %>%
    select(subject, lick_count_bin, time_rel, set_id, pc2_mean) %>%
    spread(set_id, pc2_mean)

  distances <- compute_pairwise_distances2d(plt_data_com_pc1, plt_data_com_pc2)

  plt_data_distances <- plt_data_com_pc1 %>%
    select(subject, lick_count_bin, time_rel) %>%
    bind_cols(distances)

  filt_incomplete_subjects <- plt_data_distances %>%
    filter(time_rel == 0) %>%
    gather(pair, distance, starts_with('distance')) %>%
    filter(!is.na(distance)) %>%
    group_by(subject, lick_count_bin) %>%
    summarise(count_comp = n(), .groups = 'drop') %>%
    filter(count_comp != 3)

  plt_data_distances <- plt_data_distances %>%
    filter(!subject %in% filt_incomplete_subjects$subject)

  plt_data_distances %>%
    write_csv(str_c(dir_output_pre, 'pca_lickbin_distances.csv'))

} else {
  message('toggle_process = 0: preprocessing CSVs will be read by each section')
}
```

---

## sfig8e pc1 vs pc2 solution trajectory
```{r eval=FALSE}
# Only PC1 vs PC2 is plotted (other PC pairs intentionally omitted)
dir_output_e <- str_c(dir_output, 'e/')
dir.create(dir_output_e, recursive = TRUE, showWarnings = FALSE)

fn_stem <- 'pc1_vs_pc2_trace'

df_pca_scores_summary <- read.csv(str_c(dir_output_pre, 'pca_scores_summary.csv')) %>%
  mutate(set_id  = set_id  %>% factor(levels = c('wrsuc', 'frsuc', 'wrnacl')),
         solution = solution %>% factor())

join_pca_annotation <- tibble(
  time_rel   = c(0, 3),
  annotation = c('access_start', 'access_end')
) %>%
  mutate(annotation = factor(annotation, levels = c('access_start', 'access_end')))

plt_pca_annotation <- df_pca_scores_summary %>%
  filter(time_rel == 0 | time_rel == 3) %>%
  left_join(join_pca_annotation) %>%
  format_set_id(key_set_id)

plt_data <- df_pca_scores_summary %>%
  filter(time_rel >= 0) %>%
  format_set_id(key_set_id)

plt_data_downsampled <- plt_data %>%
  group_by(set_id, solution) %>%
  filter(row_number() %% 4 == 0)

plt <- plt_data %>%
  ggplot(aes(pc1_adj, pc2_adj, color = solution)) +
  geom_hline(yintercept = 0, size = 1/3, color = 'darkgrey') +
  geom_vline(xintercept = 0, size = 1/3, color = 'darkgrey') +
  geom_path(alpha = 1/3, size = 0.2) +
  geom_point(data = plt_data_downsampled, size = 1/3, stroke = 0) +
  geom_point(data = plt_pca_annotation, aes(pc1_adj, pc2_adj, shape = annotation),
             size = 1, fill = 'white', stroke = 1/2) +
  facet_grid(.~set_id) +
  theme_ag01(6) +
  coord_cartesian(xlim = c(-2.5, 7.5), ylim = c(-2, 4), clip = 'off') +
  scale_color_manual(values = c(color_values_nacl, color_values_suc)) +
  scale_shape_manual(values = c(21, 24)) +
  force_panelsizes(rows = unit(3, 'cm'), cols = unit(3, 'cm'))

plt %>%
  add_scale_bar(
    origin = c(-2, -2),
    x_len  = 1,
    y_len  = 1
  )

save_pdf(dir_output_e, str_c(fn_stem, '_plt.pdf'), 12, 6)
plt_data %>% write_csv(str_c(dir_output_e, fn_stem, '_data.csv'))
```

---

## sfig8f: pc1 vs pc2 lick count trajectory
```{r eval=FALSE}
dir_output_f <- str_c(dir_output, 'f/')
dir.create(dir_output_f, recursive = TRUE, showWarnings = FALSE)

fn_stem <- 'lickbin_pc1_vs_pc2_trace'

df_pca_lickbin_summary <- read.csv(str_c(dir_output_pre, 'pca_scores_lickbin_summary.csv')) %>%
  mutate(set_id        = set_id        %>% factor(levels = c('wrsuc', 'frsuc', 'wrnacl')),
         lick_count_bin = lick_count_bin %>% factor()) %>%
    mutate(lick_count_bin = lick_count_bin %>%
           factor(levels = unique(lick_count_bin)[
             order(as.numeric(sub('^\\(', '', sub(',.*$', '', unique(lick_count_bin)))))
           ]))

join_pca_annotation <- tibble(
  time_rel   = c(0, 3),
  annotation = c('access_start', 'access_end')
) %>%
  mutate(annotation = factor(annotation, levels = c('access_start', 'access_end')))

plt_pca_annotation <- df_pca_lickbin_summary %>%
  filter(time_rel == 0 | time_rel == 3) %>%
  left_join(join_pca_annotation) %>%
  format_set_id(key_set_id)

plt_data <- df_pca_lickbin_summary %>%
  format_set_id(key_set_id)

plt_data_downsampled <- plt_data %>%
  group_by(set_id, lick_count_bin) %>%
  filter(row_number() %% 4 == 0)

plt <- plt_data %>%
  ggplot(aes(pc1_adj, pc2_adj, color = lick_count_bin, group = lick_count_bin)) +
  geom_hline(yintercept = 0, size = 1/3, color = 'darkgrey') +
  geom_vline(xintercept = 0, size = 1/3, color = 'darkgrey') +
  geom_path(alpha = 1/3, size = 0.2) +
  geom_point(data = plt_data_downsampled, size = 1/3, stroke = 0) +
  geom_point(data = plt_pca_annotation, aes(pc1_adj, pc2_adj, shape = annotation),
             size = 1, fill = 'white', stroke = 1/2) +
  facet_grid(.~set_id) +
  theme_ag01(6) +
  scale_color_viridis_d(option = 'rocket', end = 0.9) +
  scale_shape_manual(values = c(21, 24)) +
  force_panelsizes(rows = unit(3, 'cm'), cols = unit(3, 'cm'))

plt %>%
  add_scale_bar(
    origin = c(-2, -2),
    x_len  = 1,
    y_len  = 1
  )

save_pdf(dir_output_f, str_c(fn_stem, '_plt.pdf'), 12, 6)
plt_data %>% write_csv(str_c(dir_output_f, fn_stem, '_data.csv'))


```

---

## sfig8g: scree plot
```{r eval=FALSE}
dir_output_g <- str_c(dir_output, 'g/')
dir.create(dir_output_g, recursive = TRUE, showWarnings = FALSE)

fn_stem <- 'scree'

plt_data <- read.csv(str_c(dir_output_pre, 'pca_summary.csv'))

plt_data %>%
  ggplot(aes(pc, prop_var_cummulative, group = 1)) +
  geom_line() +
  geom_point() +
  ylab('Cummulative variance explained') +
  xlab('Principal component') +
  theme_ag01(6) +
  coord_cartesian(xlim = c(0.5, 6.5), ylim = c(0, 1), expand = F, clip = 'off') +
  force_panelsizes(rows = unit(1, 'cm'), cols = unit(1, 'cm'))

save_pdf(dir_output_g, str_c(fn_stem, '_plt.pdf'), 6, 6)
plt_data %>% write_csv(str_c(dir_output_g, fn_stem, '_data.csv'))
```

---

## sfig8h: pc1 / pc2 loadings
```{r eval=FALSE}
dir_output_h <- str_c(dir_output, 'h/')
dir.create(dir_output_h, recursive = TRUE, showWarnings = FALSE)

fn_stem <- 'pc_vs_loading'

plt_data <- read.csv(str_c(dir_output_pre, 'pca_loadings_data.csv')) %>%
  mutate(region = region %>% factor(levels = key_regions$region_label %>% unique())) %>%
  filter(pc %in% c('pc1', 'pc2'))

plt_data %>%
  ggplot(aes(region, loading, color = pc, group = pc)) +
  geom_hline(yintercept = 0, size = 1/3, color = 'darkgrey') +
  geom_line() +
  geom_point() +
  theme_ag01(6) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3)) +
  coord_cartesian(ylim = c(-1, 1.0), xlim = c(0.5, 6.5), expand = F) +
  scale_color_viridis_d(option = 'cividis', end = 0.6) +
  xlab('') +
  ylab('Loading') +
  force_panelsizes(rows = unit(1, 'cm'), cols = unit(1, 'cm'))

save_pdf(dir_output_h, str_c(fn_stem, '_plt.pdf'), 6, 6)
plt_data %>% write_csv(str_c(dir_output_h, fn_stem, '_data.csv'))
```

---



## sfig8i: time vs pairwise distance (lick count bins)
```{r eval=FALSE}
dir_output_i <- str_c(dir_output, 'i/')
dir.create(dir_output_i, recursive = TRUE, showWarnings = FALSE)

fn_stem <- 'lickbin_pc1_vs_pc2_trace_time_vs_distance'

plt_data <- read.csv(str_c(dir_output_pre, 'pca_lickbin_distances.csv')) %>%
  mutate(lick_count_bin = lick_count_bin %>% factor()) %>%
  gather(pair, distance, starts_with('distance')) %>%
  format_pair_id()

plt_data %>%
  ggplot(aes(time_rel, distance, color = pair, fill = pair, group = pair)) +
  annotate('rect', xmin = 0, xmax = 3, ymin = -Inf, ymax = Inf,
           alpha = 1/3, fill = 'darkgrey') +
  stat_summary(fun.data = 'mean_se', geom = 'ribbon', color = NA, alpha = 1/3) +
  stat_summary(fun = 'mean', geom = 'line') +
  coord_cartesian(ylim = c(0, 4), xlim = c(-3, 6), expand = F) +
  theme_ag01(6) +
  ylab('Euclidean distance') +
  xlab('Time (s)') +
  force_panelsizes(rows = unit(3, 'cm'), cols = unit(2, 'cm'))

save_pdf(dir_output_i, str_c(fn_stem, '_plt.pdf'), 4, 4)
plt_data %>% write_csv(str_c(dir_output_i, fn_stem, '_data.csv'))
```