---
title: "sfig07"
author: "adam gordon-fennell"
date: '2023-12-28'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# run all chunks from the project root so relative paths resolve correctly
knitr::opts_knit$set(root.dir = normalizePath('../'))
```

# setup
## libraries
```{r}
source('./logs_and_keys/key_local_directories.R')
Sys.unsetenv("RETICULATE_PYTHON_FALLBACK")
Sys.unsetenv("RETICULATE_PYTHON")
reticulate::use_python(path_python, required = TRUE)

library(tidyverse)
library(afex)
library(emmeans)
library(janitor)
library(readxl)
library(ggh4x) # force_panelsizes
library(arrow)
library(zoo)
library(lubridate)
library(patchwork)
library(ggbeeswarm)
library(ggpubr) # r2 on correlation
library(pals)
library(boot)  # bootstrapping
library(corrplot)
library(Hmisc)
library(plotly)

arrow::set_cpu_count(4)

source('./functions/params.R')
source('./functions/theme.R')
source('./functions/general.R')
source('./functions/r_general.R')
source('./functions/r_plots.R')
source('./functions/stats.R')
source('./functions/pca.R')
source('./functions/analysis_peth.R')
source('./functions/plotting_placements.R')
```

## directories
```{r}
dir_localdata_sessions <- './data/sessions/'
dir_output             <- './analysis_and_plots/sfig07/'
dir_fig05_pre          <- './analysis_and_plots/fig05/pre/'  # range data already preprocessed in fig05
dir_output_pre <- str_c(dir_output, 'pre/')

dir.create(dir_output, recursive = TRUE, showWarnings = FALSE)
```

## logs / keys
```{r}
log_analysis_subjects <- read_xlsx('./logs_and_keys/log_data_analysis.xlsx', sheet = 'subjects',    na = c('NA', ''))
log_analysis_fp       <- read_xlsx('./logs_and_keys/log_data_analysis.xlsx', sheet = 'fp',          na = c('NA', ''))
log_analysis_exp      <- read_xlsx('./logs_and_keys/log_data_analysis.xlsx', sheet = 'experiments', na = c('NA', ''))
log_placements        <- read.csv('./logs_and_keys/log_fiber_placements.csv', na.strings = c('', 'NA'))
```

---

# analysis / plotting
## setup
```{r}
# helper used by fp str placement sections — filters to striatum (non-LHA) regions
filt_and_format_data <- function(df){
  df %>%
    filter(!region %>% str_detect('LHA')) %>%
    filter(set_id %in% c('frsuc', 'wrsuc', 'wrnacl')) %>%
    mutate(region = region %>% factor(levels = unique(key_regions$region_label))) %>%
    format_set_id(key_set_id)
}
```

---

## preprocessing
# onset analysis: loads raw session data and saves subject-level summaries to pre/
# placement range data is already in fig05/pre/ — no reprocessing needed here
```{r eval=FALSE}
# ── setup ──────────────────────────────────────────────────────────────────────
toggle_process <- 0   # 1 = load from sessions and save  |  0 = read saved CSVs

dir.create(dir_output_pre, recursive = TRUE, showWarnings = FALSE)
```

```{r eval=FALSE}
if (toggle_process == 1) {

  # ── 1. load wrnacl session data ──────────────────────────────────────────────
  subjects_include <- log_analysis_subjects %>%
    filter(inclusion_consumption == 1) %>%
    pull(subject)

  subjects_remove <- log_analysis_subjects %>%
    filter(remove == 1) %>%
    pull(subject)

  process_blocknames <- log_analysis_fp %>%
    filter(is.na(exclude) | exclude != 1) %>%
    filter(subject %in% subjects_include) %>%
    get_set_id() %>%
    filter(set_id == 'wrnacl') %>%
    pull(blockname)

  df_fp_peth <- combine_session_fp(process_blocknames, dir_localdata_sessions) %>%
    left_join(log_analysis_fp %>% select(blockname, subject), by = 'blockname')

  # ── 2. filter subjects / QC / placements ─────────────────────────────────────
  fns_qc_metrics     <- list.files(dir_localdata_sessions, pattern = 'quality_metrics.csv', recursive = TRUE, full.names = TRUE)
  combined_qc_metrics <- bind_rows(lapply(fns_qc_metrics, read.csv))

  df_fp_peth <- df_fp_peth %>%
    filter(!subject %in% subjects_remove) %>%
    filter_qc_metrics(combined_qc_metrics, removal_type = 1) %>%
    format_regions('region', key_regions) %>%
    filter_placements('exclude_da_consumption')

  # ── 3. latency-sorted heat map data (NAcShL) ─────────────────────────────────
  df_heat <- df_fp_peth %>%
    filter(region == 'NAcShL') %>%
    mutate(lick_ts_first = lick_ts_first / 1000) %>%
    select(blockname, subject, region, trial_num, solution, lick_ts_first, time_rel, zscore_blsub)

  df_latency <- df_heat %>%
    filter(time_rel == 0) %>%
    select(blockname, subject, region, trial_num, solution, lick_ts_first) %>%
    group_by(region) %>%
    arrange(region, lick_ts_first) %>%
    mutate(trial_num_sort_lat = row_number()) %>%
    ungroup()

  df_heat <- df_heat %>% left_join(df_latency)

  df_heat %>%
    write_csv(str_c(dir_output_pre, 'fp_onset_heat_data.csv'))

  # ── 4. lick-onset-aligned trace (all regions) ────────────────────────────────
  df_onset <- df_fp_peth %>%
    filter(!is.na(lick_ts_first)) %>%
    mutate(lick_ts_first = round((lick_ts_first / 1000) / 0.05) * 0.05) %>%
    mutate(time_rel_lick = time_rel - lick_ts_first) %>%
    mutate(time_rel_lick = round(time_rel_lick / 0.05) * 0.05)

  df_onset_sbj <- df_onset %>%
    filter(time_rel_lick >= -3, time_rel_lick < 3) %>%
    group_by(subject, region, time_rel_lick) %>%
    summarise(
      zscore_blsub_sem = sd(zscore_blsub) / sqrt(n()),
      zscore_blsub     = mean(zscore_blsub),
      .groups = 'drop'
    ) %>%
    mutate(region = region %>% factor(levels = key_regions$region_label %>% unique()))

  df_onset_sbj %>% write_csv(str_c(dir_output_pre, 'fp_onset_trace_data.csv'))

  # ── 5. bootstrap significance — across subjects ───────────────────────────────
  set.seed(99)
  df_bootstrap_across <- df_onset_sbj %>%
    group_by(time_rel_lick, region) %>%
    do(bootstrap_mean(., 'zscore_blsub')) %>%
    group_by(region) %>%
    get_bootstrap_sig(var_pvalue = 'boot_pvalue', pvalue_treshold = 0.01, consecutive_filt_width = 3) %>%
    ungroup()

  df_bootstrap_across %>% write_csv(str_c(dir_output_pre, 'fp_onset_bootstrap_across_data.csv'))

  # ── 6. bootstrap significance — within subjects ───────────────────────────────
  set.seed(99)
  df_bootstrap_within <- df_onset %>%
    filter(time_rel_lick >= -1, time_rel_lick <= 0.5) %>%
    group_by(time_rel_lick, subject, region) %>%
    do(bootstrap_mean(., 'zscore_blsub')) %>%
    group_by(region, subject) %>%
    get_bootstrap_sig(var_pvalue = 'boot_pvalue', pvalue_treshold = 0.001, consecutive_filt_width = 3) %>%
    ungroup() %>%
    mutate(region = region %>% factor(levels = key_regions$region_label %>% unique()))

  df_bootstrap_within %>% write_csv(str_c(dir_output_pre, 'fp_onset_bootstrap_within_data.csv'))

  # ── 7. onset time summary — earliest significant time per subject × region ────
  df_onset_summary <- df_bootstrap_within %>%
    group_by(subject, region) %>%
    mutate(region = fct_rev(region)) %>%
    filter(sig == 1) %>%
    filter(boot_mean_observed > 0) %>%
    filter(time_rel_lick == min(time_rel_lick)) %>%
    ungroup()

  df_onset_summary %>% write_csv(str_c(dir_output_pre, 'fp_onset_summary_data.csv'))

  # ── 8. access-onset trace (0–0.31 s) ─────────
  df_fp_peth %>%
    filter(!is.na(lick_ts_first)) %>%
    filter(time_rel >= 0, time_rel <= 0.31) %>%
    group_by(subject, region, time_rel) %>%
    summarise(
      zscore_blsub_sem = sd(zscore_blsub) / sqrt(n()),
      zscore_blsub     = mean(zscore_blsub),
      .groups = 'drop'
    ) %>%
    mutate(region = region %>% factor(levels = key_regions$region_label %>% unique())) %>%
    write_csv(str_c(dir_output_pre, 'fp_access_trace_data.csv'))

} else {

  message('toggle_process = 0: preprocessing CSVs will be read by each section as needed')

}
```

---

## sfig07a: fp str placements range (2D anatomical maps)
```{r eval=FALSE}
dir_output_a <- str_c(dir_output, 'a/')
dir.create(dir_output_a, recursive = TRUE, showWarnings = FALSE)

# combine range data across time bins — all read from fig04/pre/
summary_range_combined <- read.csv(str_c(dir_fig05_pre, 'fp_str_range_prelick_data.csv'))   %>% mutate(time_bin = 'prelick')   %>% select(set_id, subject, region, time_bin, range) %>%
  bind_rows(read.csv(str_c(dir_fig05_pre, 'fp_str_range_sustained_data.csv')) %>% mutate(time_bin = 'sustained') %>% select(set_id, subject, region, time_bin, range)) %>%
  bind_rows(read.csv(str_c(dir_fig05_pre, 'fp_str_range_post_data.csv'))      %>% mutate(time_bin = 'post')      %>% select(set_id, subject, region, time_bin, range)) %>%
  mutate(set_id = factor(set_id, levels = key_set_id$set_id_label %>% unique()))
```

```{r eval=FALSE}
source('./functions/plotting_placements.R')

var_color <- 'range'
set.seed(33)

for(loop_set_id in c('WR:NaCl')){
  for(loop_time_bin in c('prelick', 'sustained', 'post')){

    loop_set_label <- loop_set_id %>% str_remove(':')
    fn_stem_a      <- str_c('placement_vs_range_', loop_set_label, '_', loop_time_bin)

    df <- summary_range_combined %>%
      filter(set_id == loop_set_id, time_bin == loop_time_bin) %>%
      join_placements() %>%
      select(set_id, subject, time_bin, region, range, starts_with('hit')) %>%
      mutate(region = region %>% factor(levels = unique(key_regions$region_label))) %>%
      filter(!is.na(range))

    if(loop_time_bin == 'prelick')   color_limits <- c(-0.2, 1)
    if(loop_time_bin == 'sustained') color_limits <- c(-1,   5)
    if(loop_time_bin == 'post')      color_limits <- c(-1,   2)

    for(loop_plane in c('sagittal', 'horizontal', 'coronal')){
      plt_str(df = df, var_color = !!sym(var_color), var_color_name = 'Range',
              vars_facet = c('.', '.'), plt_plane = loop_plane,
              plt_dim_base = 1.5, color_limits = color_limits)
      save_pdf(dir_output_a, str_c(fn_stem_a, '_', loop_plane, '.pdf'), 6, 6)
    }

    tryCatch(
      plt_str_3d(df = df, var_color = var_color, color_limits = color_limits,
                 dir_output = dir_output_a, fn_stem = fn_stem_a, toggle_save = 1),
      error = function(e) message('plt_str_3d skipped (kaleido): ', conditionMessage(e))
    )
  }
}
```

---

## sfig07b: fp str placement-range correlations
```{r eval=FALSE}
dir_output_b <- str_c(dir_output, 'b/')
dir.create(dir_output_b, recursive = TRUE, showWarnings = FALSE)

# summary_range_combined is built in sfig07a — run that setup chunk first
```

```{r eval=FALSE}
modify_plt_corr <- function(plt, loop_time_bin){
  plt <- plt + theme(strip.text = element_blank())
  if(loop_time_bin %in% c('prelick', 'sustained')) plt <- plt %>% remove_x_all()
  return(plt)
}

var_color <- 'range'
set.seed(33)

for(loop_set_id in c('WR:NaCl')){
  for(loop_time_bin in c('prelick', 'sustained', 'post')){

    loop_set_label <- loop_set_id %>% str_remove(':')
    fn_stem_b      <- str_c('placement_vs_range_', loop_set_label, '_', loop_time_bin)

    df <- summary_range_combined %>%
      filter(set_id == loop_set_id, time_bin == loop_time_bin) %>%
      join_placements() %>%
      select(set_id, subject, time_bin, region, range, starts_with('hit')) %>%
      mutate(region = region %>% factor(levels = unique(key_regions$region_label))) %>%
      filter(!is.na(range))

    if(loop_time_bin == 'prelick')   ylim_all <- c(-2,  3)
    if(loop_time_bin == 'sustained') ylim_all <- c(-4, 12)
    if(loop_time_bin == 'post')      ylim_all <- c(-2,  4)

    plt_list <- plt_corr_generic(df = df, ylim_all = ylim_all,
                                 xlim_ap = c(-3, 0, 3), xlim_ml = c(0, 2, 4), xlim_dv = c(-6, -4, -2),
                                 var_dep = var_color, var_dep_label = 'Range', plt_dims = c(2.5, 2.5))

    plt_list[['AP']] %>% modify_plt_corr(loop_time_bin) +
      plt_list[['ML']] %>% modify_plt_corr(loop_time_bin) +
      plt_list[['DV']] %>% modify_plt_corr(loop_time_bin) +
      plot_layout(nrow = 1, widths = unit(1.5, 'cm'), heights = unit(1.5, 'cm'), guides = 'collect')

    save_pdf(dir_output_b, str_c(fn_stem_b, '_corr.pdf'), 12, 6)
    df %>% write_csv(str_c(dir_output_b, fn_stem_b, '_corr_data.csv'))
    plt_list[['stats_output']] %>% write_csv(str_c(dir_output_b, fn_stem_b, '_corr_stats.csv'))
  }
}
```

---

## sfig07c: fp lick onset — heat map (NAcShL, trials sorted by latency)
requires toggle_process = 1 the first time — heat map data is saved to pre/fp_onset_heat_data.csv and read from disk on subsequent knits
```{r eval=FALSE}
dir_output_c <- str_c(dir_output, 'c/')
dir.create(dir_output_c, recursive = TRUE, showWarnings = FALSE)

plt_data_c <- read.csv(str_c(dir_output_pre, 'fp_onset_heat_data.csv'))
df_latency  <- plt_data_c %>%
  filter(time_rel == 0) %>%
  select(subject, region, trial_num_sort_lat, lick_ts_first)
```

```{r eval=FALSE}
# heat map: activity aligned to access onset, trials sorted by lick latency
fn_stem_c1 <- 'fp_heat_naclshl_time_rel_access_vs_trial'


ggplot() +
  geom_tile(data = plt_data_c %>% filter(time_rel >= -0.5, time_rel < 3),
            aes(time_rel, trial_num_sort_lat, fill = zscore_blsub)) +
  geom_point(data = df_latency, aes(lick_ts_first, trial_num_sort_lat), color = 'red', shape = '.') +
  geom_vline(xintercept = c(0, 3), color = 'white', linewidth = 1/4) +
  scale_fill_viridis_c(option = 'magma', limits = c(-5, 10), oob = scales::squish) +
  facet_grid(.~region) +
  theme_ag01(6) +
  coord_cartesian(expand = FALSE) +
  force_panelsizes(rows = unit(2, 'cm'), cols = unit(2, 'cm'))

save_pdf(dir_output_c, str_c(fn_stem_c1, '.pdf'), 6, 6)
```

```{r eval=FALSE}
# heat map: activity aligned to lick onset
fn_stem_c2 <- 'fp_heat_naclshl_time_rel_lick_vs_trial'

plt_data_c2 <- plt_data_c %>%
  filter(!is.na(lick_ts_first)) %>%
  mutate(lick_ts_first_r = round(lick_ts_first / 0.05) * 0.05) %>%
  mutate(time_rel_lick   = round((time_rel - lick_ts_first_r) / 0.05) * 0.05)

ggplot() +
  geom_tile(data = plt_data_c2 %>% filter(time_rel_lick >= -3, time_rel_lick < 0.5),
            aes(time_rel_lick, trial_num_sort_lat, fill = zscore_blsub)) +
  geom_point(data = df_latency, aes(-lick_ts_first, trial_num_sort_lat), color = 'white', shape = '.') +
  geom_vline(xintercept = 0, color = 'red', linewidth = 1/4) +
  scale_fill_viridis_c(option = 'magma', limits = c(-5, 10), oob = scales::squish) +
  theme_ag01(6) +
  coord_cartesian(expand = FALSE) +
  force_panelsizes(rows = unit(2, 'cm'), cols = unit(2, 'cm'))

save_pdf(dir_output_c, str_c(fn_stem_c2, '.pdf'), 6, 6)
```


```{r}

count_trial <- plt_data_c %>% 
  filter(time_rel == 0) %>%
  nrow()

count_subject <- plt_data_c %>% 
  filter(time_rel == 0) %>%
  select(subject) %>%
  unique() %>%
  nrow()

print(str_c('n trial: ', count_trial))
print(str_c('n subject: ', count_subject))
```

---

## sfig07d: fp lick onset — trace aligned to access onset (NAcShL)
```{r eval=FALSE}
dir_output_d <- str_c(dir_output, 'd/')
dir.create(dir_output_d, recursive = TRUE, showWarnings = FALSE)

fn_stem_d <- 'fp_trace_rel_access'

plt_data_d <- read.csv(str_c(dir_output_pre, 'fp_access_trace_data.csv')) %>%
  mutate(region = region %>% factor(levels = key_regions$region_label %>% unique())) %>%
  filter(!region %>% str_detect('LHA'))
```

```{r eval=FALSE}
plt_range <- c(0, 0.31)

plt_data_d %>%
  filter(time_rel >= plt_range[1], time_rel <= plt_range[2]) %>%
  ggplot(aes(x = time_rel, y = zscore_blsub, group = region, color = region, fill = region)) +
  geom_vline(xintercept = 0, size = 1/2, color = 'darkgrey') +
  geom_hline(yintercept = 0, size = 1/2, color = 'darkgrey') +
  stat_summary(fun = 'mean', geom = 'line') +
  stat_summary(fun.data = 'mean_se', geom = 'ribbon', alpha = 1/3, color = NA) +
  theme_ag01(6) +
  coord_cartesian(xlim = plt_range, ylim = c(-0.2, 1), expand = F, clip = 'on') +
  #scale_x_continuous(breaks = seq(-1, 0, 0.5)) +
  xlab('Time relative to access onset (s)') +
  ylab('Z-score') +
  scale_color_manual(values = color_values_regions_da7) +
  scale_fill_manual(values  = color_values_regions_da7) +
  force_panelsizes(rows = unit(2, 'cm'), cols = unit(2, 'cm'))

save_pdf(dir_output_d, str_c(fn_stem_d, '.pdf'), 6, 6)
plt_data_d %>% write_csv(str_c(dir_output_d, fn_stem_d, '_data.csv'))
```

---

## sfig07e: fp lick onset — trace across subjects (with bootstrap significance)
```{r eval=FALSE}
dir_output_e <- str_c(dir_output, 'e/')
dir.create(dir_output_e, recursive = TRUE, showWarnings = FALSE)

fn_stem_e <- 'fp_trace_rel_onset'

plt_data_e           <- read.csv(str_c(dir_output_pre, 'fp_onset_trace_data.csv')) %>%
  mutate(region = region %>% factor(levels = key_regions$region_label %>% unique())) %>%
  filter(!region %>% str_detect('LHA'))

df_bootstrap_across  <- read.csv(str_c(dir_output_pre, 'fp_onset_bootstrap_across_data.csv')) %>%
  mutate(region = region %>% factor(levels = key_regions$region_label %>% unique()))%>%
  filter(!region %>% str_detect('LHA'))
```

```{r eval=FALSE}
plt_range <- c(-1, 0)

plt_df_bootstrap <- df_bootstrap_across %>%
  filter(sig == 1) %>%
  filter(boot_mean_observed > 0) %>%
  filter(time_rel_lick >= plt_range[1], time_rel_lick <= plt_range[2])

# y positions for significance markers (staggered per region)
plt_df_bootstrap <- plt_df_bootstrap %>%
  select(region) %>%
  unique() %>%
  arrange(desc(region)) %>%
  mutate(ypos = 3.2 + row_number() / 4) %>%
  left_join(plt_df_bootstrap)

plt_data_e %>%
  filter(time_rel_lick >= plt_range[1], time_rel_lick <= plt_range[2]) %>%
  ggplot(aes(x = time_rel_lick, y = zscore_blsub, group = region, color = region, fill = region)) +
  geom_vline(xintercept = 0, color = 'darkgrey', size = 1/2) +
  geom_hline(yintercept = 0, color = 'darkgrey', size = 1/2) +
  stat_summary(fun = 'mean', geom = 'line') +
  stat_summary(fun.data = 'mean_se', geom = 'ribbon', alpha = 1/3, color = NA) +
  geom_point(data = plt_df_bootstrap, aes(x = time_rel_lick, y = ypos, color = region), size = 0.5) +
  theme_ag01(6) +
  coord_cartesian(xlim = plt_range, ylim = c(-1, 5), expand = FALSE, clip = 'off') +
  scale_x_continuous(breaks = seq(-1, 0, 0.5)) +
  xlab('Time relative to first lick (s)') +
  ylab('Z-score') +
  scale_color_manual(values = color_values_regions_da7) +
  scale_fill_manual(values  = color_values_regions_da7) +
  force_panelsizes(rows = unit(2, 'cm'), cols = unit(2, 'cm'))

save_pdf(dir_output_e, str_c(fn_stem_e, '.pdf'), 6, 6)
plt_data_e           %>% write_csv(str_c(dir_output_e, fn_stem_e, '_data.csv'))
plt_df_bootstrap     %>% write_csv(str_c(dir_output_e, fn_stem_e, '_bootstrap.csv'))
```

---

## sfig07f: fp lick onset — onset time summary + stats
```{r eval=FALSE}
dir_output_f <- str_c(dir_output, 'f/')
dir.create(dir_output_f, recursive = TRUE, showWarnings = FALSE)

fn_stem_f <- 'fp_onset_summary'

plt_data_f <- read.csv(str_c(dir_output_pre, 'fp_onset_summary_data.csv')) %>%
  mutate(region = region %>% factor(levels = rev(key_regions$region_label %>% unique())))%>%
  filter(!region %>% str_detect('LHA'))
```


```{r eval=FALSE}
plt_data_f %>%
  ggplot(aes(region, time_rel_lick, color = region)) +
  geom_hline(yintercept = 0, color = 'darkgrey') +
  geom_boxplot(outlier.shape = NA) +
  theme_ag01(6) +
  scale_color_manual(values = rev(color_values_regions_da7)) +
  ylab('Time relative to first lick (s)') +
  xlab('') +
  coord_flip(xlim = c(0.5, 7.5), ylim = c(-0.75, 0.5), expand = FALSE, clip = 'off') +
  force_panelsizes(rows = unit(2, 'cm'), cols = unit(2, 'cm'))

save_pdf(dir_output_f, str_c(fn_stem_f, '.pdf'), 6, 6)
plt_data_f %>% write_csv(str_c(dir_output_f, fn_stem_f, '_data.csv'))
```

```{r eval=FALSE}
# one-way ANOVA: onset time ~ region (each subject contributes one value per region)
stats_data <- plt_data_f %>%
  ungroup() %>%
  mutate(subject_dummy = str_c(subject, '_', row_number()))

stats_list <- stats_data %>%
  aov_rm_one_between(dir_output_f, fn_stem_f, 'subject_dummy', 'time_rel_lick', 'region')

# pairwise HSD (region × region)
stats_list[[3]] %>%
  mutate(contrast1_between = contrast1_between %>% factor(levels = key_regions$region_label %>% unique())) %>%
  mutate(contrast2_between = contrast2_between %>% factor(levels = key_regions$region_label %>% unique())) %>%
  ggplot(aes(contrast1_between, contrast2_between, label = sig_symbol)) +
  geom_text()
```

---

## sfig07g: fp str sustained — fp response vs lick count (density heat map)
```{r eval=FALSE}
dir_output_g       <- str_c(dir_output, 'g/')
dir_combined_setid <- './data/combined_setid/'
dir.create(dir_output_g, recursive = TRUE, showWarnings = FALSE)

fn_stem_g <- 'fp_str_cor_zscore_vs_lick'

fns      <- list.files(dir_combined_setid)
fns_filt <- fns[fns %>% str_detect('filtlick_peth_summary_means_trial')]
fns_filt <- fns_filt %>% str_remove('.csv')

df_g <- combined_import(import_directory = dir_combined_setid,
                        filter_strings   = fns_filt,
                        prefixes         = NA,
                        suffixes         = c('.csv'),
                        verbose          = 0
                        )[[1]] %>%
  filt_and_format_data() %>%
  filter(time_bin == 'sustained')
```

```{r eval=FALSE}
df_g %>%
  filter(zscore_blsub_mean >= -10, zscore_blsub_mean <= 20,
         lick_count >= 0, lick_count <= 30) %>%
  ggplot(aes(zscore_blsub_mean, lick_count)) +
  stat_bin2d(aes(fill = ..density..), bins = 40) +
  scale_fill_viridis_c(option = 'magma', name = 'Density',
                       limits = c(0, 0.01), oob = scales::squish) +
  stat_cor(method = "pearson", label.y = 35, label.x = -8, size = 2) +
  facet_grid(set_id ~ region) +
  theme_ag01(6) +
  coord_cartesian(xlim = c(-10, 20), ylim = c(0, 30), expand = F, clip = 'off') +
  scale_x_continuous(breaks = seq(-10, 20, 10)) +
  theme(
    strip.text.x     = element_text(margin = margin(t = 5, b = 10)),
    strip.text       = element_text(margin = margin(t = 5, r = 5, b = 5, l = 5)),
    panel.spacing    = unit(1, "lines"),
    panel.background = element_rect(fill = viridis::magma(1))
  ) +
  ylab('Lick count') +
  xlab('Z-score sustained (2-3s)') +
  force_panelsizes(rows = unit(0.75, 'cm'), cols = unit(1.8, 'cm'))

save_pdf(dir_output_g, str_c(fn_stem_g, '.pdf'), 12, 6)
df_g %>% write_csv(str_c(dir_output_g, fn_stem_g, '_data.csv'))
```

---

## sfig07h: fp str — per-subject R² (zscore vs lick count correlation)
```{r eval=FALSE}
dir_output_h <- str_c(dir_output, 'h/')
dir.create(dir_output_h, recursive = TRUE, showWarnings = FALSE)

fn_stem_h <- 'fp_str_cor_zscore_vs_lick_subject_summary_combined'

corr_sbj <- df_g %>%
  tidy_cor('zscore_blsub_mean', 'lick_count', 'subject', 'region', 'set_id') %>%
  mutate(estimate_squared = estimate^2) %>%
  ungroup()
```

```{r eval=FALSE}
corr_sbj %>%
  ggplot(aes(set_id, estimate_squared, fill = region, color = region)) +
  stat_summary(fun.data = 'mean_se', geom = 'errorbar',
               position = position_dodge(width = 0.9), width = 0.4) +
  stat_summary(fun = 'mean', geom = 'col',
               position = position_dodge(width = 0.9), width = 0.6, color = NA) +
  geom_jitter(position = position_jitterdodge(jitter.width = 0.2, dodge.width = 0.9),
              shape = 21, stroke = 0.1, size = 1) +
  theme_ag01(6) +
  scale_color_manual(values = color_values_regions_da7) +
  scale_fill_manual(values  = color_values_regions_da7) +
  ylab('R^2') +
  xlab('') +
  coord_cartesian(xlim = c(0.5, 3.5), ylim = c(0, 1), clip = 'off', expand = 0) +
  force_panelsizes(rows = unit(3, 'cm'), cols = unit(6, 'cm'))

save_pdf(dir_output_h, str_c(fn_stem_h, '.pdf'), 8, 4)
corr_sbj %>% write_csv(str_c(dir_output_h, fn_stem_h, '_data.csv'))

stats_list <- corr_sbj %>%
  mutate(subject = str_c(subject, row_number())) %>%
  aov_rm_two_between(dir_output_h, fn_stem_h, 'subject', 'estimate_squared', 'region', 'set_id')
```

---

## sfig07i: fp str — binned lick count × solution (zscore heat map)
```{r eval=FALSE}
dir_output_i <- str_c(dir_output, 'i/')
dir.create(dir_output_i, recursive = TRUE, showWarnings = FALSE)

fn_stem_i <- 'fp_str_solution_vs_lickcountbinned_heat'

join_solution_x <- tibble(
  solution = c('sucrose00', 'sucrose05', 'sucrose10', 'sucrose20', 'sucrose30',
               'nacl000',   'nacl025',   'nacl050',   'nacl100',   'nacl150'),
  plt_x    = c(1, 2, 3, 4, 5, 5, 4, 3, 2, 1),
  plt_f    = c(1, 1, 1, 1, 1, 2, 2, 2, 2, 2)
)

plt_data_i <- df_g %>%
  select(subject, region, set_id, trial_num, solution, lick_count, zscore_blsub_mean) %>%
  mutate(lick_count_bin = cut(lick_count, seq(0, 25, 5))) %>%
  group_by(set_id, region, subject, solution, lick_count_bin) %>%
  summarise(zscore_blsub_mean        = zscore_blsub_mean %>% mean(),
            sample_count_per_subject = n(),
            .groups = 'drop') %>%
  filter(sample_count_per_subject >= 3) %>%
  group_by(set_id, region, solution, lick_count_bin) %>%
  summarise(zscore_blsub_mean = zscore_blsub_mean %>% mean(), .groups = 'drop') %>%
  left_join(join_solution_x)
```

```{r eval=FALSE}
plt_data_i %>%
  filter(!is.na(lick_count_bin)) %>%
  ggplot(aes(plt_x, lick_count_bin, fill = zscore_blsub_mean)) +
  geom_tile() +
  facet_grid(set_id ~ region) +
  theme_ag01(6) +
  coord_cartesian(xlim = c(0.5, 5.5), ylim = c(0.5, 5.5), expand = F) +
  scale_fill_viridis_c(limits = c(-1, 4), oob = scales::squish) +
  force_panelsizes(rows = unit(1, 'cm'), cols = unit(1, 'cm')) +
  ylab('Binned lick count') +
  xlab('Solution value (rank)')

save_pdf(dir_output_i, str_c(fn_stem_i, '.pdf'), 8, 4)
plt_data_i %>% write_csv(str_c(dir_output_i, fn_stem_i, '_data.csv'))
```

```{r eval=FALSE}
library(lme4)
library(lmerTest)

stats_data_i <- df_g %>%
  select(set_id, subject, region, solution, lick_count, zscore_blsub_mean)

results_i <- stats_data_i %>%
  group_by(set_id, region) %>%
  group_modify(~{
    m <- lmer(
      zscore_blsub_mean ~ lick_count * solution +
        (1 | subject),
      data    = .x,
      REML    = TRUE,
      control = lmerControl(optimizer = "bobyqa")
    )
    anova(m) %>%
      as.data.frame() %>%
      rownames_to_column('term')
  }) %>%
  ungroup()

results_i <- results_i %>%
  clean_names() %>%
  rename(p_value = pr_f) %>%
  quick_sig()

results_i %>% write_csv(str_c(dir_output_i, fn_stem_i, '_stats_mm.csv'))
```

---



