---
title: "sfig10"
author: "adam gordon-fennell"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = normalizePath('../'))
```

# setup
## libraries
```{r eval=FALSE}
source('./logs_and_keys/key_local_directories.R')
Sys.unsetenv("RETICULATE_PYTHON_FALLBACK")
Sys.unsetenv("RETICULATE_PYTHON")
reticulate::use_python(path_python, required = TRUE)


library(tidyverse)
library(afex)
library(emmeans)
library(janitor)
library(readxl)
library(ggh4x)
library(arrow)
library(zoo)
library(lubridate)
library(patchwork)
library(ggbeeswarm)
library(ggpubr)
library(pals)
library(boot)
library(corrplot)
library(Hmisc)
library(plotly)
library(pracma)

arrow::set_cpu_count(4)

source('./functions/params.R')
source('./functions/theme.R')
source('./functions/general.R')
source('./functions/r_general.R')
source('./functions/r_plots.R')
source('./functions/stats.R')
source('./functions/pca.R')
source('./functions/analysis_peth.R')
source('./functions/plotting_placements.R')
source('./functions/compile_data.R')
source('./functions/r_head_fixed_processing.R')
```

## directories
```{r eval=FALSE}
dir_output         <- './analysis_and_plots/sfig10/'
dir_output_pre     <- str_c(dir_output, 'pre/')
dir_combined_setid <- './data/combined_setid/'

dir.create(dir_output,     recursive = TRUE, showWarnings = FALSE)
dir.create(dir_output_pre, recursive = TRUE, showWarnings = FALSE)
```

## logs / keys
```{r eval=FALSE}
log_analysis_fp_ets   <- read_xlsx('./logs_and_keys/log_data_analysis.xlsx',
                                   sheet = 'fp_ets', na = c('NA', ''))
log_analysis_subjects <- read_xlsx('./logs_and_keys/log_data_analysis.xlsx',
                                   sheet = 'subjects', na = c('NA', ''))
log_analysis_exp      <- read_xlsx('./logs_and_keys/log_data_analysis.xlsx',
                                   sheet = 'experiments', na = c('NA', ''))
log_placements        <- read.csv('./logs_and_keys/log_fiber_placements.csv',
                                  na.strings = c('', 'NA'))

key_events            <- read.csv('./logs_and_keys/key_events_arduino.csv')
log_tdt               <- read.csv('./logs_and_keys/log_fiberphotometry_tdt.csv',
                                   na = c('', 'NA'))
log_npm               <- read.csv('./logs_and_keys/log_fiberphotometry_npm.csv',
                                   na = c('', 'NA'))
```

## local functions
```{r eval=FALSE}
return_stim_params <- function(import_fns, dir_extracted, file_format_output) {
  # takes extracted serial data and returns stim parameters for individual
  # stimulation events
  #
  # import_fns (vector of strings): vector of blocknames used for combined_import
  # dir_extracted (string): path to the directory for serial extraction
  # file_format_output (string): 'csv'
  #
  # output: stim_params — 1 row / stimulation with columns for each parameter

  data_list <- combined_import(
    import_directory = dir_extracted,
    filter_strings   = import_fns,
    prefixes         = NA,
    suffixes         = c(str_c('_param_dynamic.', file_format_output))
  )

  stim_params <- data_list[[1]] %>%
    select(blockname, param_dynamic, param_ts, param_value) %>%
    filter(param_dynamic %in% c('trial_stim_frequency',
                                'trial_stim_pulse_duration',
                                'trial_stim_train_duration')) %>%
    arrange(blockname, param_ts) %>%
    spread(param_dynamic, param_value) %>%
    group_by(blockname) %>%
    mutate(stim_num = row_number())

  return(stim_params)
}
```

---

# initial preprocessing steps

## directories (temp and network)
```{r eval=FALSE}
# dir_tdt, dir_npm, dir_arduino_raw set in key_local_directories.R
dir_temp             <- './data/sfig10/'
dir_temp_arduino_raw <- str_c(dir_temp, 'arduino/raw/')
dir_temp_extracted   <- str_c(dir_temp, 'arduino/extracted/')
dir_temp_sessions    <- str_c(dir_temp, 'sessions/')

dir.create(dir_temp_arduino_raw, recursive = TRUE, showWarnings = FALSE)
dir.create(dir_temp_extracted,   recursive = TRUE, showWarnings = FALSE)
dir.create(dir_temp_sessions,    recursive = TRUE, showWarnings = FALSE)
```

## arduino behavioral data
```{r eval=FALSE}
# requires: access to dir_arduino_raw; log_analysis_fp_ets (blockname column)
# output:   data/sfig10/arduino/raw/   (raw arduino CSVs)
#           data/sfig10/arduino/extracted/  (event, param, param_dynamic CSVs)
# 
# manual_blocknames <- log_analysis_fp_ets %>% pull(blockname)
# 
# import_arduino(manual_blocknames, dir_arduino_raw, dir_temp_arduino_raw, overwrite = 0)
# 
# extract_serial_output(
#   dir_temp_arduino_raw,
#   key_events,
#   dir_temp_extracted,
#   manual_experiments = NA,
#   manual_blocknames  = manual_blocknames,
#   file_format_output = 'csv',
#   overwrite = 0
# )
```

## FP data — save locally and preprocess
```{r eval=FALSE}
# requires: access to dir_tdt / dir_npm; arduino extraction complete (above)
# output:   data/sfig10/sessions/  (feather + csv per session)
# 
# import_key <- log_analysis_fp_ets %>%
#   select(experiment, subject, blockname, procedure, deprivation, imaging) %>%
#   left_join(log_analysis_exp, by = 'experiment')
# 
# import_key_filt <- import_key %>%
#   filter(experiment %in% c('acp', 'acr'))
# 
# locally_save_multispout_data_behavior(
#   import_key_filt, dir_temp_sessions, overwrite = 0)
# 
# locally_save_multispout_data_fp_peth(
#   import_key_filt, dir_temp_sessions, dir_tdt, dir_npm, overwrite = 0)
# 
# locally_save_multispout_data_fp_baseline(
#   import_key_filt, dir_temp_sessions, dir_tdt, dir_npm,
#   blockname_baselines = NA, overwrite = 0)
# 
# multispout_preprocess_fp_peth(
#   import_key_filt, dir_temp_sessions, log_tdt, log_npm)
# 
# multispout_preprocess_fp_baseline(
#   import_key_filt, dir_temp_sessions, log_tdt, log_npm)
```

---

# preprocessing
```{r eval=FALSE}
# requires: data/sfig10/sessions/ (feather + fp_events.csv per session)
#           data/sfig10/arduino/extracted/ (param_dynamic CSVs for stim params)
#           log_analysis_fp_ets (blockname, trials columns)
#           log_analysis_subjects (remove column)
#           log_placements (exclude_da_consumption, hit_ap/ml/dv columns)
# output:   sfig10/pre/data_streams_peth_full.csv
#           sfig10/pre/data_streams_peth_summary.csv
#           sfig10/pre/data_streams_peth_summary_group.csv
#           sfig10/pre/data_streams_peth_summary_trace_subject.csv
#           sfig10/pre/data_streams_peth_summary_trace_group.csv
#           sfig10/pre/data_events.csv
#           sfig10/pre/str_consumption_sustained.csv
# NOTE: comment out this entire section after sfig10/pre/ CSVs have been generated
#       and data/sfig10/ can be deleted
#
# dir.create(dir_output_pre, recursive = TRUE, showWarnings = FALSE)
# 
# manual_blocknames <- log_analysis_fp_ets %>% pull(blockname)
# 
# # ── 1. stim parameters from extracted arduino data ────────────────────────────
# stim_params <- return_stim_params(
#   manual_blocknames, dir_temp_extracted, file_format_output = 'csv') %>%
#   select(blockname, event_number_arduino = stim_num, trial_stim_frequency)
# 
# # ── 2. read FP peth feather files ─────────────────────────────────────────────
# file_paths <- list.files(dir_temp_sessions,
#                          pattern = '_streams_peth_preprocessed.feather',
#                          recursive = TRUE, full.names = TRUE)
# 
# file_paths <- file_paths %>%
#   keep(~ str_detect(.x, str_c(manual_blocknames, collapse = '|')))
# 
# for (file_path in file_paths) {
#   loop_streams_peth <- read_feather(file_path) %>%
#     mutate(signal_wavelength = signal_wavelength %>% as.character()) %>%
#     ungroup()
# 
#   loop_events <- read.csv(
#     file_path %>% str_replace('_streams_peth_preprocessed.feather', '_fp_events.csv'))
# 
#   if (file_path == file_paths[1]) {
#     streams_peth <- loop_streams_peth
#     events       <- loop_events
#   } else {
#     streams_peth <- loop_streams_peth %>% bind_rows(streams_peth, .)
#     events       <- loop_events       %>% bind_rows(events, .)
#   }
# }
# 
# # ── 3. trim peth time range ───────────────────────────────────────────────────
# streams_peth <- streams_peth %>%
#   filter(time_rel > -3, time_rel < 12)
# 
# # ── 4. parse trial mA from log ────────────────────────────────────────────────
# trial_ids <- log_analysis_fp_ets %>%
#   select(blockname, trials) %>%
#   mutate(trials = str_remove_all(trials, '[//{//};]')) %>%
#   mutate(trials = str_split(trials, ',')) %>%
#   unnest_longer(trials, values_to = 'stim_id') %>%
#   mutate(stim_id = as.integer(stim_id)) %>%
#   group_by(blockname) %>%
#   mutate(event_number = row_number()) %>%
#   ungroup() %>%
#   mutate(mA = case_when(
#     stim_id == 0 ~ 0,
#     stim_id == 1 ~ 0.05,
#     stim_id == 2 ~ 0.5
#   ))
# 
# # ── 5. join mA to streams_peth and events ────────────────────────────────────
# streams_peth <- streams_peth %>%
#   left_join(trial_ids %>% select(blockname, event_number, mA),
#             by = c('blockname', 'event_number'))
# 
# events <- events %>%
#   filter(event_id_char == 'trial_start') %>%
#   left_join(trial_ids %>% select(blockname, event_number, mA),
#             by = c('blockname', 'event_number'))
# 
# # ── 6. subject, region formatting, placement and subject filters ──────────────
# streams_peth <- streams_peth %>%
#   mutate(subject = blockname %>% str_sub(12, 16)) %>%
#   format_regions('region', key_regions) %>%
#   filter_placements('exclude_da_consumption')
# 
# subjects_to_remove <- log_analysis_subjects %>%
#   filter(remove == 1) %>%
#   pull(subject)
# 
# streams_peth <- streams_peth %>%
#   filter(!subject %in% subjects_to_remove)
# 
# events <- events %>%
#   mutate(subject = blockname %>% str_sub(12, 16)) %>%
#   filter(!subject %in% subjects_to_remove)
# 
# # ── 7. compute summaries ──────────────────────────────────────────────────────
# analysis_summary_range <- 5
# 
# streams_peth_summary <- streams_peth %>%
#   filter(time_rel > 0, time_rel < analysis_summary_range) %>%
#   group_by(blockname, subject, mA, region) %>%
#   summarise(zscore_blsub = mean(zscore_blsub), .groups = 'drop')
# 
# streams_peth_summary_group <- streams_peth_summary %>%
#   group_by(mA, region) %>%
#   summarise(zscore_blsub = mean(zscore_blsub), .groups = 'drop')
# 
# streams_peth <- streams_peth %>%
#   mutate(region = region %>% factor(levels = key_regions$region_label %>% unique()))
# 
# streams_peth_summary <- streams_peth_summary %>%
#   mutate(region = region %>% factor(levels = key_regions$region_label %>% unique()))
# 
# streams_peth_summary_group <- streams_peth_summary_group %>%
#   mutate(region = region %>% factor(levels = key_regions$region_label %>% unique()))
# 
# streams_peth_subject <- streams_peth %>%
#   mutate(time_rel = round_down_to_nearest_05(time_rel)) %>%
#   group_by(subject, region, time_rel, mA) %>%
#   summarise(zscore_blsub = mean(zscore_blsub), .groups = 'drop')
# 
# streams_peth_group <- streams_peth %>%
#   mutate(time_rel = round_down_to_nearest_05(time_rel)) %>%
#   group_by(region, time_rel, mA) %>%
#   summarise(
#     zscore_blsub_sem = sd(zscore_blsub) / sqrt(n()),
#     zscore_blsub     = mean(zscore_blsub),
#     .groups = 'drop')
# 
# # ── 8. assemble consumption sustained data ────────────────────────────────────
# fns_filt <- list.files(dir_combined_setid) %>%
#   keep(~ str_detect(.x, 'filtlick_peth_summary_means_subject')) %>%
#   keep(~ str_detect(.x, str_c(c('wrnacl','wrsuc','frsuc'), collapse = '|'))) %>%
#   str_remove('.csv')
# 
# str_consumption <- combined_import(
#   import_directory = dir_combined_setid,
#   filter_strings   = fns_filt,
#   prefixes         = NA,
#   suffixes         = c('.csv'),
#   verbose          = 0
# )[[1]] %>%
#   filter(time_bin == 'sustained') %>%
#   filter(!region %>% str_detect('LHA')) %>%
#   select(set_id, subject, region, solution, zscore_blsub_mean)
# 
# # ── 9. write all preprocessed files ──────────────────────────────────────────
# streams_peth %>%
#   select(blockname, subject, branch_id, region, time, time_rel,
#          event_number, mA, zscore_blsub) %>%
#   write_csv(str_c(dir_output_pre, 'data_streams_peth_full.csv'))
# 
# streams_peth_summary %>%
#   write_csv(str_c(dir_output_pre, 'data_streams_peth_summary.csv'))
# 
# streams_peth_summary_group %>%
#   write_csv(str_c(dir_output_pre, 'data_streams_peth_summary_group.csv'))
# 
# streams_peth_subject %>%
#   write_csv(str_c(dir_output_pre, 'data_streams_peth_summary_trace_subject.csv'))
# 
# streams_peth_group %>%
#   write_csv(str_c(dir_output_pre, 'data_streams_peth_summary_trace_group.csv'))
# 
# events %>%
#   write_csv(str_c(dir_output_pre, 'data_events.csv'))
# 
# str_consumption %>%
#   write_csv(str_c(dir_output_pre, 'str_consumption_sustained.csv'))
```

---

# data import
```{r eval=FALSE}
streams_peth <- read.csv(str_c(dir_output_pre, 'data_streams_peth_full.csv')) %>%
  mutate(region = region %>% factor(levels = key_regions$region_label %>% unique()))

streams_peth_group <- read.csv(
  str_c(dir_output_pre, 'data_streams_peth_summary_trace_group.csv')) %>%
  mutate(region = region %>% factor(levels = key_regions$region_label %>% unique()))
```

---

## sfig10b: PETH region overlay (0.5 mA)
```{r eval=FALSE}
dir_output_b <- str_c(dir_output, 'b/')
dir.create(dir_output_b, recursive = TRUE, showWarnings = FALSE)

fn_stem_b <- 'ets_peth_overlay'

plt_data_b <- streams_peth_group %>%
  filter(mA == 0.5) %>%
  filter(time_rel > -3, time_rel < 12) %>%
  mutate(facet_regions = ifelse(region %>% str_detect('LHA'), 'lha', 'str'))
```

```{r eval=FALSE}
plt <- plt_data_b %>%
  ggplot(aes(time_rel, zscore_blsub, color = region, fill = region)) +
  annotate('rect', xmin = 0, xmax = 1, ymin = -Inf, ymax = Inf,
           alpha = 1/3, fill = 'darkgrey') +
  geom_hline(yintercept = 0, color = 'darkgrey', size = 0.5) +
  geom_ribbon(aes(ymax = zscore_blsub + zscore_blsub_sem,
                  ymin = zscore_blsub - zscore_blsub_sem,
                  fill = region),
              color = NA, alpha = 1/3) +
  geom_line() +
  facet_grid(. ~ facet_regions) +
  theme_ag01() +
  scale_color_manual(values = color_values_regions) +
  scale_fill_manual(values  = color_values_regions)

plt <- plt %>%
  add_scale_bar(origin = c(-3, -2), x_len = 1, y_len = 1)

plt +
  force_panelsizes(cols = unit(6, 'cm'), rows = unit(9, 'cm'))

save_pdf(dir_output_b, str_c(fn_stem_b, '.pdf'), 12, 8)
plt_data_b %>% write_csv(str_c(dir_output_b, fn_stem_b, '_data.csv'))
```

---

## sfig10c: PETH by mA level (top) + summary bar mA × region and stats (bottom)
```{r eval=FALSE}
dir_output_c <- str_c(dir_output, 'c/')
dir.create(dir_output_c, recursive = TRUE, showWarnings = FALSE)
```

### sfig10c top: PETH by mA level, faceted by region
```{r eval=FALSE}
fn_stem_c_top <- 'ets_peth'

plt_data_c_top <- streams_peth_group %>%
  mutate(mA = as.character(mA)) %>%
  filter(time_rel > -1, time_rel < 15)
```

```{r eval=FALSE}
plt <- plt_data_c_top %>%
  ggplot(aes(time_rel, zscore_blsub, color = mA, fill = mA, group = mA)) +
  annotate('rect', xmin = 0, xmax = 1, ymin = -Inf, ymax = Inf,
           alpha = 1/3, fill = 'darkgrey') +
  geom_hline(yintercept = 0, color = 'darkgrey', size = 0.5) +
  geom_ribbon(aes(ymax = zscore_blsub + zscore_blsub_sem,
                  ymin = zscore_blsub - zscore_blsub_sem),
              color = NA, alpha = 1/3) +
  geom_line() +
  facet_grid(. ~ region) +
  theme_ag01() +
  scale_color_viridis_d(end = 0.8, option = 'magma') +
  scale_fill_viridis_d(end  = 0.8, option = 'magma')

plt <- plt %>%
  add_scale_bar(origin = c(-3, -2), x_len = 1, y_len = 1)

plt +
  force_panelsizes(cols = unit(10, 'mm'), rows = unit(20, 'mm'))

save_pdf(dir_output_c, str_c(fn_stem_c_top, '.pdf'), 12, 8)
plt_data_c_top %>% write_csv(str_c(dir_output_c, fn_stem_c_top, '_data.csv'))
```

---

### sfig10c bottom: summary bar mA × region + stats
```{r eval=FALSE}
fn_stem_c <- 'ets_summary'

plt_data_c <- streams_peth %>%
  filter(time_rel > 0, time_rel <= 3) %>%
  group_by(subject, mA, region) %>%
  summarise(zscore_blsub = mean(zscore_blsub), .groups = 'drop') %>%
  mutate(mA     = mA %>% as.character()) %>%
  mutate(region = region %>% factor(levels = key_regions$region_label %>% unique())) %>%
  rename(zscore = zscore_blsub)
```

```{r eval=FALSE}
regions <- plt_data_c %>% pull(region) %>% unique()

for (loop_region in regions) {
  stats_list <- plt_data_c %>%
    filter(region == loop_region) %>%
    aov_rm_one_within(NA, NA, 'subject', 'zscore', 'mA')

  loop_stats_main <- stats_list[[2]] %>% mutate(region = loop_region)
  loop_stats_hsd  <- stats_list[[3]] %>% mutate(region = loop_region)

  if (loop_region == regions[1]) {
    stats_main <- loop_stats_main
    stats_hsd  <- loop_stats_hsd
  } else {
    stats_main <- loop_stats_main %>% bind_rows(stats_main, .)
    stats_hsd  <- loop_stats_hsd  %>% bind_rows(stats_hsd,  .)
  }
}

plt_annotations <- stats_main %>%
  filter(effect == 'mA') %>%
  select(region, sig_symbol) %>%
  mutate(mA = 2, zscore = 5.5) %>%
  mutate(region = region %>% factor(levels = key_regions$region_label %>% unique()))

plt_data_c %>%
  ggplot(aes(mA, zscore)) +
  geom_hline(yintercept = 0, color = 'darkgrey', linewidth = 1/3) +
  stat_summary(fun = 'mean', geom = 'line', aes(group = 1)) +
  stat_summary(fun.data = 'mean_se', geom = 'errorbar', aes(group = 1), width = 0) +
  geom_text(data = plt_annotations, aes(label = sig_symbol)) +
  facet_grid(. ~ region) +
  theme_ag01(6) +
  coord_cartesian(xlim = c(0.5, 3.5), ylim = c(-3, 6), expand = F) +
  scale_y_continuous(breaks = seq(-3, 6, 3)) +
  theme(strip.text.x = element_text(margin = margin(t = 5, b = 5))) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3)) +
  force_panelsizes(cols = unit(10, 'mm'), rows = unit(20, 'mm'))

save_pdf(dir_output_c, str_c(fn_stem_c, '.pdf'), 12, 8)
plt_data_c    %>% write_csv(str_c(dir_output_c, fn_stem_c, '_data.csv'))
stats_main    %>% write_csv(str_c(dir_output_c, fn_stem_c, '_aov.csv'))
stats_hsd     %>% write_csv(str_c(dir_output_c, fn_stem_c, '_aov_hsd.csv'))
```

---

## sfig10d: fiber placement maps + correlations
```{r eval=FALSE}
dir_output_d <- str_c(dir_output, 'd/')
dir.create(dir_output_d, recursive = TRUE, showWarnings = FALSE)

fn_stem_d <- 'ets'

plt_data_d <- streams_peth %>%
  filter(mA == 0.5) %>%
  filter(time_rel > 0, time_rel <= 3) %>%
  group_by(subject, mA, region) %>%
  summarise(zscore_blsub = mean(zscore_blsub), .groups = 'drop') %>%
  mutate(mA     = mA %>% as.character()) %>%
  mutate(region = region %>% factor(levels = key_regions$region_label %>% unique())) %>%
  rename(zscore = zscore_blsub) %>%
  filter(!region %>% str_detect('LHA')) %>%
  join_placements()

color_limits_d <- c(-3, 3)
```

```{r eval=FALSE}
plt_str(
  df            = plt_data_d,
  var_color     = !!sym('zscore'),
  var_color_name = 'zs',
  vars_facet    = c('.', '.'),
  plt_plane     = 'sagittal',
  plt_dim_base  = 3,
  color_limits  = color_limits_d
)
save_pdf(str_c(dir_output_d), str_c(fn_stem_d, '_sagittal.pdf'), 6, 6)

plt_str(
  df            = plt_data_d,
  var_color     = !!sym('zscore'),
  var_color_name = 'zs',
  vars_facet    = c('.', '.'),
  plt_plane     = 'horizontal',
  plt_dim_base  = 3,
  color_limits  = color_limits_d
)
save_pdf(str_c(dir_output_d), str_c(fn_stem_d, '_horizontal.pdf'), 6, 6)

plt_str(
  df            = plt_data_d,
  var_color     = !!sym('zscore'),
  var_color_name = 'zs',
  vars_facet    = c('.', '.'),
  plt_plane     = 'coronal',
  plt_dim_base  = 3,
  color_limits  = color_limits_d
)
save_pdf(str_c(dir_output_d), str_c(fn_stem_d, '_coronal.pdf'), 6, 6)

tryCatch(
  plt_str_3d(
    df           = plt_data_d,
    var_color    = 'zscore',
    color_limits = color_limits_d,
    dir_output   = dir_output_d,
    fn_stem      = fn_stem_d,
    toggle_save  = 1
  ),
  error = function(e) message('plt_str_3d skipped (kaleido): ', conditionMessage(e))
)
```

---

## sfig10e: ETS vs consumption correlation
```{r eval=FALSE}
dir_output_e <- str_c(dir_output, 'e/')
dir.create(dir_output_e, recursive = TRUE, showWarnings = FALSE)

# ETS sustained response (0.5 mA, 0–3 s)
plt_data_ets <- streams_peth %>%
  filter(mA == 0.5) %>%
  filter(time_rel > 0, time_rel <= 3) %>%
  group_by(subject, mA, region) %>%
  summarise(zscore_blsub = mean(zscore_blsub), .groups = 'drop') %>%
  mutate(mA = mA %>% as.character()) %>%
  rename(zscore_ets = zscore_blsub)

# Consumption sustained response (from preprocessed file)
str_consumption <- read.csv(str_c(dir_output_pre, 'str_consumption_sustained.csv'))
```

```{r eval=FALSE}
# sfig10e left — ETS vs NaCl 1.5 M consumption
fn_stem_e_left <- 'ets_corr_consumption_nacl150'

plt_data_nacl150 <- plt_data_ets %>%
  left_join(
    str_consumption %>% filter(solution == 'nacl150'),
    by = c('subject', 'region')
  ) %>%
  filter(!region %>% str_detect('LHA')) %>%
  mutate(region = region %>% factor(levels = key_regions$region_label %>% unique()))

plt_data_nacl150 %>%
  ggplot(aes(zscore_blsub_mean, zscore_ets, group = 1)) +
  geom_hline(yintercept = 0, color = 'darkgrey', linewidth = 1/2) +
  geom_vline(xintercept = 0, color = 'darkgrey', linewidth = 1/2) +
  geom_smooth(method = 'lm', size = 0.3, alpha = 1/5, color = 'black', formula = y ~ x) +
  stat_cor(method = 'pearson', size = 2, label.y = 7, label.x = 0, hjust = 0.5) +
  geom_point(shape = 21, stroke = 1/3, color = 'white', size = 2, alpha = 1,
             aes(fill = region)) +
  scale_fill_manual(values = color_values_regions[4:length(color_values_regions)]) +
  theme_ag01(6) +
  coord_cartesian(ylim = c(-6, 6), xlim = c(-3, 3), expand = F, clip = 'off') +
  force_panelsizes(rows = unit(3, 'cm'), cols = unit(3, 'cm')) +
  ylab('Electric tail shock response (zs)') +
  xlab('1.5 M NaCl response (zs)')

save_pdf(dir_output_e, str_c(fn_stem_e_left, '.pdf'), 4, 4)
plt_data_nacl150 %>% write_csv(str_c(dir_output_e, fn_stem_e_left, '_data.csv'))
```

```{r eval=FALSE}
# sfig10e right — ETS vs water (0.0 M NaCl) consumption
fn_stem_e_right <- 'ets_corr_consumption_nacl000'

plt_data_nacl000 <- plt_data_ets %>%
  left_join(
    str_consumption %>% filter(solution == 'nacl000'),
    by = c('subject', 'region')
  ) %>%
  filter(!region %>% str_detect('LHA')) %>%
  mutate(region = region %>% factor(levels = key_regions$region_label %>% unique()))

plt_data_nacl000 %>%
  ggplot(aes(zscore_blsub_mean, zscore_ets, group = 1)) +
  geom_hline(yintercept = 0, color = 'darkgrey', linewidth = 1/2) +
  geom_vline(xintercept = 0, color = 'darkgrey', linewidth = 1/2) +
  geom_smooth(method = 'lm', size = 0.3, alpha = 1/5, color = 'black', formula = y ~ x) +
  stat_cor(method = 'pearson', size = 2, label.y = 7, label.x = 1.5, hjust = 0.5) +
  geom_point(shape = 21, stroke = 1/3, color = 'white', size = 2, alpha = 1,
             aes(fill = region)) +
  scale_fill_manual(values = color_values_regions[4:length(color_values_regions)]) +
  theme_ag01(6) +
  coord_cartesian(ylim = c(-6, 6), xlim = c(-3, 6), expand = F, clip = 'off') +
  force_panelsizes(rows = unit(3, 'cm'), cols = unit(3, 'cm')) +
  ylab('Electric tail shock response (zs)') +
  xlab('0.0 M NaCl response (zs)')

save_pdf(dir_output_e, str_c(fn_stem_e_right, '.pdf'), 4, 4)
plt_data_nacl000 %>% write_csv(str_c(dir_output_e, fn_stem_e_right, '_data.csv'))
```

```{r eval=FALSE}
# combined correlation stats across both solutions
bind_rows(
  plt_data_nacl000 %>% rename(zscore_consumption = zscore_blsub_mean),
  plt_data_nacl150 %>% rename(zscore_consumption = zscore_blsub_mean)
) %>%
  select(solution, region, subject, zscore_ets, zscore_consumption) %>%
  tidy_cor('zscore_ets', 'zscore_consumption', 'solution') %>%
  write_csv(str_c(dir_output_e, 'ets_corr_consumption_stats.csv'))
```

---

## sfig10f: ETS vs LHA stimulation correlation
```{r eval=FALSE}
dir_output_f <- str_c(dir_output, 'f/')
dir.create(dir_output_f, recursive = TRUE, showWarnings = FALSE)

fn_stem_f <- 'ets_corr_lhastim'

# LHA stimulation group summary — per-subject initial bar data (20 Hz, VGAT and VGlut2)
df_lha_stimulation <- read.csv(
  './analysis_and_plots/fig02_sfig04/c/opto_stim_20hz_region_bar_sustained_data.csv') %>%
  filter(group_combined %in% c('vgat_stim', 'vglut2_stim')) %>%
  group_by(group_combined, region) %>%
  summarise(zscore_lhastim = mean(zscore), .groups = 'drop')
```


```{r eval=FALSE}
plt_data_f <- streams_peth %>%
  filter(mA == 0.5) %>%
  filter(time_rel > 0, time_rel <= 3) %>%
  group_by(subject, mA, region) %>%
  summarise(zscore_blsub = mean(zscore_blsub), .groups = 'drop') %>%
  mutate(mA = mA %>% as.character()) %>%
  rename(zscore_ets = zscore_blsub) %>%
  group_by(region) %>%
  summarise(zscore_ets = mean(zscore_ets)) %>%
  left_join(df_lha_stimulation, by = 'region') %>%
  filter(!is.na(group_combined)) %>%
  mutate(region = region %>% factor(levels = key_regions$region_label %>% unique()))

plt_data_f %>%
  ggplot(aes(zscore_lhastim, zscore_ets)) +
  geom_hline(yintercept = 0, color = 'darkgrey', linewidth = 1/2) +
  geom_vline(xintercept = 0, color = 'darkgrey', linewidth = 1/2) +
  geom_smooth(method = 'lm', size = 0.3, alpha = 1/5, color = 'black', formula = y ~ x) +
  stat_cor(method = 'pearson', size = 2, label.y = 6, label.x = 7.5, hjust = 0.5) +
  geom_point(shape = 21, stroke = 1/3, color = 'white', size = 2, alpha = 1,
             aes(fill = region)) +
  scale_fill_manual(values = color_values_regions[4:length(color_values_regions)]) +
  facet_grid(. ~ group_combined) +
  theme_ag01(6) +
  coord_cartesian(ylim = c(-6, 6), xlim = c(-5, 20), expand = F, clip = 'off') +
  force_panelsizes(rows = unit(3, 'cm'), cols = unit(3, 'cm')) +
  theme(strip.text.x   = element_text(margin = margin(b = 10))) +
  theme(panel.spacing.x = unit(0.5, 'cm')) +
  ylab('Electric tail shock response (zs)') +
  xlab('LHA stimulation response (zs)')

save_pdf(dir_output_f, str_c(fn_stem_f, '.pdf'), 4, 4)
plt_data_f %>% write_csv(str_c(dir_output_f, fn_stem_f, '_data.csv'))

plt_data_f %>%
  tidy_cor('zscore_ets', 'zscore_lhastim', 'group_combined') %>%
  write_csv(str_c(dir_output_f, fn_stem_f, '_stats.csv'))
```
