---
title: "sfig09"
author: "adam gordon-fennell"
date: '2026-06-11'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# run all chunks from the project root so relative paths resolve correctly
knitr::opts_knit$set(root.dir = normalizePath('../'))
```

# setup
## libraries
```{r}
source('./logs_and_keys/key_local_directories.R')
Sys.unsetenv("RETICULATE_PYTHON_FALLBACK")
Sys.unsetenv("RETICULATE_PYTHON")
reticulate::use_python(path_python, required = TRUE)

library(tidyverse)
library(afex)
library(emmeans)
library(janitor)
library(readxl)
library(ggh4x)     # force_panelsizes
library(scales)    # rescale, squish
library(arrow)
library(zoo)
library(lubridate)
library(patchwork)
library(ggbeeswarm)
library(ggpubr)    # stat_cor
library(pals)
library(boot)      # bootstrapping
library(corrplot)
library(Hmisc)
library(plotly)
library(lme4)
library(lmerTest)
library(viridisLite)

arrow::set_cpu_count(4)


source('./functions/theme.R')
source('./functions/general.R')
source('./functions/r_general.R')
source('./functions/r_plots.R')
source('./functions/stats.R')
source('./functions/pca.R')
source('./functions/analysis_peth.R')
source('./functions/plotting_placements.R')
source('./functions/params.R')
```

## directories
```{r}
dir_combined_setid   <- './data/combined_setid/'
dir_localdata_sessions <- './data/sessions/'
dir_output           <- './analysis_and_plots/sfig09/'

dir.create(dir_output, recursive = TRUE, showWarnings = FALSE)
```

## logs / keys
```{r}
log_analysis_subjects <- read_xlsx('./logs_and_keys/log_data_analysis.xlsx', sheet = 'subjects',    na = c('NA', ''))
log_analysis_fp       <- read_xlsx('./logs_and_keys/log_data_analysis.xlsx', sheet = 'fp',          na = c('NA', ''))
log_analysis_exp      <- read_xlsx('./logs_and_keys/log_data_analysis.xlsx', sheet = 'experiments', na = c('NA', ''))
log_placements        <- read.csv('./logs_and_keys/log_fiber_placements.csv', na.strings = c('', 'NA'))
```

---

# analysis / plotting
## setup helpers
```{r eval=FALSE}
# solution factor key: solution codes → display labels, colors, x-positions
solution_factor_key <- read_csv('./functions/factor_solution.csv', show_col_types = FALSE) %>%
  arrange(factor_level)

solution_levels <- solution_factor_key$solution_label %>% unique()
solution_colors <- solution_factor_key$color          %>% unique()

# saccharine-specific solution levels / colors (used by sfig09b–d)
sacc_solutions       <- c('water', 'sucrose05', 'sucrose10', 'sucrose20', 'sacc20')
solution_levels_sacc <- solution_factor_key %>%
  filter(solution %in% sacc_solutions) %>%
  pull(solution_label) %>% unique()
solution_colors_sacc <- solution_factor_key %>%
  filter(solution %in% sacc_solutions) %>%
  pull(color) %>% unique()

# set_id colors: WR:Suc, FR:Suc, WR:NaCl, FR:Sacc, WR:Water, WR/Sat:Suc
#                  1          2        3         4        5           6
colors_setid <- c("#7edb00", "#007edb", "#db007e", "#DB7E00", "black", "#DBD700")

# extended filt_and_format_data: filters regions and set_id, joins solution labels
filt_and_format_data <- function(df) {
  df %>%
    mutate(region = region %>% factor(levels = unique(key_regions$region_label))) %>%
    format_set_id(key_set_id) %>%
    left_join(solution_factor_key %>% select(solution, solution_label), by = 'solution') %>%
    mutate(solution_label = factor(solution_label, levels = solution_levels))
}

get_solution_rank <- function(df) {
  df %>%
    mutate(solution_rank = case_when(
      solution %in% c('sucrose00', 'nacl150') ~ 1,
      solution %in% c('sucrose05', 'nacl100') ~ 2,
      solution %in% c('sucrose10', 'nacl050') ~ 3,
      solution %in% c('sucrose20', 'nacl025') ~ 4,
      solution %in% c('sucrose30', 'nacl000') ~ 5
    ))
}
```

---

## preprocessing
# water trace / binned licking trace: computed from raw sessions and saved to pre/
# all other panels read pre-computed CSVs directly from data/combined_setid/
```{r eval=FALSE}
toggle_process <- 0  # 1 = load from sessions and save  |  0 = read saved CSVs

dir_output_pre <- str_c(dir_output, 'pre/')
dir.create(dir_output_pre, recursive = TRUE, showWarnings = FALSE)
```


```{r eval=FALSE}
if (toggle_process == 1) {
  # ── 1. build subject / session log for water sets ────────────────────────────
  subjects_include <- log_analysis_subjects %>%
    filter(inclusion_consumption == 1) %>%
    pull(subject)

  log_data <- log_analysis_fp %>%
    filter(is.na(exclude) | exclude != 1) %>%
    filter(subject %in% subjects_include) %>%
    get_set_id() %>%
    filter(!is.na(set_id))

  subjects_wrwater <- log_data %>%
    filter(set_id == 'wrwater') %>%
    pull(subject) %>%
    unique()

  log_data <- log_data %>%
    filter(subject %in% subjects_wrwater) %>%
    filter(set_id %in% c('wrnacl', 'frsuc', 'wrsuc', 'frmultisacc', 'wrwater'))

  set_ids_water <- c('frmultisacc', 'frsuc', 'wrnacl', 'wrsuc', 'wrwater')

  fns_qc_metrics      <- list.files(dir_localdata_sessions, pattern = 'quality_metrics.csv', recursive = TRUE, full.names = TRUE)
  combined_qc_metrics <- bind_rows(lapply(fns_qc_metrics, read.csv))

  process_blocknames <- log_data %>% pull(blockname)

  # ── 2. FP trace (water solution only, all regions) ───────────────────────────
  df_fp_peth <- combine_session_fp(process_blocknames, dir_localdata_sessions) %>%
    left_join(log_data %>% select(blockname, subject), by = 'blockname')

  df_fp_peth <- df_fp_peth %>%
    filter_qc_metrics(combined_qc_metrics, removal_type = 1) %>%
    format_regions('region', key_regions) %>%
    filter_placements('exclude_da_consumption') %>%
    filter(trial_lick == 1) %>%
    filter(time_rel >= -3, time_rel <= 8)

  plt_data_trace <- df_fp_peth %>%
    left_join(log_data %>% select(blockname, set_id), by = 'blockname') %>%
    left_join(solution_factor_key %>% select(solution, solution_label), by = 'solution') %>%
    filter(solution_label == 'Water') %>%
    group_by(set_id, region, solution, time_rel) %>%
    summarise(
      zscore_blsub_sem  = sd(zscore_blsub) / sqrt(n()),
      zscore_blsub_mean = mean(zscore_blsub),
      .groups = 'drop'
    ) %>%
    format_set_id(key_set_id) %>%
    mutate(region = region %>% factor(levels = key_regions$region_label %>% unique()))

  plt_data_trace %>% write_csv(str_c(dir_output_pre, 'fp_str_water_trace_data.csv'))

  # ── 3. binned licking trace (water solution only) ────────────────────────────
  df_binnedlick <- combine_session_binnedlick(process_blocknames, dir_localdata_sessions) %>%
    left_join(log_data %>% select(blockname, set_id, subject), by = 'blockname') %>%
    mutate(time_rel = time_bin / 1000) %>%
    select(-time_bin) %>%
    mutate(lick_hz = count_binned / (100 / 1000)) %>%
    select(-count_binned) %>%
    filter(trial_lick == 1) %>%
    group_by(set_id, solution, time_rel) %>%
    summarise(
      lick_hz_sem  = sd(lick_hz) / sqrt(n()),
      lick_hz_mean = mean(lick_hz),
      .groups = 'drop'
    ) %>%
    format_set_id(key_set_id) %>%
    left_join(solution_factor_key %>% select(solution, solution_label), by = 'solution') %>%
    mutate(solution_label = factor(solution_label, levels = solution_levels)) %>%
    filter(solution_label == 'Water')

  df_binnedlick %>% write_csv(str_c(dir_output_pre, 'fp_str_water_binnedlick_data.csv'))

} else {

  message('toggle_process = 0: preprocessing CSVs will be read by each section as needed')

}
```

---

## sfig09b: saccharine licking (left) + lick vs z-score correlation (right)
```{r eval=FALSE}
dir_output_b <- str_c(dir_output, 'b/')
dir.create(dir_output_b, recursive = TRUE, showWarnings = FALSE)

# subject-level licking summary (mean across sessions then across trials)
df_trial_sacc <- read_csv(str_c(dir_combined_setid, 'frmultisacc_full_peth_summary_means_trial.csv'), show_col_types = FALSE) %>%
  filt_and_format_data()

df_licking_summary_sacc <- df_trial_sacc %>%
  filter(time_bin == 'access') %>%
  select(blockname, subject, trial_num, solution, solution_label, lick_count) %>%
  unique() %>%
  group_by(blockname, subject, solution, solution_label) %>%
  summarise(lick_count = mean(lick_count), .groups = 'drop') %>%
  group_by(subject, solution, solution_label) %>%
  summarise(lick_count = mean(lick_count), .groups = 'drop') %>%
  mutate(solution_label = factor(solution_label, levels = solution_levels_sacc))

df_fp_summary_sacc <- read_csv(str_c(dir_combined_setid, 'frmultisacc_filtlick_peth_summary_means_subject.csv'), show_col_types = FALSE) %>%
  filt_and_format_data() %>%
  mutate(solution_label = factor(solution_label, levels = solution_levels_sacc))
```

```{r eval=FALSE}
# ── left: licking by solution ─────────────────────────────────────────────────
fn_stem_b_lick <- 'fp_sacc_summary_combined_licking'

df_licking_summary_sacc %>%
  ggplot(aes(solution_label, lick_count, group = 1)) +
  geom_line(aes(group = subject), linewidth = 1/2, alpha = 1/4) +
  stat_summary(fun = 'mean', geom = 'line') +
  stat_summary(fun.data = 'mean_se', geom = 'errorbar', width = 0) +
  theme_ag01(6) +
  coord_cartesian(xlim = c(0.5, 5.5), ylim = c(0, 20), expand = FALSE) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3)) +
  ylab('Lick count') +
  force_panelsizes(cols = unit(10, 'mm'), rows = unit(13.447, 'mm'))

save_pdf(dir_output_b, str_c(fn_stem_b_lick, '.pdf'), 12, 12)
df_licking_summary_sacc %>% write_csv(str_c(dir_output_b, fn_stem_b_lick, '_data.csv'))

stats_list_lick <- df_licking_summary_sacc %>%
  aov_rm_one_within(dir_output_b, fn_stem_b_lick, 'subject', 'lick_count', 'solution')
```

```{r eval=FALSE}
# ── licking correlation: sacc20 vs sucrose10 ─────────────────────────────────
fn_stem_b_corr <- 'fp_sacc_summary_combined_licking_corr_sacc_vs_sucrose10'

df_licking_corr <- df_licking_summary_sacc %>%
  filter(solution %in% c('sacc20', 'sucrose10')) %>%
  select(subject, solution, lick_count) %>%
  spread(solution, lick_count)

df_licking_corr %>%
  ggplot(aes(sucrose10, sacc20)) +
  geom_abline(slope = 1, intercept = 0, linewidth = 1/3, color = 'darkgrey') +
  geom_smooth(method = 'lm', color = 'red', fill = 'red', linewidth = 1/2) +
  stat_cor(method = 'pearson', size = 2, label.y = 16, aes(group = 1), color = 'black') +
  geom_point(size = 1/2) +
  theme_ag01(6) +
  coord_cartesian(xlim = c(0, 15), ylim = c(0, 15), expand = FALSE, clip = 'off') +
  force_panelsizes(cols = unit(13.447, 'mm'), rows = unit(13.447, 'mm'))

stats_corr <- df_licking_corr %>% tidy_cor('sacc20', 'sucrose10')

save_pdf(dir_output_b, str_c(fn_stem_b_corr, '.pdf'), 12, 12)
df_licking_corr  %>% write_csv(str_c(dir_output_b, fn_stem_b_corr, '_data.csv'))
stats_corr       %>% write_csv(str_c(dir_output_b, fn_stem_b_corr, '_stats_cor.csv'))
```

---

## sfig09c: saccharine — sucrose10 vs sacc20 (binned lick left, trace top, summary bar bottom)
```{r eval=FALSE}
dir_output_c <- str_c(dir_output, 'c/')
dir.create(dir_output_c, recursive = TRUE, showWarnings = FALSE)

# binned licking trace
df_binnedlick_sacc <- read_csv(str_c(dir_combined_setid, 'frmultisacc_full_binnedlick_trace_overall.csv'), show_col_types = FALSE) %>%
  format_set_id(key_set_id) %>%
  left_join(solution_factor_key %>% select(solution, solution_label), by = 'solution') %>%
  mutate(solution_label = factor(solution_label, levels = solution_levels_sacc))

# trace data for the sucrose10 vs sacc20 comparison (top sub-panel below)
plt_data_trace_sacc <- read_csv(str_c(dir_combined_setid, 'frmultisacc_filtlick_peth_summary_trace_overall.csv'), show_col_types = FALSE) %>%
  filt_and_format_data() %>%
  mutate(solution_label = factor(solution_label, levels = solution_levels_sacc))
```

```{r eval=FALSE}
# ── left: binned licking trace (sucrose10 vs sacc20) ─────────────────────────
fn_stem_c_lick <- 'fp_sacc_binnedlick_10suc_20sacc'

plt_data_c_lick <- df_binnedlick_sacc %>%
  filter(solution %in% c('sucrose10', 'sacc20'))

plt <- plt_data_c_lick %>%
  ggplot(aes(time_rel, lick_hz_mean, group = solution_label, color = solution_label, fill = solution_label)) +
  annotate("rect", xmin = 0, xmax = 3, ymin = -Inf, ymax = Inf, alpha = 1/3, fill = "darkgrey") +
  geom_hline(yintercept = 0, color = 'darkgrey', size = 0.5) +
  geom_ribbon(aes(ymin = lick_hz_mean - lick_hz_sem,
                  ymax = lick_hz_mean + lick_hz_sem),
              alpha = 1/3, color = NA) +
  geom_line() +
  scale_color_manual(values = solution_colors_sacc[c(3, 5)]) +
  scale_fill_manual(values  = solution_colors_sacc[c(3, 5)]) +
  theme_ag01(6) +
  theme(strip.text = element_text(margin = margin(t = 5, r = 5, b = 5, l = 5))) +
  theme(panel.spacing.y = unit(0.8, "lines")) +
  force_panelsizes(rows = unit(2, 'cm'), cols = unit(2, 'cm'))

plt <- plt %>%
  add_scale_bar(origin = c(-(3 * 0.1), -1), x_len = 1, y_len = 1)

plt
save_pdf(dir_output_c, str_c(fn_stem_c_lick, '.pdf'), 12, 12)
plt_data_c_lick %>% write_csv(str_c(dir_output_c, fn_stem_c_lick, '_data.csv'))
```

```{r eval=FALSE, fig.width=9, fig.height = 3}
# ── top: FP trace (sucrose10 vs sacc20) ──────────────────────────────────────
fn_stem_c_trace <- 'fp_sacc_trace_10suc_20sacc'

plt_data_c_trace <- plt_data_trace_sacc %>%
  filter(solution %in% c('sucrose10', 'sacc20'))

plt <- plt_data_c_trace %>%
  ggplot(aes(time_rel, zscore_blsub_mean, group = solution_label, color = solution_label, fill = solution_label)) +
  annotate("rect", xmin = 0, xmax = 3, ymin = -Inf, ymax = Inf, alpha = 1/3, fill = "darkgrey") +
  geom_hline(yintercept = 0, color = 'darkgrey', size = 0.5) +
  geom_ribbon(aes(ymin = zscore_blsub_mean - zscore_blsub_sem,
                  ymax = zscore_blsub_mean + zscore_blsub_sem),
              alpha = 1/3, color = NA) +
  geom_line() +
  facet_grid(set_id ~ region) +
  scale_color_manual(values = solution_colors_sacc[c(3, 5)]) +
  scale_fill_manual(values  = solution_colors_sacc[c(3, 5)]) +
  theme_ag01(6) +
  theme(strip.text = element_text(margin = margin(t = 5, r = 5, b = 5, l = 5))) +
  theme(panel.spacing.y = unit(0.8, "lines")) +
  force_panelsizes(rows = unit(2, 'cm'), cols = unit(2, 'cm'))

plt <- plt %>%
  add_scale_bar(origin = c(-3, -1), x_len = 1, y_len = 1)

plt
save_pdf(dir_output_c, str_c(fn_stem_c_trace, '.pdf'), 12, 12)
plt_data_c_trace %>% write_csv(str_c(dir_output_c, fn_stem_c_trace, '_data.csv'))
```

```{r eval=FALSE}
# ── bottom: summary bar sacc20 vs sucrose10 (sustained) ──────────────────────
fn_stem_c_bar <- 'fp_sacc_summary_combined_sustained_sacc_vs_sucrose10'

plt_data_c_bar <- df_fp_summary_sacc %>%
  filter(solution %in% c('sacc20', 'sucrose10')) %>%
  filter(time_bin == 'sustained')

ttest_results_c <- plt_data_c_bar %>%
  select(subject, region, solution, zscore_blsub_mean) %>%
  spread(solution, zscore_blsub_mean) %>%
  tidy_ttest_paired(NA, NA, 'sacc20', 'sucrose10', 'region') %>%
  quick_sig()

plt_annotation_c <- ttest_results_c %>%
  mutate(solution_label = 1.5, zscore_blsub_mean = 4.8)

plt_data_c_bar %>%
  ggplot(aes(solution_label, zscore_blsub_mean, group = 1)) +
  geom_hline(yintercept = 0, size = 1/4, color = 'darkgrey') +
  geom_line(aes(group = subject), alpha = 1/4) +
  stat_summary(fun = 'mean', geom = 'line') +
  stat_summary(fun.data = 'mean_se', geom = 'errorbar', width = 0) +
  geom_text(data = plt_annotation_c, aes(label = sig_symbol)) +
  theme_ag01(6) +
  facet_grid(. ~ region) +
  coord_cartesian(xlim = c(0, 3), ylim = c(-2.5, 5), expand = FALSE, clip = 'off') +
  theme(panel.spacing.y = unit(0.8, "lines")) +
  theme(strip.text = element_text(margin = margin(t = 5, r = 5, b = 5, l = 5))) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3)) +
  force_panelsizes(cols = unit(13.447, 'mm'), rows = unit(13.447, 'mm'))

save_pdf(dir_output_c, str_c(fn_stem_c_bar, '.pdf'), 12, 12)
plt_data_c_bar   %>% write_csv(str_c(dir_output_c, fn_stem_c_bar, '_data.csv'))
ttest_results_c  %>% write_csv(str_c(dir_output_c, fn_stem_c_bar, '_stats_ttest.csv'))
```

---

## sfig09d: saccharine delta bar (sacc20 − sucrose10, sustained)
```{r eval=FALSE}
dir_output_d <- str_c(dir_output, 'd/')
dir.create(dir_output_d, recursive = TRUE, showWarnings = FALSE)

fn_stem_d <- 'fp_sacc_summary_combined_sustained_sacc_vs_sucrose10_delta'

plt_data_d <- df_fp_summary_sacc %>%
  filter(solution %in% c('sacc20', 'sucrose10')) %>%
  filter(time_bin == 'sustained') %>%
  select(subject, region, solution, zscore_blsub_mean) %>%
  spread(solution, zscore_blsub_mean) %>%
  mutate(sacc20_minus_sucrose10 = sacc20 - sucrose10)
```

```{r eval=FALSE}
plt_data_d %>%
  ggplot(aes(region, sacc20_minus_sucrose10)) +
  stat_summary(fun = 'mean', geom = 'bar', aes(group = 1), width = 2/3, alpha = 1/3) +
  stat_summary(fun.data = 'mean_se', geom = 'errorbar', aes(group = 1), width = 0) +
  geom_hline(yintercept = 0, linewidth = 1/2, color = 'darkgrey') +
  theme_ag01(6) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3)) +
  coord_cartesian(xlim = c(0.5, 9.5), ylim = c(-0.5, 2.0), clip = 'off', expand = 0) +
  force_panelsizes(rows = unit(26, 'mm'), cols = unit(23, 'mm')) +
  theme(strip.text = element_text(margin = margin(t = 5, r = 5, b = 5, l = 5))) +
  theme(panel.spacing.y = unit(0.8, "lines")) +
  ylab('Saccharine - sucrose') +
  xlab('')

save_pdf(dir_output_d, str_c(fn_stem_d, '.pdf'), 12, 12)
plt_data_d %>% write_csv(str_c(dir_output_d, fn_stem_d, '_data.csv'))

# stats: one-way ANOVA, STR regions
stats_list_d_str <- plt_data_d %>%
  filter(!region %>% str_detect('LHA')) %>%
  mutate(subject_dummy = str_c(subject, '_', row_number())) %>%
  aov_rm_one_between(dir_output_d, str_c(fn_stem_d, '_str'), 'subject_dummy', 'sacc20_minus_sucrose10', 'region')

# stats: one-way ANOVA, LHA regions
stats_list_d_lha <- plt_data_d %>%
  filter(region %>% str_detect('LHA')) %>%
  mutate(subject_dummy = str_c(subject, '_', row_number())) %>%
  aov_rm_one_between(dir_output_d, str_c(fn_stem_d, '_lha'), 'subject_dummy', 'sacc20_minus_sucrose10', 'region')
```

---

## sfig09f: water lick rate (left: binned lick trace, right: lick count bar)
```{r eval=FALSE}
dir_output_f <- str_c(dir_output, 'f/')
dir.create(dir_output_f, recursive = TRUE, showWarnings = FALSE)

set_ids_water <- c('frmultisacc', 'frsuc', 'wrnacl', 'wrsuc', 'wrwater')
order_set_id      <- c('WR:NaCl', 'WR:Water', 'WR:Suc', 'FR:Suc', 'FR:Sacc')
order_set_id_indx <- c(3, 5, 1, 2, 4)

# binned lick trace from preprocessing
df_binnedlick_water <- read.csv(str_c(dir_output_pre, 'fp_str_water_binnedlick_data.csv')) %>%
  mutate(set_id = factor(set_id, levels = order_set_id))

# subject-level licking summary from combined_setid
subjects_include <- log_analysis_subjects %>%
  filter(inclusion_consumption == 1) %>%
  pull(subject)

log_data_water <- log_analysis_fp %>%
  filter(is.na(exclude) | exclude != 1) %>%
  filter(subject %in% subjects_include) %>%
  get_set_id() %>%
  filter(!is.na(set_id))

subjects_wrwater <- log_data_water %>%
  filter(set_id == 'wrwater') %>%
  pull(subject) %>%
  unique()

log_data_water <- log_data_water %>%
  filter(subject %in% subjects_wrwater) %>%
  filter(set_id %in% set_ids_water)

fns_f <- list.files(dir_combined_setid)
fns_f_trial <- fns_f[fns_f %>% str_detect('filtlick') &
                     fns_f %>% str_detect('peth_summary_means_trial')] %>%
  str_remove('.csv')
fns_f_trial <- fns_f_trial[grepl(paste(set_ids_water, collapse = "|"), fns_f_trial)]

plt_data_licking_f <- combined_import(
  import_directory = dir_combined_setid,
  filter_strings   = fns_f_trial,
  prefixes         = NA,
  suffixes         = c('.csv'),
  verbose          = 0
)[[1]] %>%
  filter(set_id %in% set_ids_water) %>%
  filter(subject %in% log_data_water$subject) %>%
  filt_and_format_data() %>%
  filter(solution_label == 'Water') %>%
  filter(time_bin == 'sustained') %>%
  select(blockname, set_id, subject, trial_num, solution_label, lick_count) %>%
  unique()

plt_data_licking_summary_f <- plt_data_licking_f %>%
  group_by(set_id, subject, solution_label) %>%
  summarise(
    lick_count            = mean(lick_count),
    .groups = 'drop'
  ) %>%
  mutate(set_id = factor(set_id, levels = order_set_id))
```

```{r eval=FALSE}
# ── left: binned licking trace ────────────────────────────────────────────────
fn_stem_f_lick <- 'fp_str_water_binnedlick'

plt <- df_binnedlick_water %>%
  ggplot(aes(time_rel, lick_hz_mean, group = set_id, color = set_id, fill = set_id)) +
  annotate("rect", xmin = 0, xmax = 3, ymin = -Inf, ymax = Inf, alpha = 1/3, fill = "darkgrey") +
  geom_hline(yintercept = 0, color = 'darkgrey', size = 0.5) +
  geom_ribbon(aes(ymin = lick_hz_mean - lick_hz_sem,
                  ymax = lick_hz_mean + lick_hz_sem),
              alpha = 1/3, color = NA) +
  geom_line() +
  scale_color_manual(values = colors_setid[order_set_id_indx]) +
  scale_fill_manual(values  = colors_setid[order_set_id_indx]) +
  theme_ag01(6) +
  theme(strip.text = element_text(margin = margin(t = 5, r = 5, b = 5, l = 5))) +
  theme(panel.spacing.y = unit(0.8, "lines")) +
  force_panelsizes(rows = unit(2, 'cm'), cols = unit(2, 'cm'))

plt <- plt %>%
  add_scale_bar(origin = c(-(3 * 0.1), -1), x_len = 1, y_len = 1)

plt
save_pdf(dir_output_f, str_c(fn_stem_f_lick, '.pdf'), 12, 12)
df_binnedlick_water %>% write_csv(str_c(dir_output_f, fn_stem_f_lick, '_data.csv'))
```

```{r eval=FALSE}
# ── right: lick count bar by set_id ──────────────────────────────────────────
fn_stem_f_bar <- 'fp_str_water_summary_licking'

plt_data_licking_summary_f %>%
  ggplot(aes(set_id, lick_count, color = set_id, fill = set_id)) +
  geom_hline(yintercept = 0, size = 1/4, color = 'darkgrey') +
  stat_summary(fun = 'mean', geom = 'bar', aes(group = 1), width = 2/3, alpha = 1/3, color = NA) +
  stat_summary(fun.data = 'mean_se', geom = 'errorbar', aes(group = 1), width = 0) +
  theme_ag01(6) +
  theme(axis.text.x = element_blank()) +
  coord_cartesian(xlim = c(0.2, 5.8), ylim = c(0, 20), clip = 'off', expand = 0) +
  force_panelsizes(rows = unit(13.448, 'mm'), cols = unit(10, 'mm')) +
  theme(strip.text = element_text(margin = margin(t = 5, r = 5, b = 5, l = 5))) +
  theme(panel.spacing.y = unit(0.8, "lines")) +
  scale_color_manual(values = colors_setid[order_set_id_indx]) +
  scale_fill_manual(values  = colors_setid[order_set_id_indx]) +
  ylab('Lick count') +
  xlab('')

save_pdf(dir_output_f, str_c(fn_stem_f_bar, '.pdf'), 12, 12)
plt_data_licking_summary_f %>% write_csv(str_c(dir_output_f, fn_stem_f_bar, '_data.csv'))

# one-way ANOVA: lick count ~ set_id (between subjects, dummy for repeated)
stats_list_f <- plt_data_licking_summary_f %>%
  mutate(subject_dummy = subject %>% str_c('_', row_number())) %>%
  aov_rm_one_between(dir_output_f, fn_stem_f_bar, 'subject_dummy', 'lick_count', 'set_id')
```

---

## sfig09g: water FP (top: trace, bottom: summary bar + one-way ANOVA)
```{r eval=FALSE}
dir_output_g <- str_c(dir_output, 'g/')
dir.create(dir_output_g, recursive = TRUE, showWarnings = FALSE)

# FP trace from preprocessing
plt_data_trace_water <- read.csv(str_c(dir_output_pre, 'fp_str_water_trace_data.csv')) %>%
  mutate(region = region %>% factor(levels = key_regions$region_label %>% unique())) %>%
  mutate(set_id = factor(set_id, levels = order_set_id))

# FP subject summary from combined_setid
fns_g <- list.files(dir_combined_setid)
fns_g_sbj <- fns_g[fns_g %>% str_detect('filtlick') &
                   fns_g %>% str_detect('peth_summary_means_subject')] %>%
  str_remove('.csv')
fns_g_sbj <- fns_g_sbj[grepl(paste(set_ids_water, collapse = "|"), fns_g_sbj)]

plt_data_summary_g <- combined_import(
  import_directory = dir_combined_setid,
  filter_strings   = fns_g_sbj,
  prefixes         = NA,
  suffixes         = c('.csv'),
  verbose          = 0
)[[1]] %>%
  filter(set_id %in% set_ids_water) %>%
  filter(subject %in% log_data_water$subject) %>%
  filt_and_format_data() %>%
  filter(solution_label == 'Water') %>%
  mutate(set_id = factor(set_id, levels = order_set_id))
```

```{r eval=FALSE, fig.width = 9, fig.height = 3}
# ── top: FP trace ─────────────────────────────────────────────────────────────
fn_stem_g_trace <- 'fp_str_water_trace'

plt <- plt_data_trace_water %>%
  ggplot(aes(time_rel, zscore_blsub_mean, group = set_id, color = set_id, fill = set_id)) +
  annotate("rect", xmin = 0, xmax = 3, ymin = -Inf, ymax = Inf, alpha = 1/3, fill = "darkgrey") +
  geom_hline(yintercept = 0, color = 'darkgrey', size = 0.5) +
  geom_ribbon(aes(ymin = zscore_blsub_mean - zscore_blsub_sem,
                  ymax = zscore_blsub_mean + zscore_blsub_sem),
              alpha = 1/3, color = NA) +
  geom_line() +
  facet_grid(. ~ region) +
  scale_color_manual(values = colors_setid[order_set_id_indx]) +
  scale_fill_manual(values  = colors_setid[order_set_id_indx]) +
  theme_ag01(6) +
  theme(strip.text = element_text(margin = margin(t = 5, r = 5, b = 5, l = 5))) +
  theme(panel.spacing.y = unit(0.8, "lines")) +
  force_panelsizes(rows = unit(2, 'cm'), cols = unit(2, 'cm'))

plt <- plt %>%
  add_scale_bar(origin = c(-3, -1), x_len = 1, y_len = 1)

plt
save_pdf(dir_output_g, str_c(fn_stem_g_trace, '.pdf'), 12, 12)
plt_data_trace_water %>% write_csv(str_c(dir_output_g, fn_stem_g_trace, '_data.csv'))
```

```{r eval=FALSE, fig.width = 9, fig.height = 3}
# ── bottom: summary bar (sustained) + one-way RM ANOVA (set_id within region) ─
fn_stem_g_bar <- 'fp_str_water_summary_peth_sustained'

plt_data_g_bar <- plt_data_summary_g %>%
  filter(time_bin == 'sustained')

plt_data_g_bar %>%
  ggplot(aes(set_id, zscore_blsub_mean, color = set_id, fill = set_id)) +
  geom_hline(yintercept = 0, size = 1/4, color = 'darkgrey') +
  stat_summary(fun = 'mean', geom = 'bar', aes(group = 1), width = 2/3, alpha = 1/3, color = NA) +
  stat_summary(fun.data = 'mean_se', geom = 'errorbar', aes(group = 1), width = 0) +
  theme_ag01(6) +
  theme(axis.text.x = element_blank()) +
  facet_grid(. ~ region, scales = 'free') +
  coord_cartesian(xlim = c(0.5, 5.5), ylim = c(-2, 6), clip = 'off', expand = 0) +
  force_panelsizes(rows = unit(4, 'cm'), cols = unit(2, 'cm')) +
  theme(strip.text = element_text(margin = margin(t = 5, r = 5, b = 5, l = 5))) +
  theme(panel.spacing.y = unit(0.8, "lines")) +
  scale_color_manual(values = colors_setid[order_set_id_indx]) +
  scale_fill_manual(values  = colors_setid[order_set_id_indx]) +
  ylab('Z-score sustained (2-3 s)') +
  xlab('')

save_pdf(dir_output_g, str_c(fn_stem_g_bar, '.pdf'), 12, 12)
plt_data_g_bar %>% write_csv(str_c(dir_output_g, fn_stem_g_bar, '_data.csv'))

# one-way RM ANOVA per region: set_id effect
regions_g <- unique(plt_data_g_bar$region)

results_g <- map(regions_g, function(r) {
  plt_data_g_bar %>%
    filter(region == r) %>%
    aov_rm_one_within(NA, NA, 'subject', 'zscore_blsub_mean', 'set_id')
})

stats_main_g <- map_dfr(seq_along(regions_g), function(i) {
  results_g[[i]][[2]] %>% mutate(region = regions_g[i], .before = 1)
})
stats_hsd_g <- map_dfr(seq_along(regions_g), function(i) {
  results_g[[i]][[3]] %>% mutate(region = regions_g[i], .before = 1)
})

stats_main_g %>% write_csv(str_c(dir_output_g, fn_stem_g_bar, '_aov.csv'))
stats_hsd_g  %>% write_csv(str_c(dir_output_g, fn_stem_g_bar, '_aov_hsd.csv'))
```

---

## sfig09h: water response heat map by set_id (mean sustained z-score)
```{r eval=FALSE}
dir_output_h <- str_c(dir_output, 'h/')
dir.create(dir_output_h, recursive = TRUE, showWarnings = FALSE)

fn_stem_h <- 'fp_str_water_summary_peth_sustained_heat'

plt_data_h <- plt_data_summary_g %>%
  filter(time_bin == 'sustained') %>%
  group_by(set_id, region) %>%
  summarise(zscore_blsub_mean = mean(zscore_blsub_mean), .groups = 'drop')

set_order_h <- plt_data_h %>%
  group_by(set_id) %>%
  summarise(zscore_blsub_mean_overall = mean(zscore_blsub_mean), .groups = 'drop') %>%
  arrange(zscore_blsub_mean_overall) %>%
  pull(set_id)
```

```{r eval=FALSE}
lo_h <- -1
hi_h <-  4

plt_data_h %>%
  mutate(set_id = set_id %>% factor(levels = set_order_h)) %>%
  ggplot(aes(region, set_id, fill = zscore_blsub_mean)) +
  geom_tile() +
  theme_ag01(6) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3)) +
  coord_cartesian(xlim = c(0.5, 9.5), ylim = c(0.5, 5.5), clip = 'off', expand = 0) +
  force_panelsizes(rows = unit(13.445, 'mm'), cols = unit(30, 'mm')) +
  theme(strip.text = element_text(margin = margin(t = 5, r = 5, b = 5, l = 5))) +
  theme(panel.spacing.y = unit(0.8, "lines")) +
  ylab('') + xlab('') +
  scale_fill_gradientn(
    colours = c("blue", "white", "red"),
    values  = rescale(c(lo_h, 0, hi_h)),
    limits  = c(lo_h, hi_h),
    oob     = squish
  )

save_pdf(dir_output_h, str_c(fn_stem_h, '.pdf'), 12, 12)
plt_data_h %>% write_csv(str_c(dir_output_h, fn_stem_h, '_data.csv'))
```

---

## sfig09i: water response binned by licking (heat map + mixed model)
```{r eval=FALSE}
dir_output_i <- str_c(dir_output, 'i/')
dir.create(dir_output_i, recursive = TRUE, showWarnings = FALSE)

fn_stem_i <- 'fp_str_water_heat_setid_vs_binnedlick'

# trial-level data (already loaded for sfig09f; reload with wider columns)
fns_i <- list.files(dir_combined_setid)
fns_i_trial <- fns_i[fns_i %>% str_detect('filtlick') &
                     fns_i %>% str_detect('peth_summary_means_trial')] %>%
  str_remove('.csv')
fns_i_trial <- fns_i_trial[grepl(paste(set_ids_water, collapse = "|"), fns_i_trial)]

plt_data_trial_i <- combined_import(
  import_directory = dir_combined_setid,
  filter_strings   = fns_i_trial,
  prefixes         = NA,
  suffixes         = c('.csv'),
  verbose          = 0
)[[1]] %>%
  filter(set_id %in% set_ids_water) %>%
  filter(subject %in% log_data_water$subject) %>%
  filt_and_format_data() %>%
  filter(solution_label == 'Water') %>%
  filter(time_bin == 'sustained') %>%
  select(set_id, blockname, subject, region, trial_num, solution, solution_label, lick_count, zscore_blsub_mean)

# licking normalization within set_id × subject
plt_data_licking_i <- plt_data_trial_i %>%
  select(blockname, set_id, subject, trial_num, solution_label, lick_count) %>%
  unique() %>%
  group_by(set_id, subject) %>%
  mutate(mean_setid_lick_count   = mean(lick_count)) %>%
  mutate(lick_count_normalized   = lick_count / mean_setid_lick_count) %>%
  ungroup()

plt_data_trial_i <- plt_data_trial_i %>%
  left_join(plt_data_licking_i %>%
              select(blockname, set_id, trial_num, lick_count_normalized),
            by = c('set_id', 'blockname', 'trial_num')) %>%
  mutate(set_id = factor(set_id, levels = order_set_id))

plt_data_trial_binnedlick_i <- plt_data_trial_i %>%
  mutate(lick_count_binned = cut(lick_count, breaks = seq(0, 25, 5))) %>%
  group_by(set_id, subject, region, solution, solution_label, lick_count_binned) %>%
  summarise(
    sample_count          = n(),
    zscore_blsub_mean     = mean(zscore_blsub_mean),
    lick_count_normalized = mean(lick_count_normalized),
    .groups = 'drop'
  )
```

```{r eval=FALSE}
# ── heat map: lick bin × set_id ───────────────────────────────────────────────
lo_i <- -2
hi_i <-  4

plt_data_heat_i <- plt_data_trial_binnedlick_i %>%
  group_by(set_id, region, solution_label, lick_count_binned) %>%
  summarise(zscore_blsub_mean = mean(zscore_blsub_mean), .groups = 'drop') %>%
  filter(!is.na(lick_count_binned))

plt_data_heat_i %>%
  ggplot(aes(lick_count_binned, set_id, fill = zscore_blsub_mean)) +
  geom_tile() +
  facet_grid(. ~ region) +
  theme_ag01(6) +
  coord_cartesian(xlim = c(0.5, 5.5), ylim = c(0.5, 5.5), clip = 'off', expand = 0) +
  force_panelsizes(rows = unit(12, 'mm'), cols = unit(9.578, 'mm')) +
  theme(strip.text = element_text(margin = margin(t = 5, r = 5, b = 5, l = 5))) +
  theme(panel.spacing.y = unit(0.8, "lines")) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3)) +
  ylab('') + xlab('') +
  scale_fill_gradientn(
    colours = c("blue", "white", "red"),
    values  = rescale(c(lo_i, 0, hi_i)),
    limits  = c(lo_i, hi_i),
    oob     = squish
  )

save_pdf(dir_output_i, str_c(fn_stem_i, '.pdf'), 12, 12)
plt_data_heat_i %>% write_csv(str_c(dir_output_i, fn_stem_i, '_data.csv'))
```

```{r eval=FALSE}
# ── mixed model: set_id × lick_count interaction per region ──────────────────
model_data_i <- plt_data_trial_i %>%
  select(set_id, subject, blockname, region, trial_num, lick_count, zscore_blsub_mean) %>%
  mutate(lick_count_scaled = scale(lick_count)[, 1])

regions_i <- levels(model_data_i$region)

region_models_i <- map(set_names(regions_i), function(reg) {
  df <- filter(model_data_i, region == reg)
  tryCatch(
    lmer(
      zscore_blsub_mean ~ set_id * lick_count_scaled +
        (1 + lick_count_scaled | subject) +
        (1 | blockname),
      data    = df,
      REML    = TRUE,
      control = lmerControl(optimizer = "bobyqa")
    ),
    error = function(e) { message("Failed for region: ", reg, "\n", e$message); NULL }
  )
})

region_anova_i <- map_dfr(region_models_i, function(m) {
  if (is.null(m)) return(NULL)
  anova(m) %>%
    as.data.frame() %>%
    rownames_to_column("term") %>%
    filter(term %in% c("set_id", "lick_count_scaled", "set_id:lick_count_scaled"))
}, .id = "region") %>%
  clean_names()

region_anova_i %>% write_csv(str_c(dir_output_i, fn_stem_i, '_stats_mmanova.csv'))

region_anova_i %>%
  rename(p_value = pr_f) %>%
  quick_sig() %>%
  mutate(region = region %>% factor(levels = key_regions$region_label %>% unique())) %>%
  ggplot(aes(region, term, label = sig_symbol)) +
  geom_text()
```

---

## sfig09j: satiation licking by trial bin (solution × trial bin heat map)
```{r eval=FALSE}
dir_output_j <- str_c(dir_output, 'j/')
dir.create(dir_output_j, recursive = TRUE, showWarnings = FALSE)

set_ids_sat <- c('frmultisacc', 'frsuc', 'wrnacl', 'wrsuc', 'wrwater', 'wrwatersat')

# trial-level data for satiation analysis
fns_sat <- list.files(dir_combined_setid)
fns_sat_trial <- fns_sat[fns_sat %>% str_detect('filtlick') &
                         !fns_sat %>% str_detect('triallick') &
                         fns_sat %>% str_detect('peth_summary_means_trial')] %>%
  str_remove('.csv')
fns_sat_trial <- fns_sat_trial[grepl(paste(set_ids_sat, collapse = "|"), fns_sat_trial)]

plt_data_trial_sat <- combined_import(
  import_directory = dir_combined_setid,
  filter_strings   = fns_sat_trial,
  prefixes         = NA,
  suffixes         = c('.csv'),
  verbose          = 0
)[[1]] %>%
  filt_and_format_data() %>%
  filter(!fn %>% str_detect('_triallick.csv'))

plt_data_licking_sat <- plt_data_trial_sat %>%
  filter(time_bin == 'sustained') %>%
  select(blockname, set_id, subject, trial_num, solution, solution_label, lick_count) %>%
  unique()

# binned trial licking (10-trial bins)
plt_data_licking_binned_sat <- plt_data_licking_sat %>%
  mutate(bin_trial = str_pad(((trial_num - 1) %/% 10) * 10, width = 2, pad = "0")) %>%
  group_by(blockname, set_id, subject, bin_trial, solution, solution_label) %>%
  summarise(lick_count = mean(lick_count), .groups = 'drop') %>%
  group_by(blockname, set_id, subject, bin_trial) %>%
  mutate(lick_count_binned_mean = mean(lick_count)) %>%
  ungroup() %>%
  mutate(lick_count_binned_mean_normalized = lick_count / lick_count_binned_mean)

plt_data_licking_binned_summary_sat <- plt_data_licking_binned_sat %>%
  group_by(set_id, subject, bin_trial, solution_label) %>%
  summarise(
    lick_count_mean                    = mean(lick_count),
    lick_count_binned_mean_normalized  = mean(lick_count_binned_mean_normalized),
    .groups = 'drop'
  )
```

```{r eval=FALSE}
fn_stem_j <- 'fp_satiation_water_trialbin_setid_licking'

plt_data_j <- plt_data_licking_binned_sat %>%
  filter(set_id %in% c('WR:Suc', 'FR:Suc', 'WR:NaCl'))

plt_data_j %>%
  mutate(bin_trial = bin_trial %>% as.integer()) %>%
  ggplot(aes(solution_label, lick_count, group = bin_trial, color = bin_trial)) +
  stat_summary(fun = 'mean', geom = 'line') +
  scale_color_viridis_c(end = 0.6, option = 'magma', direction = -1) +
  facet_grid(. ~ set_id, scales = 'free') +
  theme_ag01(6) +
  coord_cartesian(xlim = c(0.5, 5.5), ylim = c(0, 25), expand = FALSE, clip = 'off') +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3)) +
  force_panelsizes(rows = unit(20, 'mm'), col = unit(10, 'mm')) +
  ylab('Mean lick count') +
  xlab('')

save_pdf(dir_output_j, str_c(fn_stem_j, '.pdf'), 12, 12)
plt_data_j %>% write_csv(str_c(dir_output_j, fn_stem_j, '_data.csv'))

# mixed model: lick_count ~ bin_trial * solution (per set_id)
results_j <- plt_data_j %>%
  group_by(set_id) %>%
  group_modify(~{
    m <- lmer(lick_count ~ bin_trial * solution + (1 | subject),
              data    = .x,
              REML    = TRUE,
              control = lmerControl(optimizer = "bobyqa"))
    anova(m) %>% as.data.frame() %>% rownames_to_column('term')
  }) %>%
  ungroup() %>%
  clean_names()

results_j %>% write_csv(str_c(dir_output_j, fn_stem_j, '_aov.csv'))
```

---

## sfig09k: satiation rank × trial bin (left: licking, right: z-score)
```{r eval=FALSE}
dir_output_k <- str_c(dir_output, 'k/')
dir.create(dir_output_k, recursive = TRUE, showWarnings = FALSE)

# binned trial signal data
fns_sat_bins <- fns_sat[fns_sat %>% str_detect('filtlick') &
                        fns_sat %>% str_detect('peth_summary_means_binnedtrial')] %>%
  str_remove('.csv')
fns_sat_bins <- fns_sat_bins[grepl(paste(set_ids_sat, collapse = "|"), fns_sat_bins)]

plt_data_bins_sat <- combined_import(
  import_directory = dir_combined_setid,
  filter_strings   = fns_sat_bins,
  prefixes         = NA,
  suffixes         = c('.csv'),
  verbose          = 0
)[[1]] %>%
  filter(!fn %>% str_detect('_triallick.csv')) %>%
  filt_and_format_data() %>%
  filter(time_bin == 'sustained') %>%
  select(blockname, subject, set_id, region, time_bin, bin_trial, solution, solution_label, zscore_blsub_mean) %>%
  left_join(plt_data_licking_binned_sat, by = c('blockname', 'set_id', 'subject', 'bin_trial', 'solution', 'solution_label')) %>%
  group_by(blockname, set_id, subject, bin_trial) %>%
  mutate(zscore_blsub_binned_mean = mean(zscore_blsub_mean)) %>%
  ungroup() %>%
  mutate(zscore_blsub_mean_normalized = zscore_blsub_mean / zscore_blsub_binned_mean)

# subset to main 3 set_ids + water, rank by solution
plt_data_k <- plt_data_bins_sat %>%
  filter(set_id %in% c('WR:Suc', 'FR:Suc', 'WR:NaCl', 'WR:Water')) %>%
  get_solution_rank() %>%
  mutate(bin_trial = bin_trial %>% as.integer() + 5) %>%
  filter(solution_rank %in% c(1, 5)) %>%
  mutate(solution_rank = ifelse(solution_rank == 1, 'Low', 'High'))
```

```{r eval=FALSE}
# ── left: licking by trial bin (high vs low solution rank) ───────────────────
fn_stem_k_lick <- 'fp_satiation_rank_trialbin_licking'

plt_data_k_lick <- plt_data_licking_binned_sat %>%
  filter(set_id %in% c('WR:Suc', 'FR:Suc', 'WR:NaCl')) %>%
  get_solution_rank() %>%
  mutate(bin_trial = bin_trial %>% as.integer() + 5) %>%
  filter(solution_rank %in% c(1, 5)) %>%
  mutate(solution_rank = ifelse(solution_rank == 1, 'Low', 'High')) %>%
  group_by(set_id, subject, bin_trial, solution_rank) %>%
  summarise(lick_count = mean(lick_count), .groups = 'drop')

plt_data_k_lick %>%
  ggplot(aes(bin_trial, lick_count, color = set_id, fill = set_id,
             linetype = solution_rank, group = interaction(solution_rank, set_id))) +
  geom_hline(yintercept = 0, color = 'darkgrey', linewidth = 1/3) +
  stat_summary(fun.data = 'mean_se', geom = 'ribbon', color = NA, alpha = 1/3) +
  stat_summary(fun = 'mean', geom = 'line') +
  theme_ag01(6) +
  facet_grid(solution_rank ~ .) +
  xlab('Trial bin') +
  ylab('Mean lick count') +
  scale_color_manual(values = colors_setid[c(1, 2, 3, 5)]) +
  scale_fill_manual(values  = colors_setid[c(1, 2, 3, 5)]) +
  theme(panel.spacing.x = unit(3, "mm")) +
  theme(panel.spacing.y = unit(4, "mm")) +
  force_panelsizes(rows = unit(1, 'cm'), cols = unit(1, 'cm')) +
  coord_cartesian(xlim = c(0, 100), ylim = c(0, 20), expand = FALSE, clip = 'off') +
  scale_x_continuous(breaks = c(0, 50, 100))

save_pdf(dir_output_k, str_c(fn_stem_k_lick, '.pdf'), 12, 12)
plt_data_k_lick %>% write_csv(str_c(dir_output_k, fn_stem_k_lick, '_data.csv'))
```

```{r eval=FALSE}
# ── right: z-score by trial bin (high vs low solution rank) ──────────────────
fn_stem_k_zs <- 'fp_satiation_rank_trialbin_zscore'

plt_data_k_zs <- plt_data_k %>%
  group_by(set_id, subject, region, bin_trial, solution_rank) %>%
  summarise(zscore_blsub_mean = mean(zscore_blsub_mean), .groups = 'drop')

plt_data_k_zs %>%
  ggplot(aes(bin_trial, zscore_blsub_mean, color = set_id, fill = set_id,
             linetype = solution_rank, group = interaction(solution_rank, set_id))) +
  geom_hline(yintercept = 0, color = 'darkgrey', linewidth = 1/3) +
  stat_summary(fun.data = 'mean_se', geom = 'ribbon', color = NA, alpha = 1/3) +
  stat_summary(fun = 'mean', geom = 'line') +
  theme_ag01(6) +
  facet_grid(solution_rank ~ region) +
  xlab('Trial bin') +
  ylab('Z-score') +
  scale_color_manual(values = colors_setid[c(1, 2, 3, 5)]) +
  scale_fill_manual(values  = colors_setid[c(1, 2, 3, 5)]) +
  coord_cartesian(xlim = c(0, 100), ylim = c(-3, 6), expand = FALSE, clip = 'off') +
  scale_y_continuous(breaks = c(-3, 0, 3, 6)) +
  scale_x_continuous(breaks = c(0, 50, 100)) +
  theme(panel.spacing.x = unit(3, "mm")) +
  theme(panel.spacing.y = unit(4, "mm")) +
  force_panelsizes(rows = unit(1, 'cm'), cols = unit(0.8, 'cm'))

save_pdf(dir_output_k, str_c(fn_stem_k_zs, '.pdf'), 12, 12)
plt_data_k_zs %>% write_csv(str_c(dir_output_k, fn_stem_k_zs, '_data.csv'))
```

---

## sfig09l: satiation — zscore High × Low regression slope bar
```{r eval=FALSE}
dir_output_l <- str_c(dir_output, 'l/')
dir.create(dir_output_l, recursive = TRUE, showWarnings = FALSE)

fn_stem_l <- 'fp_satiation_rank_trialbin_zsvszs_slope'

df_slopes_zs_vs_zs <- plt_data_k %>%
  group_by(set_id, subject, region, bin_trial, solution_rank) %>%
  summarise(zscore_blsub_mean = mean(zscore_blsub_mean, na.rm = TRUE), .groups = 'drop') %>%
  spread(solution_rank, zscore_blsub_mean) %>%
  group_by(subject, set_id, region) %>%
  summarise(
    slope = coef(lm(High ~ Low))[["Low"]],
    .groups = "drop"
  )
```

```{r eval=FALSE}
df_slopes_zs_vs_zs %>%
  ggplot(aes(region, slope, color = set_id, fill = set_id, group = set_id)) +
  stat_summary(fun.data = 'mean_se', geom = 'errorbar', width = 0, position = position_dodge(0.5)) +
  stat_summary(fun = 'mean', geom = 'bar', width = 0.5, alpha = 1/3, position = position_dodge(0.5)) +
  geom_hline(yintercept = 0, linewidth = 1/2, color = 'darkgrey') +
  theme_ag01(6) +
  scale_color_manual(values = colors_setid[c(1, 2, 3, 5)]) +
  scale_fill_manual(values  = colors_setid[c(1, 2, 3, 5)]) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3)) +
  theme(strip.text = element_text(margin = margin(t = 5, r = 5, b = 5, l = 5))) +
  theme(panel.spacing.y = unit(3, "mm")) +
  ylab('High zs × low zs regression slope') +
  xlab('') +
  coord_cartesian(xlim = c(0.5, 10.5), ylim = c(-1.5, 1), expand = FALSE, clip = 'off') +
  force_panelsizes(rows = unit(30, 'mm'), cols = unit(39, 'mm'))

save_pdf(dir_output_l, str_c(fn_stem_l, '_dodge.pdf'), 12, 12)
df_slopes_zs_vs_zs %>% write_csv(str_c(dir_output_l, fn_stem_l, '_data.csv'))

# mixed ANOVA: slope ~ region (between) × set_id (within)
# note: aov_rm_one_between_one_within must be available in stats.R
stats_list_l <- df_slopes_zs_vs_zs %>%
  filter(!region %>% str_detect('LHA')) %>%
  group_by(set_id) %>%
  mutate(subject_dummy = subject %>% str_c('_', row_number())) %>%
  ungroup() %>%
  aov_rm_one_between_one_within(dir_output_l, fn_stem_l, 'subject_dummy', 'slope', 'region', 'set_id')
```

---

## sfig09m: satiation — rank × trial bin slope summary bar
```{r eval=FALSE}
dir_output_m <- str_c(dir_output, 'm/')
dir.create(dir_output_m, recursive = TRUE, showWarnings = FALSE)

fn_stem_m <- 'fp_satiation_rank_trialbin_slope'

df_slopes_m <- plt_data_k_zs %>%
  group_by(subject, set_id, solution_rank, region) %>%
  summarise(
    slope = coef(lm(zscore_blsub_mean ~ bin_trial))[["bin_trial"]],
    .groups = "drop"
  )
```

```{r eval=FALSE}
df_slopes_m %>%
  ggplot(aes(set_id, slope, color = set_id, fill = set_id)) +
  geom_hline(yintercept = 0, color = 'darkgrey', linewidth = 1/3) +
  stat_summary(fun.data = 'mean_se', geom = 'errorbar', width = 0) +
  stat_summary(fun = 'mean', geom = 'bar', width = 0.6) +
  facet_grid(solution_rank ~ region) +
  theme_ag01(6) +
  scale_color_manual(values = colors_setid[c(1, 2, 3, 5)]) +
  scale_fill_manual(values  = colors_setid[c(1, 2, 3, 5)]) +
  theme(panel.spacing.x = unit(3, "mm")) +
  theme(panel.spacing.y = unit(4, "mm")) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.3)) +
  coord_cartesian(xlim = c(0.5, 3.5), ylim = c(-0.03, 0.01), expand = FALSE, clip = 'off') +
  scale_y_continuous(breaks = seq(-0.03, 0.01, 0.01)) +
  force_panelsizes(rows = unit(1, 'cm'), cols = unit(0.8, 'cm'))

save_pdf(dir_output_m, str_c(fn_stem_m, '.pdf'), 12, 12)
df_slopes_m %>% write_csv(str_c(dir_output_m, fn_stem_m, '_data.csv'))

# two-way RM ANOVA: slope ~ set_id × solution_rank (within subjects, per region)
regions_m <- unique(df_slopes_m$region)

stats_main_m <- map_dfr(regions_m, function(r) {
  stats_list <- df_slopes_m %>%
    filter(region == r) %>%
    aov_rm_two_within(NA, NA, 'subject', 'slope', 'set_id', 'solution_rank')
  stats_list[[2]] %>% mutate(region = r)
}) %>% select(region, everything())

stats_hsd_m <- map_dfr(regions_m, function(r) {
  stats_list <- df_slopes_m %>%
    filter(region == r) %>%
    aov_rm_two_within(NA, NA, 'subject', 'slope', 'set_id', 'solution_rank')
  stats_list[[3]] %>% mutate(region = r)
}) %>% select(region, everything())

stats_main_m %>% write_csv(str_c(dir_output_m, fn_stem_m, '_aov.csv'))
stats_hsd_m  %>% write_csv(str_c(dir_output_m, fn_stem_m, '_aov_hsd.csv'))
```

---
